### 2015-04-20 paper.tex
Wrap some text

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level
% headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they
% are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF
% before submission.
% - Figures containing multiple panels/subfigures must be combined into one
% image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular
% environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table
% guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth
% environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special
% characters according to our specifications. For more tips to help reduce the
% possibility of formatting errors during conversion, please see our LaTeX
% guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2
% will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit
% size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within
% the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information
% section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with
% a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,
singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions,
% and articles.
\begin{flushleft}
{\Large
\textbf\newline{Article Title - Submission to PLOS Journals}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,\Yinyang},
Name2 Surname\textsuperscript{2,\Yinyang},
Name3 Surname\textsuperscript{2,\textcurrency a},
Name4 Surname\textsuperscript{2,\ddag},
Name5 Surname\textsuperscript{2,\ddag},
Name6 Surname\textsuperscript{2},
Name7 Surname\textsuperscript{3,*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert
% symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as
% senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
\dag Deceased

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* CorrespondingAuthor@institute.edu

\end{flushleft}

% Please keep the abstract below 300 words
\section*{Abstract}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur
eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui
eu ante cursus gravida non sed sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus,
commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis
maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

\begin{equation}\label{eq:schemeP} 
D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
\end{equation}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

% For figure citations, please use "Fig." instead of "Figure".
Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum.
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae
nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu
ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
Praesent faucibus semper libero.

\begin{figure}[h]
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\begin{enumerate}
\item{react}
\item{diffuse free particles}
\item{increment time by dt and go to 1}
\end{enumerate}

% Results and Discussion can be combined.
\section*{Results}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim
rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo
vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper
tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis
arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
faucibus semper libero.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh.
Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur
fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt
sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum
dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium
imperdiet. Sed suscipit iaculis mi at feugiat.

\subsection*{Sed ac quam id nisi malesuada congue.}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Please do not create a heading level below \subsection. For 3rd level
% headings, use \paragraph{}.
\subsection*{Subsection 1}
Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{Subsection 2}
\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat
euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et
dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue
semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel
sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
Praesent faucibus semper libero.

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim
rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo
vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper
tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis
arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
faucibus semper libero.

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque
augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit.
Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at
feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus
venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec
pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu
suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida
venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec,
auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus
luctus est, non vulputate nisl augue at dolor. For more information, see
\nameref{S1_Text}.

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
\subsection*{S1 Video}
\label{S1_Video}
{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices
gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec
euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Text}
\label{S1_Text}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Fig}
\label{S1_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S2 Fig}
\label{S2_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Table}
\label{S1_Table}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et
malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac
quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam
rhoncus vitae.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{bib1}
Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in
South Indian Tamils may be influenced by genetic selection pressure on TLR2 and
TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi:
10.1016/j.molimm.2014.11.005

\bibitem{bib2}
Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a
conceptual framework. Global Health. 2005;1: 14. Available:
http://www.globalizationandhealth.com/content/1/1/14.

\end{thebibliography}

\end{document}

### 2015-04-20 getfigs.py
Add power and drag coefficient curves

@@ -11,8 +11,9 @@ import shutil
 figdir = os.path.join(os.path.expanduser("~"), "Research",
         "Experiments", "RM2 tow tank", "Figures")
 
-figlist = ["perf_curves.tiff",
-           "perf_re_dep.tiff"]
+figlist = ["cp_curves.eps",
+           "cd_curves.eps",
+           "re_dep_cp.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2015-04-20 paper.tex
Add figure
Add power and drag coefficient curves
Add figure captions
Comment out figures on master branch
Add wake characteristic figures

@@
 \end{tabular}
-\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\begin{flushleft} 
+Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec 
+pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
 \end{flushleft}
@@
 
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
+\subsection*{Performance}
 
@@
 
-\subsection*{Sed ac quam id nisi malesuada congue.}
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/cp_curves}
+\caption{{\bf Power Coefficient Curves.}
+Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
+Reynolds numbers.}
+\label{cp-curves}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/cd_curves}
+\caption{{\bf Drag Coefficient Curves.}
+Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
+Reynolds numbers.}
+\label{cd-curves}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/re_dep_cp}
+\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
+varius, volutpat euismod diam.}
+Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
+rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\label{cp-re-dep}
+\end{figure}
+
+\subsection*{Wake characteristics}
 
@@
 semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.
+
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/meancontquiv}
+\caption{{\bf Near-Wake Mean Velocity Field.}
+Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
+$\lambda=3.1$.}
+\label{meancontquiv}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/k_contours}
+\caption{{\bf Turbulence Kinetic Energy.}
+Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
+$\lambda=3.1$.}
+\label{kcont}
+\end{figure}
 

### 2015-04-20 getfigs.py

@@ -13,7 +13,9 @@ figdir = os.path.join(os.path.expanduser("~"), "Research",
 
 figlist = ["cp_curves.eps",
            "cd_curves.eps",
-           "re_dep_cp.eps"]
+           "re_dep_cp.eps",
+	   "meancontquiv.eps",
+	   "k_contours.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2015-04-20 paper.tex
Add caption for cp re dep
Copy/paste introduction from test plan report

@@
 \section*{Introduction}
-Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur
-eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui
-eu ante cursus gravida non sed sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus,
-commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
-finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis
-maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut
-ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
-pulvinar, volutpat risus.
+Sandia National Laboratory (SNL) developed the cross-flow turbine, Reference
+Model 2 (RM2), to provide an open-source point design for MHK research and
+development, including its use as a test object for scaled model testing to
+generate power performance data that can be used to validate open-source design
+tools. More details on the reference modeling effort are provided in Neary et
+al. \cite{Neary2014}.
 
-\begin{equation}\label{eq:schemeP} 
-D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}}, 
-D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
+Dimensional analysis provides scaling laws that are used to upscale model test
+data into performance and design information for a full-scale prototype turbine.
+For hydrokinetic turbines, hydrodynamic similitude is achieved when the Reynolds
+number, Froude number and tip-speed-ratio of the model and the full scale device
+match. The Reynolds number is defined as
+\begin{equation}
+Re_L = \frac{UL}{\nu},
+\label{eq-Re}
 \end{equation}
+where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
+kinematic viscosity. The Froude number is defined as
+\begin{equation}
+Fr = \frac{U}{\sqrt{gL}},
+\label{eq-Fr}
+\end{equation}
+where $g$ is the gravitational acceleration, and the tip speed ratio is defined
+as
+\begin{equation}
+\lambda=\frac{\omega R}{U_\infty},
+\end{equation}
+where $\omega$ and $R$ are the rotor angular velocity and radius.
+For hydrokinetic turbine testing, $Re$, not $Fr$, is the dominant scaling
+parameter. However, the Froude number (based on blade tip submergence) should
+remain small (significantly below one). It is rare to achieve perfect similitude
+for $Re$, but a threshold value should be exceeded, such that scale model
+results can be extrapolated.
 
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
+As a cross-flow turbine, the RM2 blades will experience large variations in
+angles of attack as they rotate about their axis (``cross-flow turbine'' means
+the axis of rotation is perpendicular to flow direction---either vertically or
+horizontally). These variations become larger as the tip speed ratio decreases
+\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
+that the blades operate under dynamic stall, which is a complex unsteady process
+and deviates significantly from static foil behavior, during part of the
+rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
+lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
+(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
+turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
+operate in a higher density fluid, unsteady dynamic effects related to the
+blades' pitching motion and flow curvature also become more important when
+compared to wind turbines.
+
+The performance of cross-flow MHK turbines thus depends on both Reynolds number
+and solidity (note that these issues are related, since an average blade chord
+Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
+expressed in terms of tip speed ratio, the optimal value for which is a function
+of solidity). If numerical models are validated with physical model data that
+was obtained at insufficiently high Reynolds numbers, it cannot be determined
+whether problems with model predictions are caused by Reynolds number effects,
+issues related to higher solidity, or both. It is uncertain whether numerical
+models validated with physical model data obtained at low Reynolds number should
+be considered validated at all, since the scale at which the model will be
+applied is orders of magnitude larger. One way to overcome this uncertainty is
+to show that the scaled physical model test has become Reynolds number
+independent, and therefore validation efforts should be relevant at full-scale.
+
+For example, the effect of Reynolds number on average power output was shown to
+be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
+testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
+increased with Reynolds number, $Re_c$, along with a shift of the location of
+$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
+The effects of Reynolds number were quite dramatic over a relatively small range
+of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
+Wosnik \cite{Bachant2014} showed that turbine performance and near-wake
+characteristics become Reynolds number independent at $Re_c \approx 2 \times
+10^5$.
+
+The need for experimental data that is relevant to full-scale behavior stems
+from the need to validate numerical models---most importantly mid-fidelity
+models---desirable for MHK developers to predict the performance of their
+cross-flow turbine designs, since physical modeling at appropriate scales can be
+prohibitively expensive in the early stages of engineering. Furthermore,
+Navier--Stokes-based computational fluid dynamics (CFD) simulations require
+modeling in 3 dimensions, which generally necessitates high performance
+computing---a resource that is not commonly available, and more expensive.
+
+To date, attempts to validate SNL's mid-fidelity CACTUS vortex line model
+\cite{Murray2011} have relied on measurements from the Saint Anthony Falls
+Laboratory (SAFL) \cite{Hill2014} and the University of New Hampshire (UNH)
+\cite{Neary2013, Michelen2014}. For the SAFL experiments (RM2), the chord
+Reynolds number, $Re_c \sim 10^4$, was below the threshold needed to properly
+simulate lift and stall characteristics. For the UNH experiment
+\cite{Bachant2013}, the chord Reynolds number was sufficiently high at $Re_c
+\approx 2.7 \times 10^5$, but the chord/radius ratio and solidity (13.4\%)
+created instability in the free-wake evolution in the model, which caused
+significant overestimation of power coefficient.
+
+The present task is to acquire a new dataset for the lower solidity RM2 turbine,
+but at higher Reynolds numbers than those achieved in the experiments at SAFL.
+It is also suspected that the strut drag model in CACTUS could be the source of
+some discrepancy. The strut drag will be deliberately modified in the physical
+model to provide data to help answer that question. This dataset will be
+publicly available for both validation of CACTUS and other numerical models.
+This report details the experimental test plan for acquiring, processing, and
+archiving this data, which includes development of a scaled physical model, and
+descriptions of the experimental setup and procedure to be performed in a towing
+tank at the University of New Hampshire (UNH).
+
 \section*{Materials and Methods}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/cp_curves}
+%\includegraphics[width=\textwidth]{figures/cp_curves}
 \caption{{\bf Power Coefficient Curves.}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/cd_curves}
+%\includegraphics[width=\textwidth]{figures/cd_curves}
 \caption{{\bf Drag Coefficient Curves.}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/re_dep_cp}
-\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
-varius, volutpat euismod diam.}
-Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
-rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+%\includegraphics[width=\textwidth]{figures/re_dep_cp}
+\caption{{\bf Power Coefficient Reynolds Number Dependence.}
+Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
 \label{cp-re-dep}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/meancontquiv}
+%\includegraphics[width=\textwidth]{figures/meancontquiv}
 \caption{{\bf Near-Wake Mean Velocity Field.}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/k_contours}
+%\includegraphics[width=\textwidth]{figures/k_contours}
 \caption{{\bf Turbulence Kinetic Energy.}
@@
 
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
 % Compile your BiBTeX database using our plos2015.bst
@@
 % 
-\begin{thebibliography}{10}
-\bibitem{bib1}
-Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in
-South Indian Tamils may be influenced by genetic selection pressure on TLR2 and
-TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi:
-10.1016/j.molimm.2014.11.005
-
-\bibitem{bib2}
-Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a
-conceptual framework. Global Health. 2005;1: 14. Available:
-http://www.globalizationandhealth.com/content/1/1/14.
-
-\end{thebibliography}
+\bibliography{library}
 

### 2015-04-20 paper.tex
Combine results and discussion

@@
 % Results and Discussion can be combined.
-\section*{Results}
+\section*{Results and Discussion}
 Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
@@
 
-\section*{Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
-diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim
-rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo
-vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper
-tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis
-arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
-faucibus semper libero.
-
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
-ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque
-augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at
-feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus
-venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec
-pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu
-suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida
-venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec,
-auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus
-luctus est, non vulputate nisl augue at dolor. For more information, see
-\nameref{S1_Text}.
-
 \section*{Supporting Information}

### 2015-04-20 paper.tex
Add acknowledgements from test plan report

@@
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et
-malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac
-quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam
-rhoncus vitae.
+
+This study was supported by the Department of Energy (DOE), Office of Energy
+Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
+(WWPTO). Sandia National Laboratories is a multi-program laboratory managed and
+operated by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
+Corporation, for the U.S. Department of Energy's National Nuclear Security
+Administration under contract DE-AC04-94AL85000.
 

### 2015-04-20 paper.tex
Add turbine description

@@
 \section*{Materials and Methods}
-\subsection*{Etiam eget sapien nibh.}
+\subsection*{Turbine Model}
 
 % For figure citations, please use "Fig." instead of "Figure".
-Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae
-nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu
-ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
-sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
+parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
+with the exception of the shaft diameter, which was scaled from the SAFL RM2
+shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
+which may aid in comparison of the results, though this was not a top priority.
+Geometric parameters are shown in Table~\ref{tab:turb-geom} and a drawing of the
+turbine design is shown in Figure~\ref{fig:turbine-drawing}. The turbine model
+components---blades, struts, shaft, and center hub sections---were fabricated
+from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
+class 2 specifications. CAD models of the turbine are available from
+\cite{Bachant2015-RM2-CAD}.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{l|l|l}
+   & Full-scale & Model (1:6) \\
+\hline 
+Diameter (m)   & 6.450 & 1.075 \\ 
+Height (m)     & 4.840 & 0.8067 \\ 
+Blade root chord (m) & 0.4000 & 0.06667 \\ 
+Blade tip chord (m)  & 0.2400 & 0.04000 \\ 
+Blade profile & NACA 0021 & NACA 0021 \\ 
+Blade mount & 1/2 chord & 1/2 chord \\ 
+Blade pitch (deg.) & 0.0 & 0.0 \\ 
+Strut profile & NACA 0021 & NACA 0021 \\ 
+Strut chord (m) & 0.3600 & 0.06000 \\ 
+Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\ 
+\end{tabular}
+\caption{RM2 turbine geometric parameters.}
+\label{tab:turb-geom}
+\end{table}
 
 \begin{figure}[h]
-\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
-varius, volutpat euismod diam.}
-Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
-rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
+\caption{{\bf Turbine Model Drawing.}
+Drawing of the turbine with and without strut covers.}
+\label{fig:turbine-drawing}
 \end{figure}
 
-\begin{enumerate}
-\item{react}
-\item{diffuse free particles}
-\item{increment time by dt and go to 1}
-\end{enumerate}
-
-% Results and Discussion can be combined.
 \section*{Results and Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
-diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim
-rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo
-vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper
-tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis
-arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
-faucibus semper libero.
 

### 2015-04-20 paper.tex
Style fixes
Add facility and instrumentation section from test plan

@@
 \section*{Materials and Methods}
+
 \subsection*{Turbine Model}
@@
 which may aid in comparison of the results, though this was not a top priority.
-Geometric parameters are shown in Table~\ref{tab:turb-geom} and a drawing of the
-turbine design is shown in Figure~\ref{fig:turbine-drawing}. The turbine model
+Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
+turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
 components---blades, struts, shaft, and center hub sections---were fabricated
@@
 \end{tabular}
-\caption{RM2 turbine geometric parameters.}
+\caption{\textbf{RM2 turbine geometric parameters.}}
 \label{tab:turb-geom}
@@
 \end{figure}
+
+\subsection*{Facility and instrumentation}
+
+Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
+3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
+pictured in Figure~\ref{fig:tow-tank}. The turbine was mounted in a frame built
+from NACA 0020 struts, attached to the tow carriage by four linear bearings,
+which transfer all streamwise force to a pair of S-beam load cells. The turbine
+shaft RPM was controlled by a servo motor system, which allowed prescription of
+the turbine tip speed ratio. The load torque was measured by an inline rotary
+torque transducer and a load cell mounted at a fixed distance from the servo
+motor, providing a redundant measurement. Turbine shaft angle was measured using
+the servo drive's emulated encoder output, set to $10^5$ counts per turbine
+shaft revolution. Carriage speed, and therefore inflow velocity was measured
+using a linear encoder with 10 $\mu$m resolution. All of these
+performance-related quantities were sampled as 2 kHz, while the tow tank's
+motion controller provided redundant measurements of the carriage speed and
+turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
+downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
+sampling at 200 Hz. A drawing of the experimental setup is shown in
+Figure~\ref{fig:exp-setup}.
+
+\begin{figure}[h]
+\caption{Photos of the UNH towing tank and turbine test bed.} 
+\label{fig:tow-tank}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+%\includegraphics[clip,trim=0.01in 0 0 0,
+%width=0.95\textwidth]{Figures/tank_cross_section}
+\caption{Illustration of the experimental setup.}
+\label{fig:exp-setup}
+\end{figure}
+
+\paragraph{Synchronization.} The three data acquisition instrumentation
+subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
+(wake velocity measurements)---started sampling at precisely the same time each
+tow, after being triggered by a TTL pulse created by the motion controller. This
+strategy retained synchronization for all performance signal samples (tow speed,
+torque, drag, angular velocity), ensuring precise calculation of, e.g., power
+coefficient. Since there is also synchronization of the initial sample from each
+three subsystems, correlation of events in the performance and wake signals is
+also possible.
+
+\paragraph{Tare drag and torque compensation.} Tare torque and drag runs were
+performed to measure the shaft bearing friction torque and turbine mounting
+frame drag, respectively. Tare drag runs were performed for each tow speed in
+the experiment, for which the mean value was used in data processing. Tare
+torque runs were performed by rotating the turbine shaft (without blades) in air
+at constant angular velocity for a specified duration, over the range of angular
+velocities used throughout the experiment. Tare torque was fit with a linear
+regression versus shaft angular velocity, and added to the measured turbine
+torque in post-processing.
 

### 2015-04-20 paper.tex
Add test parameters section
Add todo list

@@
 
+% To-do notes
+\usepackage{todonotes}
+
 %% Include all macros below
@@
 \end{flushleft}
+
+\listoftodos
 
@@
 
+\subsection*{Test parameters}
+
+Data collection runs were separated into individual tows, for which all
+independent variables---tow speed, tip speed ratio, velocity probe
+position---were held constant. These runs were grouped into logical test matrix
+``sections,'' in which typically a single independent variable was varied.
+
+\todo[inline]{Add all test matrix sections and their descriptions here.}
+
 \section*{Results and Discussion}

### 2015-04-20 paper.tex
Add Re table
Add tentative title

@@
 \begin{flushleft}
-{\Large
-\textbf\newline{Article Title - Submission to PLOS Journals}
-}
+
+{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
+cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
+and blade support strut drag}}
 \newline
@@
 
+\begin{table}[ht]
+\centering
+\begin{tabular}{c|c|c}
+Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
+\hline 
+0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
+0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
+0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
+0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
+1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
+1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
+1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
+\end{tabular} 
+\caption{{\textbf Test Reynolds numbers.}Turbine diameter and approximate blade 
+chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
+\end{table}
+
+\todo[inline]{Check which chord length was used to calculate $Re_c$, and
+recalculate using $\lambda=3.1$.}
+
 \section*{Results and Discussion}

### 2015-04-20 paper.tex
Slight modification to title

@@
 cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
-and blade support strut drag}}
+and blade support strut losses}}
 \newline

### 2015-04-20 paper.tex
Add author names

@@
 \\
-Name1 Surname\textsuperscript{1,\Yinyang},
-Name2 Surname\textsuperscript{2,\Yinyang},
-Name3 Surname\textsuperscript{2,\textcurrency a},
-Name4 Surname\textsuperscript{2,\ddag},
-Name5 Surname\textsuperscript{2,\ddag},
-Name6 Surname\textsuperscript{2},
-Name7 Surname\textsuperscript{3,*},
-with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
+Peter Bachant\textsuperscript{1,\Yinyang},
+Martin Wosnik\textsuperscript{1,\Yinyang},
+Budi Gunawan\textsuperscript{2,\textcurrency a},
+Vincent Neary\textsuperscript{2,\ddag}
 \\

### 2015-04-20 paper.tex
Change tense

@@
 
-The present task is to acquire a new dataset for the lower solidity RM2 turbine,
-but at higher Reynolds numbers than those achieved in the experiments at SAFL.
-It is also suspected that the strut drag model in CACTUS could be the source of
-some discrepancy. The strut drag will be deliberately modified in the physical
-model to provide data to help answer that question. This dataset will be
+The present task was to acquire a new dataset for the lower solidity RM2
+turbine, but at higher Reynolds numbers than those achieved in the experiments
+at SAFL. It is also suspected that the strut drag model in CACTUS could be the
+source of some discrepancy. The strut drag was deliberately modified in the
+physical model to provide data to help answer that question. This dataset is
 publicly available for both validation of CACTUS and other numerical models.
-This report details the experimental test plan for acquiring, processing, and
-archiving this data, which includes development of a scaled physical model, and
-descriptions of the experimental setup and procedure to be performed in a towing
-tank at the University of New Hampshire (UNH).
 

### 2015-04-20 paper.tex
Remove author summary
Fix labels and remove template text
Remove template table and fix labels

@@
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
-erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
-cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
-volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
-non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
-convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
-ultrices, ultrices elit pulvinar, volutpat risus.
-
 \linenumbers
@@
 Re_L = \frac{UL}{\nu},
-\label{eq-Re}
+\label{eq:Re}
 \end{equation}
@@
 Fr = \frac{U}{\sqrt{gL}},
-\label{eq-Fr}
+\label{eq:Fr}
 \end{equation}
@@
 
-\begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\caption{
-{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-\begin{tabular}{|l|l|l|l|l|l|l|l|}
-\hline
-\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-\end{tabular}
-\begin{flushleft} 
-Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec 
-pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
-\end{table}
-
 \subsection*{Performance}
@@
 Reynolds numbers.}
-\label{cp-curves}
+\label{fig:cp-curves}
 \end{figure}
@@
 Reynolds numbers.}
-\label{cd-curves}
+\label{fig:cd-curves}
 \end{figure}
@@
 Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
-\label{cp-re-dep}
+\label{fig:cp-re-dep}
 \end{figure}
@@
 
-% Please do not create a heading level below \subsection. For 3rd level
-% headings, use \paragraph{}.
-\subsection*{Subsection 1}
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
-massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
-amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
-eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
-erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
-semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.
-
-\subsection*{Subsection 2}
-\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat
-euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et
-dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue
-semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel
-sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+\subsection*{Strut drag losses}
 

### 2015-04-21 paper.tex
Fix boldface
Fix labels
Add K transport bar graph figure

@@
 \end{tabular} 
-\caption{{\textbf Test Reynolds numbers.}Turbine diameter and approximate blade 
+\caption{{\bf Test Reynolds numbers.}Turbine diameter and approximate blade 
 chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
@@
 $\lambda=3.1$.}
-\label{meancontquiv}
+\label{fig:meancontquiv}
 \end{figure}
@@
 $\lambda=3.1$.}
-\label{kcont}
+\label{fig:kcont}
+\end{figure}
+
+\begin{figure}[ht!]
+\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
+\caption{{\bf Mean Kinetic Energy Transport.}
+Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
+\label{fig:Ktransport}
 \end{figure}

### 2015-04-21 getfigs.py

@@ -15,7 +15,8 @@ figlist = ["cp_curves.eps",
            "cd_curves.eps",
            "re_dep_cp.eps",
 	   "meancontquiv.eps",
-	   "k_contours.eps"]
+	   "k_contours.eps",
+	   "K_trans_bar_graph.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2015-04-21 paper.tex
Discuss wake figures

@@
 
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
-massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
-amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
-eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
-erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
-semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.
+The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
+($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
+velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
+lower acceleration around the turbine thanks to lower rotor drag coefficient and
+blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
+vortex shedding are relatively weaker.
 
@@
 
+Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
+mainly see unsteadiness in the flow generated by the blade tip vortex shedding
+(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
+generation is lower overall, without the intense vertical band around $y/R=-1$,
+which indicated that the RM2 blades are operating further from
+stall---consistent with the higher tip speed ratio operation.
+
 \begin{figure}[h]
@@
 
+Totals for the transport terms in the mean kinetic energy equation---analyzed
+identically to \cite{Bachant2015-JoT}---are shown in Fig.~\ref{fig:Ktransport}.
+Due to the weaker blade vortex shedding, we see transport due to vertical
+advection at this point in the wake is approximately 3 times lower than the
+higher solidity UNH-RVAT. We also see relatively lower levels of cross-stream
+turbulent transport thanks to the lack of blade stall vortex shedding. These
+results may have interesting implications regarding the application of turbines
+with lower power coefficient to possibly improve overall array performance
+through enhanced transport of kinetic energy from the free stream, though a
+detailed anaylsis of the downstream evolution and turbine interaction will be
+necessary.
+
 \begin{figure}[ht!]
-\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
+%\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
 \caption{{\bf Mean Kinetic Energy Transport.}

### 2015-04-21 paper.tex
Write about performance figures

@@
 
-Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur
-fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt
-sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum
-dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium
-imperdiet. Sed suscipit iaculis mi at feugiat.
+Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
+versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
+respectively. $C_P$ is shown to increase in general with $Re$, along with a
+reduction in the optimal tip speed ratio, due to stall delay. These effect
+diminish with increasing $Re$, which is expected as the blade boundary layers
+transition from laminar to turbulent \cite{Lissaman1983,
+Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
+effects, but vary much less dramatically from each other.
 
@@
 \end{figure}
+
+The behavior of the power coefficient at $\lambda=3.1$ is plotted in
+Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
+highlighted. We see that the power coefficient of the turbine increases
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$,
+beyond which there appears to be a small, linear, positive trend. The tendency
+of $C_P$ to continue increasing slightly could be an effect of lower virtual
+camber when compared to the strong $Re$-indepdendence of the higher $c/R$
+UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
 

### 2015-04-21 paper.tex
Update title and author affiliations

@@
 {\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
-cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
-and blade support strut losses}}
+cross-flow hydrokinetic turbine at transitional Reynolds numbers: Power production, 
+near-wake dynamics, and blade support strut losses}}
 \newline
@@
 \bigskip
-\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, 
+USA
 \\
-\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
+\bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque, NM, USA
 \\

### 2015-04-21 paper.tex
Fix up author designations

@@
 \\
-Peter Bachant\textsuperscript{1,\Yinyang},
-Martin Wosnik\textsuperscript{1,\Yinyang},
-Budi Gunawan\textsuperscript{2,\textcurrency a},
-Vincent Neary\textsuperscript{2,\ddag}
+Peter Bachant\textsuperscript{1,*},
+Martin Wosnik\textsuperscript{1},
+Budi Gunawan\textsuperscript{2},
+Vincent Neary\textsuperscript{2}
 \\
@@
 
-% Insert additional author notes using the symbols described below. Insert
-% symbol callouts after author names as necessary.
-%
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as
-% senior authorship.
-\ddag These authors also contributed equally to this work.
-
-% Current address notes
-\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
-
-% Deceased author note
-\dag Deceased
-
-% Group/Consortium Author Note
-\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* CorrespondingAuthor@institute.edu
+% Use the asterisk to denote corresponding authorship and provide email address
+% in note below.
+* pxL3@unh.edu
 

### 2015-04-21 paper.tex
Define MHK

@@
 
-\section*{Introduction}
-Sandia National Laboratory (SNL) developed the cross-flow turbine, Reference
-Model 2 (RM2), to provide an open-source point design for MHK research and
-development, including its use as a test object for scaled model testing to
-generate power performance data that can be used to validate open-source design
-tools. More details on the reference modeling effort are provided in Neary et
-al. \cite{Neary2014}.
+\section*{Introduction} Sandia National Laboratory (SNL) developed the
+cross-flow turbine, Reference Model 2 (RM2), to provide an open-source point
+design for marine hydrokinetic (MHK) energy research and development, including
+its use as a test object for scaled model testing to generate power performance
+data that can be used to validate open-source design tools. More details on the
+reference modeling effort are provided in Neary et al. \cite{Neary2014}.
 

### 2015-04-21 paper.tex
Change hyperref parameters
Change tense of 'indicated'

@@
 % section for more info)
-\usepackage{nameref,hyperref}
+\usepackage{nameref}
+\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
 
@@
 generation is lower overall, without the intense vertical band around $y/R=-1$,
-which indicated that the RM2 blades are operating further from
+which indicates that the RM2 blades are operating further from
 stall---consistent with the higher tip speed ratio operation.

### 2015-04-21 paper.tex
Space in figure caption
Cite Re dep paper to be submitted

@@
 of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
-Wosnik \cite{Bachant2014} showed that turbine performance and near-wake
-characteristics become Reynolds number independent at $Re_c \approx 2 \times
-10^5$.
+Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine
+performance and near-wake characteristics become Reynolds number independent at
+$Re_c \approx 2 \times 10^5$.
 
@@
 \end{tabular} 
-\caption{{\bf Test Reynolds numbers.}Turbine diameter and approximate blade 
+\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade 
 chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}

### 2015-04-22 getfigs.py
Add strut torque figure

@@ -16,7 +16,8 @@ figlist = ["cp_curves.eps",
            "re_dep_cp.eps",
 	   "meancontquiv.eps",
 	   "k_contours.eps",
-	   "K_trans_bar_graph.eps"]
+	   "K_trans_bar_graph.eps",
+	   "no_blades_all.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2015-04-22 paper.tex
Add strut torque figure
Add perf covers figure

@@
 \begin{figure}[h]
-%\includegraphics[width=\textwidth]{figures/cp_curves}
+\includegraphics[width=\textwidth]{figures/cp_curves}
 \caption{{\bf Power Coefficient Curves.}
@@
 \begin{figure}[h]
-%\includegraphics[width=\textwidth]{figures/cd_curves}
+\includegraphics[width=\textwidth]{figures/cd_curves}
 \caption{{\bf Drag Coefficient Curves.}
@@
 \begin{figure}[h]
-%\includegraphics[width=\textwidth]{figures/re_dep_cp}
+\includegraphics[width=\textwidth]{figures/re_dep_cp}
 \caption{{\bf Power Coefficient Reynolds Number Dependence.}
@@
 \begin{figure}[h]
-%\includegraphics[width=\textwidth]{figures/meancontquiv}
-\caption{{\bf Near-Wake Mean Velocity Field.}
+\includegraphics[width=\textwidth]{figures/meancontquiv}
+\caption{{\bf Mean Velocity.}
 Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
@@
 \begin{figure}[h]
-%\includegraphics[width=\textwidth]{figures/k_contours}
+\includegraphics[width=\textwidth]{figures/k_contours}
 \caption{{\bf Turbulence Kinetic Energy.}
@@
 \begin{figure}[ht!]
-%\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
+\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
 \caption{{\bf Mean Kinetic Energy Transport.}
@@
 \subsection*{Strut drag losses}
+
+\begin{figure}[ht!]
+\includegraphics[width=\textwidth]{figures/no_blades_all}
+\caption{{\bf Strut drag losses.}
+Measurements of the strut drag losses for (a) NACA 0021 and (b) cylindrical 
+struts, both stationary and towed.}
+\label{fig:no-blades}
+\end{figure}
+
+\begin{figure}[ht!]
+\includegraphics[width=\textwidth]{figures/perf_covers}
+\caption{{\bf High drag strut performance.}
+Turbine performance and rotor drag coefficient curves with both NACA 0021
+and cylindrical struts.}
+\label{fig:perf-covers}
+\end{figure}
 

### 2015-04-22 getfigs.py

@@ -17,7 +17,8 @@ figlist = ["cp_curves.eps",
 	   "meancontquiv.eps",
 	   "k_contours.eps",
 	   "K_trans_bar_graph.eps",
-	   "no_blades_all.eps"]
+	   "no_blades_all.eps",
+	   "perf_covers.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2015-04-22 getfigs.py
Use subplots fig for perf Re dep

@@ -13,7 +13,7 @@ figdir = os.path.join(os.path.expanduser("~"), "Research",
 
 figlist = ["cp_curves.eps",
            "cd_curves.eps",
-           "re_dep_cp.eps",
+           "perf_re_dep.eps",
 	   "meancontquiv.eps",
 	   "k_contours.eps",
 	   "K_trans_bar_graph.eps",

### 2015-04-22 paper.tex
Use subplots fig for perf Re dep
Add figures

@@
 \begin{figure}[h]
-\caption{{\bf Turbine Model Drawing.}
-Drawing of the turbine with and without strut covers.}
+\includegraphics[width=0.65\textwidth]{figures/turbine}
+\caption{{\bf Turbine Model.}
+Drawing of the turbine.}
 \label{fig:turbine-drawing}
@@
 \centering
-%\includegraphics[clip,trim=0.01in 0 0 0,
-%width=0.95\textwidth]{Figures/tank_cross_section}
+\includegraphics[clip,trim=0.01in 0 0 0,
+width=\textwidth]{figures/tank_cross_section}
 \caption{Illustration of the experimental setup.}
@@
 
+Wake measurements were all performed at 1 m downstream, which corresponds to
+$x/D = 0.93$. The cross-stream and vertical coordinates are shown in
+Fig.~\ref{fig:coordinates}.
+
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figures/turbine_coordinate_system}
+\caption{{\bf Coordinate system.} Wake measurement coordinate system and 
+cross-stream/vertical coordinates. All dimensions are in meters.} 
+\label{fig:coordinates}
+\end{figure}
+
 \section*{Results and Discussion}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/re_dep_cp}
-\caption{{\bf Power Coefficient Reynolds Number Dependence.}
-Power coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
+\includegraphics[width=\textwidth]{figures/perf_re_dep}
+\caption{{\bf Reynolds Number effects on performance.}
+Power and drag coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
 \label{fig:cp-re-dep}

### 2015-04-22 paper.tex
Update figure captions
Delete supporting information section

@@
 \caption{{\bf Turbine Model.}
-Drawing of the turbine.}
+A drawing of the turbine model.}
 \label{fig:turbine-drawing}
@@
 width=\textwidth]{figures/tank_cross_section}
-\caption{Illustration of the experimental setup.}
+\caption{{\bf Experimental setup.} Illustration of the experimental setup.}
 \label{fig:exp-setup}
@@
 
-\section*{Supporting Information}
-
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-\subsection*{S1 Video}
-\label{S1_Video}
-{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices
-gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec
-euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Text}
-\label{S1_Text}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
-ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Fig}
-\label{S1_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
-ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S2 Fig}
-\label{S2_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
-ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Table}
-\label{S1_Table}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod
-ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
 \section*{Acknowledgments}

### 2015-04-23 paper.tex
Discuss data processing

@@
 
+\subsection*{Data Processing}
+
+For each tow, a relevant quasi-steady duration is selected, and then truncated
+to include a whole number of blade passages. Over this duration relevant
+statistics are calculated.
+
+To calculate turbine RPM from shaft angle, the encoder signal is differentiated
+using a second order central difference scheme, after which a relatively
+small-windowed moving average smoothing filter is applied to match the noise
+level present in the redundant turbine RPM measurement from the motion
+controller. A similar approach is used for calculating tow carriage speed
+$U_\infty$ from carriage position measurements. Power and drag coefficients are
+calculated as instantaneous quantities from the carriage speed as
+
+\begin{equation}
+C_P = \frac{T \omega}{\frac{1}{2} \rho A U_\infty^3}
+\end{equation}
+and
+\begin{equation}
+C_D = \frac{F_\mathrm{drag}}{\frac{1}{2} \rho A U_\infty^2},
+\end{equation}
+where $\rho$ is the fluid density (1000 kg/m\textsuperscript{3}) and $A$ is
+the turbine frontal area $DH$.
+
+All data processing and plotting code, along with the reduced dataset are
+available from \cite{Bachant2015-RM2-data}. Note that this code will
+automatically download raw data as necessary so users can perform a full
+reanalysis of the measurements presented here.
+
 \section*{Results and Discussion}

### 2015-04-23 paper.tex
Write conclusions

@@
 
+\subsection*{Conclusions}
+
+The performance and near-wake for a 1:6 scale DOE Reference Model 2 cross-flow
+turbine was measured in a towing tank. Performance was assessed for Reynolds
+number dependence, showing a convergence to a weakly $Re$-dependent linear
+regime at approximately $Re_D \approx 1 \times 10^6$ or $Re_{c,\mathrm{ave}}
+\approx 2 \times 10^5$. Comparison was made between this turbine and the higher
+solidity UNH-RVAT, tested in nearly identical conditions, which showed similar
+Reynold number thresholds but a flatter linear regime, likely to due virtual
+camber of the higher chord-to-radius ratio of the UNH-RVAT blades.
+
+The wake at $x/D=0.93$ downstream was shown to be relatively symmetrical and
+lacked the evidence of strong blade stall, which once again differentiates this
+turbine from the UNH-RVAT. Terms from the mean kinetic energy transport equation
+were also computed in this $y$--$z$ plane, showing the relative importance of
+the vertical advection compared with turbulent transport terms at this location.
+It is interesting to note that though the turbine is a more effective energy
+converter than the UNH-RVAT, its wake recovery may in fact be slower due to
+weaker blade tip vortex shedding.
+
+The effects of parasitic drag from blade support struts on turbine performance
+were measured by rotating the turbine without blades while stationary and while
+towing. It is shown that these losses---even for a streamlined hydrofoil
+strut---can become significant quickly at higher tip speed ratios---up to an
+approximate 5 percentage point decrease in power coefficient at a tip speed
+ratio of 5. These measurements were repeated with a set of high-drag cylindrical
+struts, which as expected, prevented the turbine from producing any mechanical
+power at any tip speed ratio. Nevertheless these measurements provide important
+validation data for both high and low fidelity numerical performance prediction
+models, allowing researchers to test models without blade effects.
+
+This data, along with the code for processing and visualization, is provided
+openly via a Creative Commons license, and is available from
+\cite{Bachant2015-RM2-data}. The authors hope that this can provide
+opportunities for extensive validation of predictive tools for the complex
+unsteady flow physics of cross-flow turbines.
+
 \section*{Acknowledgments}

### 2015-09-10 paper.tex
Correct tense
Use PLOS bibstyle
Remove dummy abstract

@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
-erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
-cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
-volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
-non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
-convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
-ultrices, ultrices elit pulvinar, volutpat risus.
+\todo[inline]{Write abstract.}
 
@@
 
-For each tow, a relevant quasi-steady duration is selected, and then truncated
+For each tow, a relevant quasi-steady duration was selected, and then truncated
 to include a whole number of blade passages. Over this duration relevant
@@
 % 
+\bibliographystyle{plos2015}
 \bibliography{library}

### 2015-09-10 paper.tex
Add test matrix section names and descriptions

@@
 position---were held constant. These runs were grouped into logical test matrix
-``sections,'' in which typically a single independent variable was varied.
+``sections,'' in which typically a single independent variable was varied. Test
+matrix section names and descriptions are given below, which outline the
+experimental data and code repository \cite{Bachant2015-RM2-data}.
 
-\todo[inline]{Add all test matrix sections and their descriptions here.}
+\begin{itemize}
+
+    \item \texttt{Perf-\{speed\}}: Performance curve at \texttt{\{speed\}} m/s
+    tow speed, performed for (0.4, 0.6, 0.8, 1.0, 1.2) m/s.
+
+    \item \texttt{Perf-\{speed\}-b}: Second performance curve at
+    \texttt{\{speed\}} m/s, performed for the same tow speeds as above for
+    reduced statistical uncertainty.
+
+    \item \texttt{Perf-1.0-covers}: Performance curve at 1.0 m/s tow speed with
+    cylindrical strut covers.
+
+    \item \texttt{Perf-1.0-no-blades-covers}: Performance curve at 1.0 m/s with
+    no blades and cylindrical strut covers.
+
+    \item \texttt{Perf-1.0-no-blades}: Performance curve at 1.0 m/s with no
+    blades (NACA 0021 struts only).
+
+    \item \texttt{Perf-tsr\_0}: Performance at $\lambda=3.1$ for multiple tow
+    speeds.
+
+    \item \texttt{Perf-tsr\_0-b}: Additional set of runs duplicating the
+    \texttt{Perf-tsr\_0} parameters.
+
+    \item \texttt{Strut-torque-covers}: Measuring parasitic torque from
+    cylindrical struts without towing.
+
+    \item \texttt{Strut-torque}: Measuring parasitic torque from
+    NACA 0021 struts without towing.
+
+    \item \texttt{Tare-drag}: Drag on the turbine frame measured with the turbine
+    removed.
+
+    \item \texttt{Tare-torque}: Measurements of friction torque in shaft
+    bearings for a range of RPMs used in the experiments.
+
+    \item \texttt{Wake-\{speed\}-\{z/H\}}: Cross-stream wake profile at 1 m
+    downstream ($x/D=0.93$), $\lambda=3.1$, \texttt{\{speed\}} m/s tow speed,
+    and \texttt{\{z/H\}} vertical location.
+\end{itemize}
 

### 2015-09-10 paper.tex
Recalculate Reynolds number table

@@
 \centering
-\begin{tabular}{c|c|c}
-Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
+\begin{tabular}{c|c|c|c|c}
+Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{ave}}$\\ 
 \hline 
-0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
-0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
-0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
-0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
-1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
-1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
-1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
+0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\ 
+0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\ 
+0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\ 
+1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\ 
+1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\ 
 \end{tabular}
+
 \caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade
-chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
+    chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ corresponding to various
+    tow speeds at $\lambda=3.1$.}
+
+\label{tab:re}
 \end{table}
-
-\todo[inline]{Check which chord length was used to calculate $Re_c$, and
-recalculate using $\lambda=3.1$.}
 

### 2015-09-10 paper.tex
Add comment about strut drag losses
Notes about comparing terms from different measurement areas

@@
 advection at this point in the wake is approximately 3 times lower than the
-higher solidity UNH-RVAT. We also see relatively lower levels of cross-stream
-turbulent transport thanks to the lack of blade stall vortex shedding. These
-results may have interesting implications regarding the application of turbines
-with lower power coefficient to possibly improve overall array performance
-through enhanced transport of kinetic energy from the free stream, though a
-detailed anaylsis of the downstream evolution and turbine interaction will be
-necessary.
+higher solidity UNH-RVAT. Note that direct comparison is somewhat invalid, since
+the total measurement plane area is about 5\% lower for this experiment.
+However, the differences observed are beyond this discrepancy. We also see
+relatively lower levels of cross-stream turbulent transport thanks to the lack
+of blade stall vortex shedding. These results may have interesting implications
+regarding the application of turbines with lower power coefficient to possibly
+improve overall array performance through enhanced transport of kinetic energy
+from the free stream, though a detailed anaylsis of the downstream evolution and
+turbine interaction will be necessary.
 
@@
 \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
-\caption{{\bf Mean Kinetic Energy Transport.}
-Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
+
+\caption{{\bf Mean Kinetic Energy Transport.} Weighted average estimates for
+    terms contributing to streamwise recovery of mean kinetic energy, multiplied by
+    two due to implied symmetry.}
+
 \label{fig:Ktransport}
@@
 \subsection*{Strut drag losses}
+
+We see that strut drag losses increase with tip speed ratio to the power 2--3,
+which makes streamlined struts much more important for low solidity turbines,
+given the inverse correlation between solidity and $\lambda_0$.
 

### 2015-09-11 paper.tex
Rearrange first couple introduction paragraphs

@@
 
-\section*{Introduction} Sandia National Laboratory (SNL) developed the
-cross-flow turbine, Reference Model 2 (RM2), to provide an open-source point
-design for marine hydrokinetic (MHK) energy research and development, including
-its use as a test object for scaled model testing to generate power performance
-data that can be used to validate open-source design tools. More details on the
-reference modeling effort are provided in Neary et al. \cite{Neary2014}.
+\section*{Introduction}
 
-Dimensional analysis provides scaling laws that are used to upscale model test
-data into performance and design information for a full-scale prototype turbine.
-For hydrokinetic turbines, hydrodynamic similitude is achieved when the Reynolds
-number, Froude number and tip-speed-ratio of the model and the full scale device
-match. The Reynolds number is defined as
+Sandia National Laboratories, in collaboration with the US Department of Energy
+developed the Reference Model devices to provide modeling targets for advancing
+marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
+Model 2 (RM2), a cross-flow turbine intended for river environments, was
+initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
+line code \cite{Murray2011}. A scaled physical model of the RM2 was then
+designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
+CACTUS predictions. Experimental performance measurements were significantly
+lower than the numerical results \cite{Hill2014}, which was assumed to be caused
+by the physical model's low Reynolds number
 \begin{equation}
@@
 where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
-kinematic viscosity. The Froude number is defined as
-\begin{equation}
-Fr = \frac{U}{\sqrt{gL}},
-\label{eq:Fr}
-\end{equation}
-where $g$ is the gravitational acceleration, and the tip speed ratio is defined
-as
+kinematic viscosity.
+
+As a cross-flow turbine, the RM2 blades experience large variations in angles of
+attack as they rotate about their axis (``cross-flow turbine'' means the axis of
+rotation is perpendicular to flow direction---either vertically or
+horizontally). These variations become larger as the tip speed ratio
 \begin{equation}
@@
 \end{equation}
-where $\omega$ and $R$ are the rotor angular velocity and radius.
-For hydrokinetic turbine testing, $Re$, not $Fr$, is the dominant scaling
-parameter. However, the Froude number (based on blade tip submergence) should
-remain small (significantly below one). It is rare to achieve perfect similitude
-for $Re$, but a threshold value should be exceeded, such that scale model
-results can be extrapolated.
-
-As a cross-flow turbine, the RM2 blades will experience large variations in
-angles of attack as they rotate about their axis (``cross-flow turbine'' means
-the axis of rotation is perpendicular to flow direction---either vertically or
-horizontally). These variations become larger as the tip speed ratio decreases
+where $\omega$ and $R$ are the rotor angular velocity and radius, decreases
 \cite{Para2002}. Typically, the maximum angles of attack are sufficiently large

### 2015-09-11 paper.tex
Add blank line
Clarify chord Reynolds number def

@@
 % For figure citations, please use "Fig." instead of "Figure".
+
 A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
@@
 \begin{tabular}{c|c|c|c|c}
-Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{ave}}$\\ 
+Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{mid}}$\\ 
 \hline 
@@
 
-\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade
-    chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ corresponding to various
-    tow speeds at $\lambda=3.1$.}
+\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
+    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at tip, root, and
+    mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
 
@@
     \includegraphics[width=\textwidth]{figures/perf_re_dep}
-\caption{{\bf Reynolds Number effects on performance.}
-Power and drag coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
+
+    \caption{{\bf Reynolds Number effects on performance.} Power and drag
+        coefficient at $\lambda=3.1$ plotted versus turbine diameter and approximate
+        average blade root chord Reynolds number.}
+
     \label{fig:cp-re-dep}

### 2015-09-11 paper.tex
Clarify chord location

@@
 \caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
-    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at tip, root, and
-    mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
+    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at blade tip, root,
+    and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
 

### 2015-09-11 paper.tex
Totals --> weighted averages

@@
 
-Totals for the transport terms in the mean kinetic energy equation---analyzed
-identically to \cite{Bachant2015-JoT}---are shown in Fig.~\ref{fig:Ktransport}.
-Due to the weaker blade vortex shedding, we see transport due to vertical
-advection at this point in the wake is approximately 3 times lower than the
-higher solidity UNH-RVAT. Note that direct comparison is somewhat invalid, since
-the total measurement plane area is about 5\% lower for this experiment.
-However, the differences observed are beyond this discrepancy. We also see
-relatively lower levels of cross-stream turbulent transport thanks to the lack
-of blade stall vortex shedding. These results may have interesting implications
-regarding the application of turbines with lower power coefficient to possibly
-improve overall array performance through enhanced transport of kinetic energy
-from the free stream, though a detailed anaylsis of the downstream evolution and
-turbine interaction will be necessary.
+Weighted averages for the transport terms in the mean kinetic energy
+equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
+Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
+transport due to vertical advection at this point in the wake is approximately 3
+times lower than the higher solidity UNH-RVAT. Note that direct comparison is
+somewhat invalid, since the total measurement plane area is about 5\% lower for
+this experiment. However, the differences observed are beyond this discrepancy.
+We also see relatively lower levels of cross-stream turbulent transport thanks
+to the lack of blade stall vortex shedding. These results may have interesting
+implications regarding the application of turbines with lower power coefficient
+to possibly improve overall array performance through enhanced transport of
+kinetic energy from the free stream, though a detailed anaylsis of the
+downstream evolution and turbine interaction will be necessary.
 

### 2015-10-14 paper.tex
Write abstract; resolves #9

@@
 
-\listoftodos
-
 % Please keep the abstract below 300 words
@@
 
-\todo[inline]{Write abstract.}
+The mechanical power, total rotor drag, and near-wake properties of a 1:6 scale
+Reference Model 2 (RM2) were measured in a towing tank. Performance was measured
+at multiple Reynolds numbers by varying tow carriage speed, and weak linear
+$Re$-dependence was achieved at a turbine diameter Reynolds number $Re_D \approx
+10^6$. An optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the
+near wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
+turbulence, and mean kinetic energy transport mechanisms were compared and
+contrasted with results from a high solidity turbine acquired with the same test
+apparatus. Overall, lower levels of streamwise wake recovery were calculated for
+the RM2 rotor---a consequence of both the relatively low solidity and tapered
+blades. The effects of blade support strut drag on turbine performance were
+investigated by covering the rotor's NACA 0021 struts with cylinders. As
+expected, this modification drastically reduced rotor power coefficient. Strut
+drag was also measured for the NACA 0021 and cylindrical configurations with the
+blades removed. These measurements provide a comprehensive open dataset for
+validating numerical models' predictive capabilities for low solidity rotors.
 

### 2015-10-14 paper.tex
Add CFT to abstract
Properties --> flow
Minor introduction edit

@@
 
-The mechanical power, total rotor drag, and near-wake properties of a 1:6 scale
-Reference Model 2 (RM2) were measured in a towing tank. Performance was measured
-at multiple Reynolds numbers by varying tow carriage speed, and weak linear
-$Re$-dependence was achieved at a turbine diameter Reynolds number $Re_D \approx
-10^6$. An optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the
-near wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
-turbulence, and mean kinetic energy transport mechanisms were compared and
-contrasted with results from a high solidity turbine acquired with the same test
-apparatus. Overall, lower levels of streamwise wake recovery were calculated for
-the RM2 rotor---a consequence of both the relatively low solidity and tapered
-blades. The effects of blade support strut drag on turbine performance were
-investigated by covering the rotor's NACA 0021 struts with cylinders. As
-expected, this modification drastically reduced rotor power coefficient. Strut
-drag was also measured for the NACA 0021 and cylindrical configurations with the
-blades removed. These measurements provide a comprehensive open dataset for
-validating numerical models' predictive capabilities for low solidity rotors.
+The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
+Reference Model 2 (RM2) cross-flow turbine were measured in a towing tank.
+Performance was measured at multiple Reynolds numbers by varying tow carriage
+speed, and weak linear $Re$-dependence was achieved at a turbine diameter
+Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio $\lambda_0 =
+3.1$ was chosen, at which the near wake velocity was measured at 1 m
+$(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
+transport mechanisms were compared and contrasted with results from a high
+solidity turbine acquired with the same test apparatus. Overall, lower levels of
+streamwise wake recovery were calculated for the RM2 rotor---a consequence of
+both the relatively low solidity and tapered blades. The effects of blade
+support strut drag on turbine performance were investigated by covering the
+rotor's NACA 0021 struts with cylinders. As expected, this modification
+drastically reduced rotor power coefficient. Strut drag was also measured for
+the NACA 0021 and cylindrical configurations with the blades removed. These
+measurements provide a comprehensive open dataset for validating numerical
+models' predictive capabilities for low solidity rotors.
 
@@
 CACTUS predictions. Experimental performance measurements were significantly
-lower than the numerical results \cite{Hill2014}, which was assumed to be caused
-by the physical model's low Reynolds number
+lower than the numerical results \cite{Hill2014}, which was assumed to be a 
+result of the physical model's low Reynolds number
 \begin{equation}

### 2015-10-14 paper.tex
Add citation for dataset
Minor edits

@@
 physical model to provide data to help answer that question. This dataset is
-publicly available for both validation of CACTUS and other numerical models.
+publicly available for both validation of CACTUS and other numerical models
+\cite{Bachant2015-RM2-data}.
 
@@
 with the exception of the shaft diameter, which was scaled from the SAFL RM2
-shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
+model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
 which may aid in comparison of the results, though this was not a top priority.

### 2015-10-14 paper.tex
Mention the lower solidity to blame for weaker tip vortices; resolves #13
Add exp setup photo; resolves #5

@@
 downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
-sampling at 200 Hz. A drawing of the experimental setup is shown in
-Figure~\ref{fig:exp-setup}.
+sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
+Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
 
 \begin{figure}[h]
-\caption{Photos of the UNH towing tank and turbine test bed.} 
-\label{fig:tow-tank}
+    \centering
+
+    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}
+
+    \caption{\textbf{Experimental setup.} Photo of the UNH tow tank and
+        turbine test bed with RM2 installed.}
+
+    \label{fig:exp-setup-photo}
 \end{figure}
@@
     \centering
+
     \includegraphics[clip,trim=0.01in 0 0 0,
     width=\textwidth]{figures/tank_cross_section}
+
     \caption{{\bf Experimental setup.} Illustration of the experimental setup.}
+
     \label{fig:exp-setup}
@@
 blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
-vortex shedding are relatively weaker.
+vortex shedding are relatively weaker, which is likely an effect of the RM2's
+lower solidity and tapered blades.
 

### 2015-12-01 paper.tex
Add Budi's edits and comments

@@
 \label{eq:Re}
-\end{equation}
-where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
+\end{equation}\textbf{\textit{[why not go straight with defining ReD and ReC here, so it's also clear which U and L are used for each of these?]}}
+where $U$ is ?free-stream? velocity, $L$ is characteristic length scales (?blade-chord length?), and $\nu$ is the fluid
 kinematic viscosity.
@@
 \lambda=\frac{\omega R}{U_\infty},
-\end{equation}
+\end{equation}\textbf{\textit{[define Uinf. it looks like a list of notation at the end of the paper could help a alot]}}
 where $\omega$ and $R$ are the rotor angular velocity and radius, decreases
@@
 cross-flow turbine designs, since physical modeling at appropriate scales can be
-prohibitively expensive in the early stages of engineering. Furthermore,
-Navier--Stokes-based computational fluid dynamics (CFD) simulations require
-modeling in 3 dimensions, which generally necessitates high performance
-computing---a resource that is not commonly available, and more expensive.
+prohibitively expensive in the early stages of engineering.
 
@@
 A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
-parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
+parameters were scaled from the RM2 design report \cite{Barone2011},
 with the exception of the shaft diameter, which was scaled from the SAFL RM2
@@
 3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
-pictured in Figure~\ref{fig:tow-tank}. The turbine was mounted in a frame built
+pictured in Figure~\ref{fig:tow-tank}\textbf{\textit{[missing fig?]}}. The turbine was mounted in a frame built
 from NACA 0020 struts, attached to the tow carriage by four linear bearings,
-which transfer all streamwise force to a pair of S-beam load cells. The turbine
+which transfer all streamwise force to a pair of S-beam load cells \textbf{\textit{[need reference for each sensor - load cells, ADV, etc.]}}. The turbine
 shaft RPM was controlled by a servo motor system, which allowed prescription of
 the turbine tip speed ratio. The load torque was measured by an inline rotary
-torque transducer and a load cell mounted at a fixed distance from the servo
-motor, providing a redundant measurement. Turbine shaft angle was measured using
+torque transducer. A load cell mounted, mounted at a fixed distance from the servo
+motor, provides a redundant measurement. Turbine shaft angle was measured using
 the servo drive's emulated encoder output, set to $10^5$ counts per turbine
@@
 using a linear encoder with 10 $\mu$m resolution. All of these
-performance-related quantities were sampled as 2 kHz, while the tow tank's
-motion controller provided redundant measurements of the carriage speed and
-turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
+performance-related quantities were sampled at 2 kHz, while the tow tank's
+motion controller provided redundant measurements of the carriage speed \textbf{\textit{[need to say how well the agreement between these two measurements are and which one is used throughout the paper; else, remove one of these]}} turbine angular velocity sampled at 1 kHz.
+Turbine wake measurements at 1 meter
 downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
@@
     \caption{{\bf Experimental setup.} Illustration of the experimental setup.}
-
+    \textbf{\textit{[would be good to indicate the water surface with text of drawing ( e.g. a triangle and three lines]}}
     \label{fig:exp-setup}
@@
 performed to measure the shaft bearing friction torque and turbine mounting
-frame drag, respectively. Tare drag runs were performed for each tow speed in
-the experiment, for which the mean value was used in data processing. Tare
+frame drag, respectively \textbf{\textit{[explain the purpose of these measurements; how the final drag and torque data were compensated using the tare measurements]}}.
+Tare drag runs were performed for each tow speed in
+the experiment, for which the mean value was used in data processing\textbf{\textit{[describe how this was done - without blades but shaft?]}}. Tare
 torque runs were performed by rotating the turbine shaft (without blades) in air
@@
 
+\textbf{\textit{[The list below is too detailed for a journal paper - suggest to remove the list and leave only the citation]}}
 \begin{itemize}
@@
 
-For each tow, a relevant quasi-steady duration was selected, and then truncated
+For each tow, a relevant quasi-steady duration was selected \textbf{\textit{[need a discussion on how this is done and justified]}}, and then truncated
 to include a whole number of blade passages. Over this duration relevant
@@
 respectively. $C_P$ is shown to increase in general with $Re$, along with a
-reduction in the optimal tip speed ratio, due to stall delay. These effect
+reduction in the optimal tip speed ratio, due to stall delay \textbf{\textit{[need to explain what stall delay is]}}. These effect
 diminish with increasing $Re$, which is expected as the blade boundary layers
-transition from laminar to turbulent \cite{Lissaman1983,
+transition from laminar to turbulent \textbf{\textit{[I wonder if this is relevant, since all cases are already in well in the turbulent regime]}} \cite{Lissaman1983,
 Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
-effects, but vary much less dramatically from each other.
+effects, but vary much less dramatically from each other.\textbf{\textit{[Overall I think we need more discussion for Figs 5 & 6.
+For fig 5, maybe a discussion on stall delay and why Re independence is not achieve is sufficient.
+Fig 6, need to find something to say, e.g.
+(1)why the trends look like that, is this expected?
+(2)Why they don't differ much between each other.
+(3) mention that CD increases with ReD.
+]}}
 
@@
 Reynolds numbers.}
+
+\textbf{\textit{[This figure shows that we haven't achieved Re independence (close though).
+I am sure many others will notice this.
+Need to state why we couldn't go over Re = 1.3E6.
+I presume due to technical limitation.]}}
 \label{fig:cp-curves}
@@
 highlighted. We see that the power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$,
-beyond which there appears to be a small, linear, positive trend. The tendency
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
+beyond which there appears to be a small, linear, positive trend \textbf{\textit{[dCP/dRe seems to increase again for the two points: second and third highest Cp - any suggestion for the cause of this?
+On a second thought, I think it's more appropriate to plot Re Vs.
+max Cp here ( don't fix TSR to 3.1, but pick a value which gives max Cp]}} .
+The tendency
 of $C_P$ to continue increasing slightly could be an effect of lower virtual
-camber when compared to the strong $Re$-indepdendence of the higher $c/R$
+camber \textbf{\textit{[I think we need to elaborate more on this. On its own, this sentence sounds very speculative]}} when compared to the strong $Re$-independence of the higher $c/R$
 UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
@@
 vortex shedding are relatively weaker, which is likely an effect of the RM2's
-lower solidity and tapered blades.
+lower solidity and tapered blades.\textbf{\textit{[the last 2 sentences: it's difficult to understand this without knowing the UNH-RVAT.
+Suggest to add a discussion on the similarity & differences between RVAT and RM2 dimensions, testing, and add the mean velocity plot for RVAT side-by-side with the one for RM2.
+Need more details on how you see the effects of vortex shedding are weaker.]}}
 
@@
 Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
-$\lambda=3.1$.}
+$\lambda=3.1$.}\textbf{\textit{[is this looking downstream or upstream? may want to indicate the rotation direction of the downstream rotor side ( right or left)]}}
 \label{fig:meancontquiv}
@@
 Weighted averages for the transport terms in the mean kinetic energy
-equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
+equation---analyzed identically to \cite{Bachant2015-JoT}\textbf{\textit{[Although this has been written in the cited reference, I feel we need to discuss this so that at least readers understand the reason of doing this analysis]}}---are shown in
 Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
@@
 which makes streamlined struts much more important for low solidity turbines,
-given the inverse correlation between solidity and $\lambda_0$.
+given the inverse correlation between solidity and $\lambda_0$.\textbf{\textit{[need more to write here]}}
 

### 2015-12-01 paper.tex
Address Budi's first comment about Re definition

@@
 \begin{equation}
-Re_L = \frac{UL}{\nu},
+Re_D = \frac{U_\infty D}{\nu},
 \label{eq:Re}
-\end{equation}\textbf{\textit{[why not go straight with defining ReD and ReC here, so it's also clear which U and L are used for each of these?]}}
-where $U$ is ?free-stream? velocity, $L$ is characteristic length scales (?blade-chord length?), and $\nu$ is the fluid
-kinematic viscosity.
+\end{equation}
+where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter (note
+that in some cases the blade chord length $c$ is used as this length scale), and
+$\nu$ is the fluid kinematic viscosity.
 

### 2015-12-01 paper.tex
U_infty is defined in Re def
Fix broken fig reference and trim whitespace

@@
 \lambda=\frac{\omega R}{U_\infty},
-\end{equation}\textbf{\textit{[define Uinf. it looks like a list of notation at the end of the paper could help a alot]}}
+\end{equation}
 where $\omega$ and $R$ are the rotor angular velocity and radius, decreases
@@
 3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
-pictured in Figure~\ref{fig:tow-tank}\textbf{\textit{[missing fig?]}}. The turbine was mounted in a frame built
+pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
 from NACA 0020 struts, attached to the tow carriage by four linear bearings,

### 2015-12-01 paper.tex
Explain stall delay

@@
 respectively. $C_P$ is shown to increase in general with $Re$, along with a
-reduction in the optimal tip speed ratio, due to stall delay \textbf{\textit{[need to explain what stall delay is]}}. These effect
+reduction in the optimal tip speed ratio, due to the tendency of foils to stall at higher angles of attack at higher $Re$, and the higher angle of attack ranges seen by the blades at lower $\lambda$.
+These effects
 diminish with increasing $Re$, which is expected as the blade boundary layers

### 2015-12-02 paper.tex
Move sensor references comment to issue #23

@@
 from NACA 0020 struts, attached to the tow carriage by four linear bearings,
-which transfer all streamwise force to a pair of S-beam load cells \textbf{\textit{[need reference for each sensor - load cells, ADV, etc.]}}. The turbine
+which transfer all streamwise force to a pair of S-beam load cells. The turbine
 shaft RPM was controlled by a servo motor system, which allowed prescription of

### 2015-12-02 paper.tex
Move comment about torque trans/arm to issue #24

@@
 the turbine tip speed ratio. The load torque was measured by an inline rotary
-torque transducer. A load cell mounted, mounted at a fixed distance from the servo
-motor, provides a redundant measurement. Turbine shaft angle was measured using
-the servo drive's emulated encoder output, set to $10^5$ counts per turbine
-shaft revolution. Carriage speed, and therefore inflow velocity was measured
-using a linear encoder with 10 $\mu$m resolution. All of these
+torque transducer. A load cell mounted, mounted at a fixed distance from the
+servo motor, provides a redundant measurement. Turbine shaft angle was measured
+using the servo drive's emulated encoder output, set to $10^5$ counts per
+turbine shaft revolution. Carriage speed, and therefore inflow velocity was
+measured using a linear encoder with 10 $\mu$m resolution. All of these
 performance-related quantities were sampled at 2 kHz, while the tow tank's
-motion controller provided redundant measurements of the carriage speed \textbf{\textit{[need to say how well the agreement between these two measurements are and which one is used throughout the paper; else, remove one of these]}} turbine angular velocity sampled at 1 kHz.
-Turbine wake measurements at 1 meter
+motion controller provided redundant measurements of the carriage speed turbine
+angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
 downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,

### 2015-12-02 paper.tex
Move comment to issue #17
Address Budi's comments on tare measurements

@@
     \caption{{\bf Experimental setup.} Illustration of the experimental setup.}
-    \textbf{\textit{[would be good to indicate the water surface with text of drawing ( e.g. a triangle and three lines]}}
+
     \label{fig:exp-setup}
@@
 
-\paragraph{Tare drag and torque compensation.} Tare torque and drag runs were
-performed to measure the shaft bearing friction torque and turbine mounting
-frame drag, respectively \textbf{\textit{[explain the purpose of these measurements; how the final drag and torque data were compensated using the tare measurements]}}.
-Tare drag runs were performed for each tow speed in
-the experiment, for which the mean value was used in data processing\textbf{\textit{[describe how this was done - without blades but shaft?]}}. Tare
-torque runs were performed by rotating the turbine shaft (without blades) in air
-at constant angular velocity for a specified duration, over the range of angular
-velocities used throughout the experiment. Tare torque was fit with a linear
-regression versus shaft angular velocity, and added to the measured turbine
-torque in post-processing.
+\paragraph{Tare drag and torque compensation.} To best estimate the hydrodynamic
+loads on the turbine rotor alone, tare torque and drag runs were performed to
+measure the shaft bearing friction torque and turbine mounting frame drag,
+respectively. Tare drag runs---measured with the turbine removed---were
+performed for each tow speed in the experiment, for which the mean value was
+subtracted in data processing, to arrive at an estimate for drag on the turbine
+alone. Tare torque runs were performed by rotating the turbine shaft (without
+blades) in air at constant angular velocity for a specified duration, over the
+range of angular velocities used throughout the experiment. Tare torque was fit
+with a linear regression versus shaft angular velocity, and added to the
+measured turbine torque in post-processing.
 

### 2015-12-02 paper.tex
Describe how steady duration is found

@@
 
-For each tow, a relevant quasi-steady duration was selected \textbf{\textit{[need a discussion on how this is done and justified]}}, and then truncated
-to include a whole number of blade passages. Over this duration relevant
-statistics are calculated.
+For each tow speed, a relevant quasi-steady duration was selected by manually
+inspecting a plot of the $C_P$ time series, and then truncated to include a
+whole number of blade passages. Over this duration relevant statistics are
+calculated.
 

### 2015-12-02 paper.tex
Clarify the role of blade BL transition

@@
 diminish with increasing $Re$, which is expected as the blade boundary layers
-transition from laminar to turbulent \textbf{\textit{[I wonder if this is relevant, since all cases are already in well in the turbulent regime]}} \cite{Lissaman1983,
+transition to turbulence closer to the leading edge \cite{Lissaman1983,
 Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar

### 2015-12-02 paper.tex
Move comment to issue #25

@@
 respectively. $C_P$ is shown to increase in general with $Re$, along with a
-reduction in the optimal tip speed ratio, due to the tendency of foils to stall at higher angles of attack at higher $Re$, and the higher angle of attack ranges seen by the blades at lower $\lambda$.
-These effects
-diminish with increasing $Re$, which is expected as the blade boundary layers
-transition to turbulence closer to the leading edge \cite{Lissaman1983,
-Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
-effects, but vary much less dramatically from each other.\textbf{\textit{[Overall I think we need more discussion for Figs 5 & 6.
-For fig 5, maybe a discussion on stall delay and why Re independence is not achieve is sufficient.
-Fig 6, need to find something to say, e.g.
-(1)why the trends look like that, is this expected?
-(2)Why they don't differ much between each other.
-(3) mention that CD increases with ReD.
-]}}
+reduction in the optimal tip speed ratio, due to the tendency of foils to stall
+at higher angles of attack at higher $Re$, and the higher angle of attack ranges
+seen by the blades at lower $\lambda$. These effects diminish with increasing
+$Re$, which is expected as the blade boundary layers transition to turbulence
+closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}. The
+rotor drag coefficient curves show similar effects, but vary much less
+dramatically from each other.
 

### 2015-12-02 paper.tex
Move comment to issue #26

@@
 Reynolds numbers.}
-
-\textbf{\textit{[This figure shows that we haven't achieved Re independence (close though).
-I am sure many others will notice this.
-Need to state why we couldn't go over Re = 1.3E6.
-I presume due to technical limitation.]}}
 \label{fig:cp-curves}
@@
 dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
-beyond which there appears to be a small, linear, positive trend \textbf{\textit{[dCP/dRe seems to increase again for the two points: second and third highest Cp - any suggestion for the cause of this?
-On a second thought, I think it's more appropriate to plot Re Vs.
-max Cp here ( don't fix TSR to 3.1, but pick a value which gives max Cp]}} .
-The tendency
+beyond which there appears to be a small, linear, positive trend. The tendency
 of $C_P$ to continue increasing slightly could be an effect of lower virtual

### 2015-12-02 paper.tex
Move comment to issue #26

@@
 highlighted. We see that the power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
-beyond which there appears to be a small, linear, positive trend. The tendency
-of $C_P$ to continue increasing slightly could be an effect of lower virtual
-camber \textbf{\textit{[I think we need to elaborate more on this. On its own, this sentence sounds very speculative]}} when compared to the strong $Re$-independence of the higher $c/R$
-UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$
+\textbf{\textit{[define Rec]}}, beyond which there appears to be a small,
+linear, positive trend. The tendency of $C_P$ to continue increasing slightly
+could be an effect of lower virtual camber when compared to the strong
+$Re$-independence of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
 

### 2015-12-02 paper.tex
Move comment to issue #28

@@
 vortex shedding are relatively weaker, which is likely an effect of the RM2's
-lower solidity and tapered blades.\textbf{\textit{[the last 2 sentences: it's difficult to understand this without knowing the UNH-RVAT.
-Suggest to add a discussion on the similarity & differences between RVAT and RM2 dimensions, testing, and add the mean velocity plot for RVAT side-by-side with the one for RM2.
-Need more details on how you see the effects of vortex shedding are weaker.]}}
+lower solidity and tapered blades.
 

### 2015-12-02 paper.tex
Comment on turbine orientation in mean velocity fig

@@
     \includegraphics[width=\textwidth]{figures/meancontquiv}
-\caption{{\bf Mean Velocity.}
-Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
-$\lambda=3.1$.}\textbf{\textit{[is this looking downstream or upstream? may want to indicate the rotation direction of the downstream rotor side ( right or left)]}}
+
+    \caption{{\bf Mean Velocity.}Mean velocity field (looking upstream) at 1 m
+    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
+    Fig.~\ref{fig:coordinates} for turbine axis orientation.}
+
     \label{fig:meancontquiv}

### 2015-12-02 paper.tex
More comments in figure captions re turbine orientation

@@
 
-    \caption{{\bf Mean Velocity.}Mean velocity field (looking upstream) at 1 m
+    \caption{{\bf Mean Velocity.} Mean velocity field (looking upstream) at 1 m
     downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
-    Fig.~\ref{fig:coordinates} for turbine axis orientation.}
+    Fig.~\ref{fig:coordinates} for turbine axis orientation. Solid dark gray
+    lines indicate turbine frontal area.}
 
@@
     \includegraphics[width=\textwidth]{figures/k_contours}
-\caption{{\bf Turbulence Kinetic Energy.}
-Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
-$\lambda=3.1$.}
+
+    \caption{{\bf Turbulence Kinetic Energy.} Turbulence kinetic energy (looking
+    upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
+    $\lambda=3.1$. Solid black lines indicate turbine frontal area.}
+
     \label{fig:kcont}

### 2015-12-02 paper.tex
Move comment to issue #6

@@
 Weighted averages for the transport terms in the mean kinetic energy
-equation---analyzed identically to \cite{Bachant2015-JoT}\textbf{\textit{[Although this has been written in the cited reference, I feel we need to discuss this so that at least readers understand the reason of doing this analysis]}}---are shown in
+equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
 Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see

### 2015-12-02 paper.tex
Comment already existing as issue #7

@@
 which makes streamlined struts much more important for low solidity turbines,
-given the inverse correlation between solidity and $\lambda_0$.\textbf{\textit{[need more to write here]}}
+given the inverse correlation between solidity and $\lambda_0$.
 

### 2015-12-02 paper.tex
Define chord-based Re

@@
 highlighted. We see that the power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$
-\textbf{\textit{[define Rec]}}, beyond which there appears to be a small,
-linear, positive trend. The tendency of $C_P$ to continue increasing slightly
-could be an effect of lower virtual camber when compared to the strong
-$Re$-independence of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda c U_\infty/
+\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
+positive trend. The tendency of $C_P$ to continue increasing slightly could be
+an effect of lower virtual camber when compared to the strong $Re$-independence
+of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
 

### 2015-12-02 paper.tex
Consistency in Re_c definition

@@
 \caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
-    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at blade tip, root,
-    and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
+blade chord Reynolds numbers $Re_c \equiv \lambda U_\infty c / \nu$ at blade
+tip, root, and mid-span, corresponding to various tow speeds at $\lambda=3.1$.}
 
@@
 highlighted. We see that the power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda c U_\infty/
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
 \nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,

### 2015-12-02 paper.tex
Discuss lack of Re-independence; resolves #26

@@
 $Re$, which is expected as the blade boundary layers transition to turbulence
-closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}. The
-rotor drag coefficient curves show similar effects, but vary much less
-dramatically from each other.
+closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}.
+
+Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
+not collapse exactly onto each other. Note that the data collection was limited
+at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
+the tow carriage drive belt. In contrast to the power coefficient data, the
+rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge 0.6
+\times 10^6$.
 

### 2015-12-03 paper.tex
Reformat figure syntax and use file extensions
More figure and equation syntax cleanup
Add uncertainty analysis section from test plan report

@@
 \begin{figure}[h]
-\includegraphics[width=0.65\textwidth]{figures/turbine}
-\caption{{\bf Turbine Model.}
-A drawing of the turbine model.}
+    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
+
+    \caption{{\bf Turbine Model.} A drawing of the turbine model.}
+
     \label{fig:turbine-drawing}
@@
 
-    \caption{\textbf{Experimental setup.} Photo of the UNH tow tank and
-        turbine test bed with RM2 installed.}
+    \caption{\textbf{Experimental setup.} Photo of the UNH tow tank and turbine
+    test bed with RM2 installed.}
 
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/turbine_coordinate_system}
+    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
+
     \caption{{\bf Coordinate system.} Wake measurement coordinate system and
     cross-stream/vertical coordinates. All dimensions are in meters.}
+
     \label{fig:coordinates}
 \end{figure}
+
+\subsection*{Uncertainty Analysis}
+
+Uncertainty was considered from a combination of systematic
+and random errors. The random error was inferred from the sample standard
+deviation and the systematic from the sensor calibrations or datasheets.
+Combining both sources of error, along with their propagation into quantities
+derived from multiple measurements, followed the procedures outlined in
+Coleman and Steele (2009) \cite{ColemanSteele}, described below.
+
+An expanded uncertainty interval with 95\% confidence was computed for
+$\lambda$, $C_P$, and $C_D$
+\begin{equation}
+    U_{95} = t_{95} u_c,
+\end{equation}
+where $t_{95}$ is the value from the Student-$t$ distribution for a 95\%
+confidence interval and $u_c$ is the combined standard uncertainty. Combined
+standard uncertainty for a given quantity $X$ is calculated by
+\begin{equation}
+    u_X^2 = s_X^2 + b_X^2,
+\end{equation}
+where $s_X$ is the sample standard deviation, calculated as the standard
+deviation of the mean per turbine revolution, and $b_X$ is the systematic
+uncertainty, computed by
+\begin{equation}
+    b_{X}^2 = \sum_{i=1}^J \left( \frac{\partial X}{\partial x_i} \right)^2
+    b_{x_i}^2,
+\end{equation}
+where $x_i$ is a primitive quantity used to calculate $X$ (e.g. $T$, $\omega$,
+and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
+systematic uncertainty, estimated as half the value listed in
+Table~\ref{tab-sensors}.
+
+Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which can
+be obtained using the Welch--Satterthwaite formula
+\begin{equation}
+    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
+        \sum_{k=1}^M b_k^4/\nu_{b_k}},
+\end{equation}
+where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
+$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
+$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
+samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
+\begin{equation}
+    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
+\end{equation}
+where the quantity in parentheses is the relative uncertainty of $b_k$.
+
+From previous measurements of a similarly-sized vertical-axis turbine with the
+same experimental setup, we expect expanded uncertainties for $\lambda$, $C_P$,
+and $C_D$ to be approximately 0.008, 0.01, and 0.02, respectively, at a tow
+speed $U_\infty = 1.0$ m/s. These values are well within the discrepancies
+between previous measurements and predictions by CACTUS \cite{Michelen2014},
+making the data from the experiments described here suitable for model validation.
 
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/cp_curves}
-\caption{{\bf Power Coefficient Curves.}
-Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
-Reynolds numbers.}
+    \includegraphics[width=\textwidth]{figures/cp_curves.eps}
+
+    \caption{{\bf Power Coefficient Curves.} Mean rotor power coefficient
+    plotted versus mean tip speed ratio for multiple Reynolds numbers.}
+
     \label{fig:cp-curves}
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figures/cd_curves}
-\caption{{\bf Drag Coefficient Curves.}
-Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
-Reynolds numbers.}
+    \includegraphics[width=\textwidth]{figures/cd_curves.eps}
+
+    \caption{{\bf Drag Coefficient Curves.} Mean rotor drag coefficient plotted
+    versus mean tip speed ratio for multiple Reynolds numbers.}
+
     \label{fig:cd-curves}
@@
 \begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/perf_re_dep}
+    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
 
@@
 \begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/meancontquiv}
+    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
 
@@
 \begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/k_contours}
+    \includegraphics[width=\textwidth]{figures/k_contours.eps}
 
@@
 \begin{figure}[ht!]
-\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
+    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
 
     \caption{{\bf Mean Kinetic Energy Transport.} Weighted average estimates for
-    terms contributing to streamwise recovery of mean kinetic energy, multiplied by
-    two due to implied symmetry.}
+    terms contributing to streamwise recovery of mean kinetic energy, multiplied
+    by two due to implied symmetry.}
 
@@
 \begin{figure}[ht!]
-\includegraphics[width=\textwidth]{figures/no_blades_all}
-\caption{{\bf Strut drag losses.}
-Measurements of the strut drag losses for (a) NACA 0021 and (b) cylindrical
-struts, both stationary and towed.}
+    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
+
+    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
+    (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}
+
     \label{fig:no-blades}
@@
 \begin{figure}[ht!]
-\includegraphics[width=\textwidth]{figures/perf_covers}
-\caption{{\bf High drag strut performance.}
-Turbine performance and rotor drag coefficient curves with both NACA 0021
-and cylindrical struts.}
+    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
+
+    \caption{{\bf High drag strut performance.} Turbine performance and rotor
+    drag coefficient curves with both NACA 0021 and cylindrical struts.}
+
     \label{fig:perf-covers}

### 2015-12-03 paper.tex
Change to past tense
Test matrix section names and descriptions are now in the exp repo README; resolves #21

@@
 ``sections,'' in which typically a single independent variable was varied. Test
-matrix section names and descriptions are given below, which outline the
-experimental data and code repository \cite{Bachant2015-RM2-data}.
-
-\textbf{\textit{[The list below is too detailed for a journal paper - suggest to remove the list and leave only the citation]}}
-\begin{itemize}
-
-    \item \texttt{Perf-\{speed\}}: Performance curve at \texttt{\{speed\}} m/s
-    tow speed, performed for (0.4, 0.6, 0.8, 1.0, 1.2) m/s.
-
-    \item \texttt{Perf-\{speed\}-b}: Second performance curve at
-    \texttt{\{speed\}} m/s, performed for the same tow speeds as above for
-    reduced statistical uncertainty.
-
-    \item \texttt{Perf-1.0-covers}: Performance curve at 1.0 m/s tow speed with
-    cylindrical strut covers.
-
-    \item \texttt{Perf-1.0-no-blades-covers}: Performance curve at 1.0 m/s with
-    no blades and cylindrical strut covers.
-
-    \item \texttt{Perf-1.0-no-blades}: Performance curve at 1.0 m/s with no
-    blades (NACA 0021 struts only).
-
-    \item \texttt{Perf-tsr\_0}: Performance at $\lambda=3.1$ for multiple tow
-    speeds.
-
-    \item \texttt{Perf-tsr\_0-b}: Additional set of runs duplicating the
-    \texttt{Perf-tsr\_0} parameters.
-
-    \item \texttt{Strut-torque-covers}: Measuring parasitic torque from
-    cylindrical struts without towing.
-
-    \item \texttt{Strut-torque}: Measuring parasitic torque from
-    NACA 0021 struts without towing.
-
-    \item \texttt{Tare-drag}: Drag on the turbine frame measured with the turbine
-    removed.
-
-    \item \texttt{Tare-torque}: Measurements of friction torque in shaft
-    bearings for a range of RPMs used in the experiments.
-
-    \item \texttt{Wake-\{speed\}-\{z/H\}}: Cross-stream wake profile at 1 m
-    downstream ($x/D=0.93$), $\lambda=3.1$, \texttt{\{speed\}} m/s tow speed,
-    and \texttt{\{z/H\}} vertical location.
-\end{itemize}
+matrix section names and descriptions are provided in the \texttt{README.md}
+file of the experimental data and code repository \cite{Bachant2015-RM2-data}.
 
@@
 
-Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which can
-be obtained using the Welch--Satterthwaite formula
+Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
+was obtained using the Welch--Satterthwaite formula
 \begin{equation}

### 2015-12-03 paper.tex
Reference the Reynolds number table
Discuss strut drag results and cite Rawlings thesis; resolves #22 and resolves #7

@@
 file of the experimental data and code repository \cite{Bachant2015-RM2-data}.
+Tow speed and their corresponding turbine diameter and blade chord Reynolds
+numbers are presented in Tab.~\ref{tab:re}.
 
@@
 
+Performance curves for the rotor with both NACA 0021 and cylindrical struts are
+shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
+struts reduce performance dramatically, which worsens as $\lambda$ increases.
+This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
+though the strut losses in this case are larger due to the very high drag profile.
+
+\begin{figure}[ht!]
+    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
+
+    \caption{{\bf High drag strut performance.} Turbine performance and rotor
+        drag coefficient curves with both NACA 0021 and cylindrical struts.}
+
+    \label{fig:perf-covers}
+\end{figure}
+
+Measurements for the power coefficient contributions of the strut drag losses
+are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
+struts---both in towed and stationary conditions. These are computed in the same
+fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the blades removed.
 We see that strut drag losses increase with tip speed ratio to the power 2--3,
 which makes streamlined struts much more important for low solidity turbines,
-given the inverse correlation between solidity and $\lambda_0$.
+given the inverse correlation between solidity and $\lambda_0$
+\cite{Templin1974}.
 
@@
 
-\begin{figure}[ht!]
-    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
-
-    \caption{{\bf High drag strut performance.} Turbine performance and rotor
-    drag coefficient curves with both NACA 0021 and cylindrical struts.}
-
-    \label{fig:perf-covers}
-\end{figure}
+Strut drag losses do not change much for the streamlined NACA 0021 struts in the
+towed versus stationary configuration. However, for the cylindrical struts,
+losses increase significantly when towed and operating in the mid range of tip
+speed ratios. With respect to numerical modeling, these measurements will allow
+support struts to be simulated without blades, to isolate and evaluate the
+ability to predict these losses independent of the blade loading.
 

### 2015-12-04 paper.tex
Add strut covers drawing; resolves #32

@@
     \label{fig:turbine-drawing}
+\end{figure}
+
+For investigating the effects of support strut drag losses, a set of cylindrical
+strut covers was designed to slip over the blades. Endcaps were also fabricated
+to allow the high drag strut cover configuration to be operated without blades.
+A drawing of the strut covers is shown in Fig.~\ref{fig:covers}.
+
+\begin{figure}[h]
+    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
+
+    \caption{{\bf Strut Covers.} A drawing of the high drag strut cover
+        configuration with and without blades.}
+
+    \label{fig:covers}
 \end{figure}

### 2016-01-15 paper.tex
Note that the turbine is a vertical-axis turbine

@@
 The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
-Reference Model 2 (RM2) cross-flow turbine were measured in a towing tank.
-Performance was measured at multiple Reynolds numbers by varying tow carriage
-speed, and weak linear $Re$-dependence was achieved at a turbine diameter
-Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio $\lambda_0 =
-3.1$ was chosen, at which the near wake velocity was measured at 1 m
-$(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
+Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured in a
+towing tank. Performance was measured at multiple Reynolds numbers by varying
+tow carriage speed, and weak linear $Re$-dependence was achieved at a turbine
+diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio
+$\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured at 1
+m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
 transport mechanisms were compared and contrasted with results from a high
@@
 marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
-Model 2 (RM2), a cross-flow turbine intended for river environments, was
-initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
-line code \cite{Murray2011}. A scaled physical model of the RM2 was then
-designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
-CACTUS predictions. Experimental performance measurements were significantly
-lower than the numerical results \cite{Hill2014}, which was assumed to be a
-result of the physical model's low Reynolds number
+Model 2 (RM2), a vertical-axis cross-flow turbine intended for river
+environments, was initially designed by Barone et al. \cite{Barone2011} using
+the CACTUS vortex line code \cite{Murray2011}. A scaled physical model of the
+RM2 was then designed and built by the Saint Anthony Falls Laboratory (SAFL) to
+validate the CACTUS predictions. Experimental performance measurements were
+significantly lower than the numerical results \cite{Hill2014}, which was
+assumed to be a result of the physical model's low Reynolds number
 \begin{equation}

### 2016-01-15 paper.tex
Remove awkward comma per @wosnik
For --> of

@@
 rotation is perpendicular to flow direction---either vertically or
-horizontally). These variations become larger as the tip speed ratio
+horizontally). These variations become larger at lower tip speed ratio
 \begin{equation}
@@
 \end{equation}
-where $\omega$ and $R$ are the rotor angular velocity and radius, decreases
+where $\omega$ and $R$ are the rotor angular velocity and radius
 \cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
@@
 Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
-expressed in terms of tip speed ratio, the optimal value for which is a function
+expressed in terms of tip speed ratio, the optimal value of which is a function
 of solidity). If numerical models are validated with physical model data that

### 2016-01-15 paper.tex
Add lambda symbol

@@
 Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
-expressed in terms of tip speed ratio, the optimal value of which is a function
-of solidity). If numerical models are validated with physical model data that
-was obtained at insufficiently high Reynolds numbers, it cannot be determined
-whether problems with model predictions are caused by Reynolds number effects,
-issues related to higher solidity, or both. It is uncertain whether numerical
-models validated with physical model data obtained at low Reynolds number should
-be considered validated at all, since the scale at which the model will be
-applied is orders of magnitude larger. One way to overcome this uncertainty is
-to show that the scaled physical model test has become Reynolds number
-independent, and therefore validation efforts should be relevant at full-scale.
+expressed in terms of tip speed ratio $\lambda$, the optimal value of which is a
+function of solidity). If numerical models are validated with physical model
+data that was obtained at insufficiently high Reynolds numbers, it cannot be
+determined whether problems with model predictions are caused by Reynolds number
+effects, issues related to higher solidity, or both. It is uncertain whether
+numerical models validated with physical model data obtained at low Reynolds
+number should be considered validated at all, since the scale at which the model
+will be applied is orders of magnitude larger. One way to overcome this
+uncertainty is to show that the scaled physical model test has become Reynolds
+number independent, and therefore validation efforts should be relevant at
+full-scale.
 

### 2016-01-15 paper.tex
Clean up CFT kinematics description as suggested by @wosnik

@@
 
-As a cross-flow turbine, the RM2 blades experience large variations in angles of
-attack as they rotate about their axis (``cross-flow turbine'' means the axis of
-rotation is perpendicular to flow direction---either vertically or
-horizontally). These variations become larger at lower tip speed ratio
+As a consequence of the inherently unsteady nature of the cross-flow rotor, the
+RM2 blades experience large variations in angles of attack as they rotate about
+their axis (``cross-flow'' means the axis of rotation is perpendicular to flow
+direction). These variations become larger at lower tip speed ratio
 \begin{equation}

### 2016-01-15 paper.tex
Max on C_P is a subscript rather than separated by comma

@@
 be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
-testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
+testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$,
 increased with Reynolds number, $Re_c$, along with a shift of the location of
-$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
-The effects of Reynolds number were quite dramatic over a relatively small range
-of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
+$C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
+effects of Reynolds number were quite dramatic over a relatively small range of
+$Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
 Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine

### 2016-01-15 paper.tex
Clarify that Bachant and Wosnik turbine was high solidity

@@
 $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
-Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine
-performance and near-wake characteristics become Reynolds number independent at
-$Re_c \approx 2 \times 10^5$.
+Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that performance and
+near-wake characteristics of a high solidity cross-flow turbine become Reynolds
+number independent at $Re_c \approx 2 \times 10^5$.
 

### 2016-01-16 paper.tex
Start line numbers from beginning; resolves #34
Clean up strut drag motivation

@@
 \begin{document}
+\linenumbers
 \vspace*{0.35in}
@@
 models' predictive capabilities for low solidity rotors.
-
-\linenumbers
 
@@
 turbine, but at higher Reynolds numbers than those achieved in the experiments
-at SAFL. It is also suspected that the strut drag model in CACTUS could be the
-source of some discrepancy. The strut drag was deliberately modified in the
-physical model to provide data to help answer that question. This dataset is
-publicly available for both validation of CACTUS and other numerical models
-\cite{Bachant2015-RM2-data}.
+at SAFL. It was suspected that the strut drag model in CACTUS could be the
+source of some discrepancy. Thus, the strut drag was deliberately and
+significantly increased in the physical model to provide data to help answer
+that question. This dataset is publicly available for both validation of CACTUS
+and other numerical models \cite{Bachant2015-RM2-data}.
 

### 2016-01-16 paper.tex
Built --> fabricated per @wosnik
Prescription --> precise control per @wosnik

@@
 
-A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
-parameters were scaled from the RM2 design report \cite{Barone2011},
+A 1:6 scale model of the RM2 rotor was designed and fabricated. Turbine
+geometric parameters were scaled from the RM2 design report \cite{Barone2011},
 with the exception of the shaft diameter, which was scaled from the SAFL RM2
@@
 which transfer all streamwise force to a pair of S-beam load cells. The turbine
-shaft RPM was controlled by a servo motor system, which allowed prescription of
-the turbine tip speed ratio. The load torque was measured by an inline rotary
+shaft RPM was controlled by a servo motor system, which allowed precise control
+of the turbine tip speed ratio. The load torque was measured by an inline rotary
 torque transducer. A load cell mounted, mounted at a fixed distance from the

### 2016-01-16 paper.tex
Remove duplicate word
Clean up strut covers description

@@
 For investigating the effects of support strut drag losses, a set of cylindrical
-strut covers was designed to slip over the blades. Endcaps were also fabricated
-to allow the high drag strut cover configuration to be operated without blades.
-A drawing of the strut covers is shown in Fig.~\ref{fig:covers}.
+covers were designed to slip over the struts, which provided a significant
+increase in strut drag. Endcaps were also fabricated to allow the high drag
+strut cover configuration to be operated without blades. A drawing of the strut
+covers is shown in Fig.~\ref{fig:covers}.
 
@@
 of the turbine tip speed ratio. The load torque was measured by an inline rotary
-torque transducer. A load cell mounted, mounted at a fixed distance from the
-servo motor, provides a redundant measurement. Turbine shaft angle was measured
-using the servo drive's emulated encoder output, set to $10^5$ counts per
-turbine shaft revolution. Carriage speed, and therefore inflow velocity was
-measured using a linear encoder with 10 $\mu$m resolution. All of these
-performance-related quantities were sampled at 2 kHz, while the tow tank's
-motion controller provided redundant measurements of the carriage speed turbine
-angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
-downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
-sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
+torque transducer. A load cell mounted at a fixed distance from the servo motor,
+provides a redundant measurement. Turbine shaft angle was measured using the
+servo drive's emulated encoder output, set to $10^5$ counts per turbine shaft
+revolution. Carriage speed, and therefore inflow velocity was measured using a
+linear encoder with 10 $\mu$m resolution. All of these performance-related
+quantities were sampled at 2 kHz, while the tow tank's motion controller
+provided redundant measurements of the carriage speed turbine angular velocity
+sampled at 1 kHz. Turbine wake measurements at 1 meter downstream were measured
+with a Nortek Vectrino+ acoustic Doppler velocimeter, sampling at 200 Hz. A
+photo and drawing of the experimental setup are shown in
 Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

### 2016-01-16 paper.tex
Clean up torque arm description
Minor edits to synchronization paragraph

@@
 of the turbine tip speed ratio. The load torque was measured by an inline rotary
-torque transducer. A load cell mounted at a fixed distance from the servo motor,
-provides a redundant measurement. Turbine shaft angle was measured using the
-servo drive's emulated encoder output, set to $10^5$ counts per turbine shaft
-revolution. Carriage speed, and therefore inflow velocity was measured using a
-linear encoder with 10 $\mu$m resolution. All of these performance-related
-quantities were sampled at 2 kHz, while the tow tank's motion controller
-provided redundant measurements of the carriage speed turbine angular velocity
-sampled at 1 kHz. Turbine wake measurements at 1 meter downstream were measured
-with a Nortek Vectrino+ acoustic Doppler velocimeter, sampling at 200 Hz. A
-photo and drawing of the experimental setup are shown in
+torque transducer. A load cell mounted at a fixed distance from the servo motor
+via a moment arm provided a redundant torque measurement. Turbine shaft angle
+was measured using the servo drive's emulated encoder output, set to $10^5$
+counts per turbine shaft revolution. Carriage speed, and therefore inflow
+velocity was measured using a linear encoder with 10 $\mu$m resolution. All of
+these performance-related quantities were sampled at 2 kHz, while the tow tank's
+motion controller provided redundant measurements of the carriage speed turbine
+angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
+downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
+sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
 Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
@@
 torque, drag, angular velocity), ensuring precise calculation of, e.g., power
-coefficient. Since there is also synchronization of the initial sample from each
-three subsystems, correlation of events in the performance and wake signals is
-also possible.
+coefficient. Since there was also synchronization of the initial sample from
+each of the three subsystems, correlation of events in the performance and wake
+signals is also possible.
 

### 2016-01-16 paper.tex
Mention blockage ratio and why it was not corrected for; resolves #36

@@
 3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
-pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
-from NACA 0020 struts, attached to the tow carriage by four linear bearings,
-which transfer all streamwise force to a pair of S-beam load cells. The turbine
-shaft RPM was controlled by a servo motor system, which allowed precise control
-of the turbine tip speed ratio. The load torque was measured by an inline rotary
-torque transducer. A load cell mounted at a fixed distance from the servo motor
-via a moment arm provided a redundant torque measurement. Turbine shaft angle
-was measured using the servo drive's emulated encoder output, set to $10^5$
-counts per turbine shaft revolution. Carriage speed, and therefore inflow
-velocity was measured using a linear encoder with 10 $\mu$m resolution. All of
-these performance-related quantities were sampled at 2 kHz, while the tow tank's
-motion controller provided redundant measurements of the carriage speed turbine
-angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
-downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
-sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
-Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
+pictured in Fig.~\ref{fig:exp-setup}. The blockage ratio based on the rotor
+frontal and tank cross-sectional area was 10\%. The turbine was mounted in a
+frame built from NACA 0020 struts, attached to the tow carriage by four linear
+bearings, which transfer all streamwise force to a pair of S-beam load cells.
+The turbine shaft RPM was controlled by a servo motor system, which allowed
+precise control of the turbine tip speed ratio. The load torque was measured by
+an inline rotary torque transducer. A load cell mounted at a fixed distance from
+the servo motor via a moment arm provided a redundant torque measurement.
+Turbine shaft angle was measured using the servo drive's emulated encoder
+output, set to $10^5$ counts per turbine shaft revolution. Carriage speed, and
+therefore inflow velocity was measured using a linear encoder with 10 $\mu$m
+resolution. All of these performance-related quantities were sampled at 2 kHz,
+while the tow tank's motion controller provided redundant measurements of the
+carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
+measurements at 1 meter downstream were measured with a Nortek Vectrino+
+acoustic Doppler velocimeter, sampling at 200 Hz. A photo and drawing of the
+experimental setup are shown in Fig.~\ref{fig:exp-setup-photo} and
+Fig.~\ref{fig:exp-setup}, respectively.
 
@@
 calculated.
+
+Since the blockage ratio was relatively low (10\%), and a definitive blockage
+correction for cross-flow turbines has not been established \cite{Cavagnaro2014}
+blockage effects were not corrected for. Furthermore, most numerical modeling
+efforts can easily incorporate finite domains, meaning blockage corrections
+could create an additional variable to obfuscate validation efforts.
 

### 2016-01-16 paper.tex
Shorten title; towards #37

@@
 
-{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
-cross-flow hydrokinetic turbine at transitional Reynolds numbers: Power production,
-near-wake dynamics, and blade support strut losses}}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include
+{\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
+        turbine at transitional Reynolds numbers: Power production, near-wake dynamics,
+        and blade support strut losses}} \newline
+% Insert author names, affiliations
+% and corresponding author email (do not
+% include
 % titles, positions, or degrees).
-\\
-Peter Bachant\textsuperscript{1,*},
-Martin Wosnik\textsuperscript{1},
-Budi Gunawan\textsuperscript{2},
-Vincent Neary\textsuperscript{2}
-\\
-\bigskip
-\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH,
-USA
-\\
-\bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque, NM, USA
-\\
-\bigskip
+\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
+Gunawan\textsuperscript{2}, Vincent Neary\textsuperscript{2} \\ \bigskip \bf{1}
+Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, USA
+\\ \bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque,
+NM, USA \\ \bigskip
 

### 2016-01-16 paper.tex
Add Vince's middle inital and Sandia's full address; fixes #40 and fixes #41

@@
         turbine at transitional Reynolds numbers: Power production, near-wake dynamics,
-        and blade support strut losses}} \newline
-% Insert author names, affiliations
+        and blade support strut losses}} \newline % Insert author names, affiliations
 % and corresponding author email (do not
@@
 \\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
-Gunawan\textsuperscript{2}, Vincent Neary\textsuperscript{2} \\ \bigskip \bf{1}
+Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip \bf{1}
 Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, USA
-\\ \bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque,
-NM, USA \\ \bigskip
+\\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O. Box 5800,
+Albuquerque, New Mexico 87185-MS1124 \\ \bigskip
 

### 2016-01-16 paper.tex
Shorten title a bit more; towards #37

@@
 {\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
-        turbine at transitional Reynolds numbers: Power production, near-wake dynamics,
-        and blade support strut losses}} \newline % Insert author names, affiliations
+        turbine at transitional Reynolds numbers: Power production, strut losses, and
+        near-wake dynamics}} \newline % Insert author names, affiliations
 % and corresponding author email (do not
@@
 \\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
-Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip \bf{1}
-Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, USA
-\\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O. Box 5800,
-Albuquerque, New Mexico 87185-MS1124 \\ \bigskip
+Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
+\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
+NH, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
+Box 5800, Albuquerque, New Mexico 87185-MS1124 \\ \bigskip
 

### 2016-01-16 getfigs.py
Copy figures from local submodule repo

@@ -1,24 +1,20 @@
 #!/usr/bin/env python
-"""
-This script copies figures from the RM2 tow tank
-experiment directory.
-"""
+"""This script copies figures from the RM2 tow tank experiment directory."""
 
 import os
 import sys
 import shutil
 
-figdir = os.path.join(os.path.expanduser("~"), "Research",
-        "Experiments", "RM2 tow tank", "Figures")
+figdir = os.path.join("RM2-tow-tank", "Figures")
 
 figlist = ["cp_curves.eps",
            "cd_curves.eps",
            "perf_re_dep.eps",
-	   "meancontquiv.eps",
-	   "k_contours.eps",
-	   "K_trans_bar_graph.eps",
-	   "no_blades_all.eps",
-	   "perf_covers.eps"]
+    	   "meancontquiv.eps",
+           "k_contours.eps",
+    	   "K_trans_bar_graph.eps",
+    	   "no_blades_all.eps",
+    	   "perf_covers.eps"]
 
 for fig in figlist:
     shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))

### 2016-01-16 getbib.py
Minor cleanup in getbib.py

@@ -1,7 +1,5 @@
 #!/usr/bin/env python
-"""
-This script copies my personal BibTeX file to the current directory.
-"""
+"""This script copies my personal BibTeX file to the current directory."""
 
 import os
 import shutil
@@ -15,7 +13,7 @@ else:
 bibpath = os.path.join(os.path.expanduser("~"), "Google Drive",
                        "Library", "Library.bib")
 biburl = "https://raw.githubusercontent.com/petebachant/Library/master/Library.bib"
-                       
+
 try:
     shutil.copy2(bibpath, "library.bib")
 except FileNotFoundError:

### 2016-01-16 scripts/makefigs.sh
Create scripts dir

@@ -1,0 +1,5 @@
+#!/usr/bin/env bash
+
+cd RM2-tow-tank
+python plot.py --all --save --noshow
+

### 2016-01-17 scripts/makefigs.sh
Whitespace

@@ -2,4 +2,3 @@
 
 cd RM2-tow-tank
 python plot.py --all --save --noshow
-

### 2016-01-17 scripts/cleanfigs.sh
Add script to clean figures

@@ -1,0 +1,4 @@
+#!/usr/bin/env bash
+# Clean all intermediate converted figures
+
+rm figures/*-converted-to.*

### 2016-01-17 scripts/makefigs.sh
Copy new figures in makefigs.sh

@@ -2,3 +2,5 @@
 
 cd RM2-tow-tank
 python plot.py --all --save --noshow
+cd ..
+python scripts/getfigs.py

### 2016-01-17 paper.tex
Add table of sensors

@@
 
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{c|c|c|c}
+        Measured quantity & Device type & Mfg. \& model & Nominal accuracy \\
+        \hline 
+        Carriage position & Linear encoder & Renishaw LM15 & 10 $\mu$m/pulse \cite{RenishawLM15}\\
+        Turbine angle & Servo encoder output & Kollmorgen AKD & 10$^5$ pulse/rev \cite{KollmorgenAKD}\\
+        Turbine torque & Rotary transducer & Interface T8-200 & $\pm$0.5 Nm \cite{InterfaceT8}\\ 
+        Turbine torque (2) & Load cell (\& arm) & Sentran ZB3-200 & $\pm$0.2 Nm \cite{SentranZB}\\
+        Drag force, left & Load cell & Sentran ZB3-500 & $\pm$0.6 N \cite{SentranZB}\\
+        Drag force, right & Load cell & Sentran ZB3-500 & $\pm$0.6 N \cite{SentranZB}\\
+        Fluid velocity & ADV & Nortek Vectrino+ & $\pm$0.5\% $\pm$1 mm/s \cite{NortekVectrino}\\
+    \end{tabular}
+    \caption{Details of the sensors used in the experiment. Note that ``(2)''
+        denotes a secondary redundant measurement. ``Turbine torque (2)'' nominal
+        accuracy was estimated by combining load cell accuracy and arm machining
+        tolerances ($\pm 1 \times 10^{-4}$ m) as root-sum-square.}
+    \label{tab:sensors}
+\end{table}
+
 \paragraph{Synchronization.} The three data acquisition instrumentation
@@
 
-Uncertainty was considered from a combination of systematic
-and random errors. The random error was inferred from the sample standard
-deviation and the systematic from the sensor calibrations or datasheets.
-Combining both sources of error, along with their propagation into quantities
-derived from multiple measurements, followed the procedures outlined in
-Coleman and Steele (2009) \cite{ColemanSteele}, described below.
+Uncertainty was considered from a combination of systematic and random errors.
+The random error was inferred from the sample standard deviation and the
+systematic error from the sensor calibrations or datasheets. Combining both
+sources of error, along with their propagation into quantities derived from
+multiple measurements, followed the procedures outlined in Coleman and Steele
+(2009) \cite{ColemanSteele}, described below.
 

### 2016-01-17 paper.tex
Replace table with inline references for sensors

--- 2016-01-16 paper.tex
@@
 frame built from NACA 0020 struts, attached to the tow carriage by four linear
-bearings, which transfer all streamwise force to a pair of S-beam load cells.
-The turbine shaft RPM was controlled by a servo motor system, which allowed
-precise control of the turbine tip speed ratio. The load torque was measured by
-an inline rotary torque transducer. A load cell mounted at a fixed distance from
-the servo motor via a moment arm provided a redundant torque measurement.
-Turbine shaft angle was measured using the servo drive's emulated encoder
-output, set to $10^5$ counts per turbine shaft revolution. Carriage speed, and
-therefore inflow velocity was measured using a linear encoder with 10 $\mu$m
-resolution. All of these performance-related quantities were sampled at 2 kHz,
-while the tow tank's motion controller provided redundant measurements of the
-carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
+bearings, which transfer all streamwise force to a pair of Sentran ZB S-beam
+load cells \cite{SentranZB}. The turbine shaft RPM was controlled by a servo
+motor system, which allowed precise control of the turbine tip speed ratio. The
+load torque was measured by an Interface T8 200 Nm capacity inline rotary torque
+transducer \cite{InterfaceT8}. An additional Sentran ZB load cell mounted at a
+fixed distance from the servo motor via a moment arm provided a redundant torque
+measurement. Turbine shaft angle was measured using the Kollmorgen AKD servo
+drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
+turbine shaft revolution. Carriage speed, and therefore inflow velocity was
+measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
+\cite{RenishawLM15}. All of these performance-related quantities were sampled at
+2 kHz, while the tow tank's motion controller provided redundant measurements of
+the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
 measurements at 1 meter downstream were measured with a Nortek Vectrino+
-acoustic Doppler velocimeter, sampling at 200 Hz. A photo and drawing of the
-experimental setup are shown in Fig.~\ref{fig:exp-setup-photo} and
-Fig.~\ref{fig:exp-setup}, respectively.
+acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
+and drawing of the experimental setup are shown in
+Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
 

### 2016-01-17 paper.tex
Add uncertainty formulas adapted from RVAT-Re-dep paper

@@
 
-Uncertainty was considered from a combination of systematic and random errors.
-The random error was inferred from the sample standard deviation and the
-systematic error from the sensor calibrations or datasheets. Combining both
-sources of error, along with their propagation into quantities derived from
-multiple measurements, followed the procedures outlined in Coleman and Steele
-(2009) \cite{ColemanSteele}, described below.
+Both systematic and random errors were combined to calculate experimental
+uncertainty. The random error was inferred from the sample standard deviation
+(on a per-revolution basis) and the systematic error was estimated from the
+sensor calibrations or datasheets. Combining both sources of error, along with
+their propagation into quantities derived from multiple measurements, followed
+the procedures outlined in Coleman and Steele \cite{ColemanSteele}, described
+below.
 
-An expanded uncertainty interval with 95\% confidence was computed for
-$\lambda$, $C_P$, and $C_D$
+For the mean rotor power and drag coefficients an expanded uncertainty interval
+with 95\% confidence
 \begin{equation}
@@
 \end{equation}
-where $t_{95}$ is the value from the Student-$t$ distribution for a 95\%
-confidence interval and $u_c$ is the combined standard uncertainty. Combined
-standard uncertainty for a given quantity $X$ is calculated by
+was computed, where $t_{95}$ is the value from the Student-$t$ distribution for
+a 95\% confidence interval and $u_c$ is the combined standard uncertainty.
+Combined standard uncertainty for a given quantity $X$ is calculated by
 \begin{equation}
-    u_X^2 = s_X^2 + b_X^2,
+    u_X^2 = s_{\bar{X}}^2 + b_X^2,
 \end{equation}
-where $s_X$ is the sample standard deviation, calculated as the standard
-deviation of the mean per turbine revolution, and $b_X$ is the systematic
-uncertainty, computed by
+where $s_{\bar{X}}$ is the sample standard deviation of the mean per turbine
+revolution ($s_{\bar{X}} = s_X/\sqrt{N}$), and $b_X$ is the systematic
+uncertainty, computed as
 \begin{equation}
@@
 and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
-systematic uncertainty, estimated as half the value listed in
-Table~\ref{tab-sensors}.
+systematic uncertainty, estimated as half the value listed on the sensor
+manufacturer's calibration or datasheet.
 
@@
 $\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
-samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
+samples (or turbine revolutions). $\nu_{b_k}$ was estimated as
 \begin{equation}
@@
 \end{equation}
-where the quantity in parentheses is the relative uncertainty of $b_k$.
-
-From previous measurements of a similarly-sized vertical-axis turbine with the
-same experimental setup, we expect expanded uncertainties for $\lambda$, $C_P$,
-and $C_D$ to be approximately 0.008, 0.01, and 0.02, respectively, at a tow
-speed $U_\infty = 1.0$ m/s. These values are well within the discrepancies
-between previous measurements and predictions by CACTUS \cite{Michelen2014},
-making the data from the experiments described here suitable for model validation.
+where the quantity in parentheses is the relative uncertainty of $b_k$, assumed
+to be 0.25.
 

### 2016-01-17 paper.tex
Shorten uncertainty section

@@
 
-Both systematic and random errors were combined to calculate experimental
-uncertainty. The random error was inferred from the sample standard deviation
-(on a per-revolution basis) and the systematic error was estimated from the
-sensor calibrations or datasheets. Combining both sources of error, along with
-their propagation into quantities derived from multiple measurements, followed
-the procedures outlined in Coleman and Steele \cite{ColemanSteele}, described
-below.
-
 For the mean rotor power and drag coefficients an expanded uncertainty interval
@@
 was computed, where $t_{95}$ is the value from the Student-$t$ distribution for
-a 95\% confidence interval and $u_c$ is the combined standard uncertainty.
-Combined standard uncertainty for a given quantity $X$ is calculated by
+a 95\% confidence interval and $u_c$ is the combined standard uncertainty
+\cite{ColemanSteele}. Combined standard uncertainty for the sample mean of a
+given quantity $X$ is calculated by
 \begin{equation}

### 2016-01-18 paper.tex
Add filter width for RPM moving average

@@
 To calculate turbine RPM from shaft angle, the encoder signal is differentiated
-using a second order central difference scheme, after which a relatively
-small-windowed moving average smoothing filter is applied to match the noise
-level present in the redundant turbine RPM measurement from the motion
-controller. A similar approach is used for calculating tow carriage speed
-$U_\infty$ from carriage position measurements. Power and drag coefficients are
-calculated as instantaneous quantities from the carriage speed as
+using a second order central difference scheme, after which an 8 sample wide
+moving average smoothing filter is applied to match the noise level present in
+the redundant turbine RPM measurement from the motion controller. A similar
+approach is used for calculating tow carriage speed $U_\infty$ from carriage
+position measurements. Power and drag coefficients are calculated as
+instantaneous quantities from the carriage speed as
 

### 2016-01-18 paper.tex
Add load cell capacity

@@
 frame built from NACA 0020 struts, attached to the tow carriage by four linear
-bearings, which transfer all streamwise force to a pair of Sentran ZB S-beam
-load cells \cite{SentranZB}. The turbine shaft RPM was controlled by a servo
-motor system, which allowed precise control of the turbine tip speed ratio. The
-load torque was measured by an Interface T8 200 Nm capacity inline rotary torque
-transducer \cite{InterfaceT8}. An additional Sentran ZB load cell mounted at a
-fixed distance from the servo motor via a moment arm provided a redundant torque
-measurement. Turbine shaft angle was measured using the Kollmorgen AKD servo
-drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
-turbine shaft revolution. Carriage speed, and therefore inflow velocity was
-measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
-\cite{RenishawLM15}. All of these performance-related quantities were sampled at
-2 kHz, while the tow tank's motion controller provided redundant measurements of
-the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
-measurements at 1 meter downstream were measured with a Nortek Vectrino+
-acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
-and drawing of the experimental setup are shown in
+bearings, which transfer all streamwise force to a pair of 500 lbf capacity
+Sentran ZB S-beam load cells \cite{SentranZB}. The turbine shaft RPM was
+controlled by a servo motor system, which allowed precise control of the turbine
+tip speed ratio. The load torque was measured by an Interface T8 200 Nm capacity
+inline rotary torque transducer \cite{InterfaceT8}. An additional Sentran ZB
+load cell mounted at a fixed distance from the servo motor via a moment arm
+provided a redundant torque measurement. Turbine shaft angle was measured using
+the Kollmorgen AKD servo drive's emulated encoder output \cite{KollmorgenAKD},
+set to $10^5$ counts per turbine shaft revolution. Carriage speed, and therefore
+inflow velocity was measured using a Renishaw LM15 linear encoder with 10 $\mu$m
+resolution \cite{RenishawLM15}. All of these performance-related quantities were
+sampled at 2 kHz, while the tow tank's motion controller provided redundant
+measurements of the carriage speed turbine angular velocity sampled at 1 kHz.
+Turbine wake measurements at 1 meter downstream were measured with a Nortek
+Vectrino+ acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200
+Hz. A photo and drawing of the experimental setup are shown in
 Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

### 2016-01-18 paper.tex
Load cells are ZB3 model

@@
 bearings, which transfer all streamwise force to a pair of 500 lbf capacity
-Sentran ZB S-beam load cells \cite{SentranZB}. The turbine shaft RPM was
+Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft RPM was
 controlled by a servo motor system, which allowed precise control of the turbine

### 2016-01-18 paper.tex
Discuss power and drag coefficient curves more; resolves #25

@@
 
-Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
-versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
-respectively. $C_P$ is shown to increase in general with $Re$, along with a
-reduction in the optimal tip speed ratio, due to the tendency of foils to stall
-at higher angles of attack at higher $Re$, and the higher angle of attack ranges
-seen by the blades at lower $\lambda$. These effects diminish with increasing
-$Re$, which is expected as the blade boundary layers transition to turbulence
-closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}.
-
-Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
-not collapse exactly onto each other. Note that the data collection was limited
-at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
-the tow carriage drive belt. In contrast to the power coefficient data, the
-rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge 0.6
-\times 10^6$.
+Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
+tip speed ratio in Fig.~\ref{fig:cp-curves}. $C_P$ is shown to increase in
+general with $Re$, along with a reduction in the optimal tip speed ratio, due to
+the tendency of foils to stall at higher angles of attack at higher $Re$, and
+the higher angle of attack ranges seen by the blades at lower $\lambda$. These
+effects diminish with increasing $Re$, which is expected as the blade boundary
+layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
+    Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer as it moves
+against the adverse pressure gradient on the suction side of the foil. Note how
+at lower tip speed ratios and Reynolds numbers, $C_P$ becomes significantly
+negative, which is possible thanks to the speed control of the experimental
+setup's servo motor applying negative torque to the rotor.
 
@@
 
+Mean rotor drag coefficients are plotted versus tip speed ratio in
+Fig.~\ref{fig:cd-curves}. These $C_D$ curves show fewer differences compared to
+the power coefficient curves, which is most noticeable at low $\lambda$ and low
+$Re$. The relative similarity could be attributed to the effects of stall, where
+the lift-to-drag ratio on the blades may drop, decreasing rotor torque, though
+the total resultant force due to high blade drag retains a similar component in
+the streamwise direction.
+
 \begin{figure}[h]
@@
 
-The behavior of the power coefficient at $\lambda=3.1$ is plotted in
-Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
-highlighted. We see that the power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
-\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
-positive trend. The tendency of $C_P$ to continue increasing slightly could be
-an effect of lower virtual camber when compared to the strong $Re$-independence
-of the higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
+Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
+not collapse exactly onto each other. Note that the data collection was limited
+at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
+the tow carriage drive belt. However, in contrast to the power coefficient data,
+the rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge
+0.6 \times 10^6$.
+
+The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
+Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
+of $C_D$ was observed. We see that the power coefficient of the turbine
+increases dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda
+U_\infty c / \nu \approx 2 \times 10^5$, beyond which there appears to be a
+small, linear, positive trend. The tendency of $C_P$ to continue increasing
+slightly could be an effect of lower ``virtual camber''---or flow curvature
+\cite{Migliore1980}---when compared to the strong $Re$-independence of the
+higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
 
@@
 
-    \label{fig:cp-re-dep}
+    \label{fig:perf-re-dep}
 \end{figure}

### 2016-01-18 paper.tex
Move strut drag section after performance; resolves #39
Note how similar C_D for high drag struts helps support the Re-independence of C_D at lower Re

@@
 
+\subsection*{Strut drag losses}
+
+Performance curves for the rotor with both NACA 0021 and cylindrical struts are
+shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
+struts reduce performance dramatically, which worsens as $\lambda$ increases.
+This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
+though the strut losses in this case are larger due to the very high drag profile.
+
+\begin{figure}[ht!]
+    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
+
+    \caption{{\bf High drag strut performance.} Turbine performance and rotor
+        drag coefficient curves with both NACA 0021 and cylindrical struts.}
+
+    \label{fig:perf-covers}
+\end{figure}
+
+Measurements for the power coefficient contributions of the strut drag losses
+are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
+struts---both in towed and stationary conditions. These are computed in the same
+fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the blades removed.
+We see that strut drag losses increase with tip speed ratio to the power 2--3,
+which makes streamlined struts much more important for low solidity turbines,
+given the inverse correlation between solidity and $\lambda_0$
+\cite{Templin1974}.
+
+\begin{figure}[ht!]
+    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
+
+    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
+        (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}
+
+    \label{fig:no-blades}
+\end{figure}
+
+Strut drag losses do not change much for the streamlined NACA 0021 struts in the
+towed versus stationary configuration, which helps explain why overall rotor
+drag coefficients remain relatively constant even at low Reynolds number, were
+$C_P$ is dramatically reduced, or even negative. For the cylindrical struts,
+losses increase significantly when towed and operating in the mid range of tip
+speed ratios. Though a real turbine would never use such high drag struts, with
+respect to numerical modeling, these measurements will allow support struts to
+be simulated without blades, to isolate and evaluate the ability to predict
+these losses independent of the blade loading.
+
 \subsection*{Wake characteristics}
@@
 
-\subsection*{Strut drag losses}
-
-Performance curves for the rotor with both NACA 0021 and cylindrical struts are
-shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
-struts reduce performance dramatically, which worsens as $\lambda$ increases.
-This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
-though the strut losses in this case are larger due to the very high drag profile.
-
-\begin{figure}[ht!]
-    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
-
-    \caption{{\bf High drag strut performance.} Turbine performance and rotor
-        drag coefficient curves with both NACA 0021 and cylindrical struts.}
-
-    \label{fig:perf-covers}
-\end{figure}
-
-Measurements for the power coefficient contributions of the strut drag losses
-are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
-struts---both in towed and stationary conditions. These are computed in the same
-fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the blades removed.
-We see that strut drag losses increase with tip speed ratio to the power 2--3,
-which makes streamlined struts much more important for low solidity turbines,
-given the inverse correlation between solidity and $\lambda_0$
-\cite{Templin1974}.
-
-\begin{figure}[ht!]
-    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
-
-    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
-    (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}
-
-    \label{fig:no-blades}
-\end{figure}
-
-Strut drag losses do not change much for the streamlined NACA 0021 struts in the
-towed versus stationary configuration. However, for the cylindrical struts,
-losses increase significantly when towed and operating in the mid range of tip
-speed ratios. With respect to numerical modeling, these measurements will allow
-support struts to be simulated without blades, to isolate and evaluate the
-ability to predict these losses independent of the blade loading.
-
 \subsection*{Conclusions}

### 2016-01-18 paper.tex
Add two paragraphs from @nearyvs; fixes #43 and fixes #48

@@
 \section*{Introduction}
+
+The Reference Model Project (RMP), sponsored by the US Department of Energy,
+launched six marine hydrokinetic (MHK) technology point designs as reference
+models (RM) to serve as non-proprietary test articles for open research
+development, and to benchmark performance and costs for technology developers
+\cite{Neary2014, Neary2014a}. Open-source RMP products, along with supporting
+documentation, are available at the RMP website
+\url{http://energy.sandia.gov/rmp} to facilitate their use in future R\&D
+studies by industry, academia, and national laboratories. These products
+include: Design specifications and computer-aided design (CAD) files for each RM
+device to allow exact replication for physical and numerical modeling studies;
+Resource site information used to design each RM device; and references to
+physical modeling data sets that can be used to validate numerical modeling
+design and analysis tools.
+
+Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
+that was designed to operate in a reach of the lower Mississippi River near
+Baton Rouge, Louisiana \cite{Barone2011, Neary2011}.
 

### 2016-01-18 paper.tex
Refine introduction a bit

--- 2016-01-18 paper.tex
@@
 
-Sandia National Laboratories, in collaboration with the US Department of Energy
-developed the Reference Model devices to provide modeling targets for advancing
-marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
-Model 2 (RM2), a vertical-axis cross-flow turbine intended for river
-environments, was initially designed by Barone et al. \cite{Barone2011} using
-the CACTUS vortex line code \cite{Murray2011}. A scaled physical model of the
-RM2 was then designed and built by the Saint Anthony Falls Laboratory (SAFL) to
-validate the CACTUS predictions. Experimental performance measurements were
-significantly lower than the numerical results \cite{Hill2014}, which was
-assumed to be a result of the physical model's low Reynolds number
-\begin{equation}
-    Re_D = \frac{U_\infty D}{\nu},
-\label{eq:Re}
-\end{equation}
-where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter (note
-that in some cases the blade chord length $c$ is used as this length scale), and
-$\nu$ is the fluid kinematic viscosity.
+The Reference Model Project (RMP), sponsored by the US Department of Energy,
+produced six marine hydrokinetic (MHK) technology point designs as reference
+models (RM) to serve as non-proprietary test articles for open research
+development, and to benchmark performance and costs for technology developers
+\cite{Neary2014, Neary2014a}. Open-source RMP products, along with supporting
+documentation, are available at the RMP website
+\url{http://energy.sandia.gov/rmp} to facilitate their use in future R\&D
+studies by industry, academia, and national laboratories. These products
+include: Technical specifications and computer-aided design (CAD) files for each
+RM device to allow exact replication for physical and numerical modeling
+studies; Resource site information used to design each RM device; and references
+to physical modeling data sets that can be used to validate numerical modeling
+design and analysis tools.
+
+Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
+that was designed to operate in a reach of the lower Mississippi River near
+Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three blades,
+a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R$, and a
+preliminary analysis with Sandia's CACTUS vortex line numerical model
+\cite{Murray2011} predicted a full-scale performance coefficient of 47\% at 1
+m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
+3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
+and radius, respectively. An initial experimental measurement campaign with a
+1:15 scale RM2 rotor conducted at the Saint Anthony Falls Laboratory (SAFL) at
+the University of Minnesota resulted in maximum power coefficient of
+approximately 5\% at a tip speed ratio $\lambda = 2.2$. This discrepancy between
+numerical and physical model performance prompted the experimental measurements
+presented here, namely due to the low Reynolds number---$Re_D = U_\infty D /
+\nu$, where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter,
+and $\nu$ is the fluid kinematic viscosity---of the 1:15 scale tests, which were
+performed at $Re_D \sim 10^5$ \cite{Hill2014}.
 
@@
 direction). These variations become larger at lower tip speed ratio
-\begin{equation}
-    \lambda=\frac{\omega R}{U_\infty},
-\end{equation}
-where $\omega$ and $R$ are the rotor angular velocity and radius
 \cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
@@
 lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
-(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
-turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
-operate in a higher density fluid, unsteady dynamic effects related to the
-blades' pitching motion and flow curvature also become more important when
-compared to wind turbines.
+(MHK) cross-flow turbines typically have higher solidity than their similar wind
+turbine counterparts (often called vertical-axis wind turbines, or VAWTs), and
+hence operate at lower tip-speed ratios.
 

### 2016-01-18 paper.tex
No need to repeat 'tip speed ratio'

@@
 the University of Minnesota resulted in maximum power coefficient of
-approximately 5\% at a tip speed ratio $\lambda = 2.2$. This discrepancy between
-numerical and physical model performance prompted the experimental measurements
-presented here, namely due to the low Reynolds number---$Re_D = U_\infty D /
-\nu$, where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter,
-and $\nu$ is the fluid kinematic viscosity---of the 1:15 scale tests, which were
-performed at $Re_D \sim 10^5$ \cite{Hill2014}.
+approximately 5\% at $\lambda = 2.2$. This discrepancy between numerical and
+physical model performance prompted the experimental measurements presented
+here, namely due to the low Reynolds number---$Re_D = U_\infty D / \nu$, where
+$U_\infty$ is the free stream velocity, $D$ is the rotor diameter, and $\nu$ is
+the fluid kinematic viscosity---of the 1:15 scale tests, which were performed at
+$Re_D \sim 10^5$ \cite{Hill2014}.
 

### 2016-01-18 paper.tex
Remove paragraph about CFT kinematics/dynamics

@@
 $Re_D \sim 10^5$ \cite{Hill2014}.
-
-As a consequence of the inherently unsteady nature of the cross-flow rotor, the
-RM2 blades experience large variations in angles of attack as they rotate about
-their axis (``cross-flow'' means the axis of rotation is perpendicular to flow
-direction). These variations become larger at lower tip speed ratio
-\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
-that the blades operate under dynamic stall, which is a complex unsteady process
-and deviates significantly from static foil behavior, during part of the
-rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
-lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
-(MHK) cross-flow turbines typically have higher solidity than their similar wind
-turbine counterparts (often called vertical-axis wind turbines, or VAWTs), and
-hence operate at lower tip-speed ratios.
 

### 2016-01-18 paper.tex
Remove paragraph about solidity and clean up later motivation a bit

@@
 
-The performance of cross-flow MHK turbines thus depends on both Reynolds number
-and solidity (note that these issues are related, since an average blade chord
-Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
-expressed in terms of tip speed ratio $\lambda$, the optimal value of which is a
-function of solidity). If numerical models are validated with physical model
-data that was obtained at insufficiently high Reynolds numbers, it cannot be
-determined whether problems with model predictions are caused by Reynolds number
-effects, issues related to higher solidity, or both. It is uncertain whether
-numerical models validated with physical model data obtained at low Reynolds
-number should be considered validated at all, since the scale at which the model
-will be applied is orders of magnitude larger. One way to overcome this
-uncertainty is to show that the scaled physical model test has become Reynolds
-number independent, and therefore validation efforts should be relevant at
-full-scale.
-
-For example, the effect of Reynolds number on average power output was shown to
-be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
-testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$,
-increased with Reynolds number, $Re_c$, along with a shift of the location of
+The effect of Reynolds number on average power output was shown to be
+significant on the 2 m Sandia Research Darrieus turbine in wind tunnel testing
+\cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$, increased with
+Reynolds number, $Re_c$ (based on blade chord rather than diameter, though these
+are approximately proportional), along with a shift of the location of
 $C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
@@
 
-The need for experimental data that is relevant to full-scale behavior stems
-from the need to validate numerical models---most importantly mid-fidelity
-models---desirable for MHK developers to predict the performance of their
-cross-flow turbine designs, since physical modeling at appropriate scales can be
-prohibitively expensive in the early stages of engineering.
-
-To date, attempts to validate SNL's mid-fidelity CACTUS vortex line model
-\cite{Murray2011} have relied on measurements from the Saint Anthony Falls
-Laboratory (SAFL) \cite{Hill2014} and the University of New Hampshire (UNH)
-\cite{Neary2013, Michelen2014}. For the SAFL experiments (RM2), the chord
-Reynolds number, $Re_c \sim 10^4$, was below the threshold needed to properly
-simulate lift and stall characteristics. For the UNH experiment
-\cite{Bachant2013}, the chord Reynolds number was sufficiently high at $Re_c
-\approx 2.7 \times 10^5$, but the chord/radius ratio and solidity (13.4\%)
-created instability in the free-wake evolution in the model, which caused
-significant overestimation of power coefficient.
+As part of the engineering process it is generally less expensive to assess
+designs via numerical rather than physical models. However, it is
+important---especially when dealing with fluid dynamics where the ``exact''
+physics cannot be resolved with even the most advanced computers---that
+numerical models be validated against experimental data. It is uncertain whether
+numerical models validated with physical model data obtained at low Reynolds
+number should be considered validated at all, since the scale at which the model
+will be applied for real world design problems is orders of magnitude larger.
+One way to overcome this uncertainty is to show that the scaled physical model
+test has become Reynolds number independent, and therefore validation efforts
+should be relevant at full-scale, which was the strategy employed here.
 

### 2016-01-18 paper.tex
Tighten up and expand last paragraph of introduction

@@
 
-The present task was to acquire a new dataset for the lower solidity RM2
-turbine, but at higher Reynolds numbers than those achieved in the experiments
-at SAFL. It was suspected that the strut drag model in CACTUS could be the
-source of some discrepancy. Thus, the strut drag was deliberately and
-significantly increased in the physical model to provide data to help answer
-that question. This dataset is publicly available for both validation of CACTUS
-and other numerical models \cite{Bachant2015-RM2-data}.
+The present task was to acquire a new experimental dataset for the lower
+solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
+modeling. It was hypothesized that the parasitic losses from rotor blade support
+struts could play an important role in overall turbine performance. Thus, the
+parasitic torque from strut drag was measured without blades, then deliberately
+and significantly increased in the physical model to provide data to help answer
+that question. The velocity field in the near-wake of the turbine was then
+measured to compare with measurements from a higher solidity rotor in the same
+experimental setup \cite{Bachant2015-JoT}, and provide validation data for
+numerical models that predict wake flows, which determine turbine--turbine
+interaction and optimal spacing for turbine arrays. This dataset, along with the
+code for processing and visualization, is publicly available
+\cite{Bachant2015-RM2-data}.
 

### 2016-01-18 paper.tex
Call turbine a physical model and note that the measurements were experimental; resolves #49

@@
 The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
-Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured in a
-towing tank. Performance was measured at multiple Reynolds numbers by varying
-tow carriage speed, and weak linear $Re$-dependence was achieved at a turbine
-diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio
-$\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured at 1
-m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
-transport mechanisms were compared and contrasted with results from a high
-solidity turbine acquired with the same test apparatus. Overall, lower levels of
-streamwise wake recovery were calculated for the RM2 rotor---a consequence of
-both the relatively low solidity and tapered blades. The effects of blade
-support strut drag on turbine performance were investigated by covering the
-rotor's NACA 0021 struts with cylinders. As expected, this modification
+Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured
+experimentally in a towing tank. Performance was measured at multiple Reynolds
+numbers by varying tow carriage speed, and weak linear $Re$-dependence was
+achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal
+tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity
+was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean
+kinetic energy transport mechanisms were compared and contrasted with results
+from a high solidity turbine acquired with the same test apparatus. Overall,
+lower levels of streamwise wake recovery were calculated for the RM2 rotor---a
+consequence of both the relatively low solidity and tapered blades. The effects
+of blade support strut drag on turbine performance were investigated by covering
+the rotor's NACA 0021 struts with cylinders. As expected, this modification
 drastically reduced rotor power coefficient. Strut drag was also measured for
@@
 
-A 1:6 scale model of the RM2 rotor was designed and fabricated. Turbine
+A 1:6 scale physical model of the RM2 rotor was designed and fabricated. Turbine
 geometric parameters were scaled from the RM2 design report \cite{Barone2011},

### 2016-01-18 paper.tex
Add links to GitHub repo; resolves #20

@@
 interaction and optimal spacing for turbine arrays. This dataset, along with the
-code for processing and visualization, is publicly available
-\cite{Bachant2015-RM2-data}.
+code for processing and visualization, is publicly available (licensed via
+Creative Commons CC-BY for data and MIT license for code) as a Git repository on
+GitHub (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable
+archive with a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
 
@@
 This data, along with the code for processing and visualization, is provided
-openly via a Creative Commons license, and is available from
-\cite{Bachant2015-RM2-data}. The authors hope that this can provide
-opportunities for extensive validation of predictive tools for the complex
-unsteady flow physics of cross-flow turbines.
+openly via a Creative Commons license (MIT license for code), and is available
+as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
+citeable archive \cite{Bachant2015-RM2-data}. The authors hope that this can
+provide opportunities for extensive validation of predictive tools for the
+complex unsteady flow physics of cross-flow turbines.
 

### 2016-01-18 paper.tex
Add Vince's recommended edits plus more to the abstract

@@
 The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
-Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured
-experimentally in a towing tank. Performance was measured at multiple Reynolds
-numbers by varying tow carriage speed, and weak linear $Re$-dependence was
-achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal
-tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity
-was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean
-kinetic energy transport mechanisms were compared and contrasted with results
-from a high solidity turbine acquired with the same test apparatus. Overall,
-lower levels of streamwise wake recovery were calculated for the RM2 rotor---a
-consequence of both the relatively low solidity and tapered blades. The effects
-of blade support strut drag on turbine performance were investigated by covering
-the rotor's NACA 0021 struts with cylinders. As expected, this modification
-drastically reduced rotor power coefficient. Strut drag was also measured for
-the NACA 0021 and cylindrical configurations with the blades removed. These
-measurements provide a comprehensive open dataset for validating numerical
-models' predictive capabilities for low solidity rotors.
+physical reference model vertical-axis cross-flow turbine were measured
+experimentally in a towing tank, to provide a comprehensive open dataset for
+validating numerical models. Performance was measured at multiple Reynolds
+numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
+at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
+ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
+at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
+mean kinetic energy transport were compared with results from a high solidity
+turbine acquired with the same test apparatus. Overall, lower levels of
+streamwise wake recovery were calculated for the RM2 case---a consequence of
+both the relatively low solidity and tapered blades reducing blade tip vortex
+shedding---responsible for mean vertical advection---and lower levels of
+turbulence caused by higher operating tip speed ratio and therefore reduced
+dynamic stall. The effects of blade support strut drag on turbine performance
+were investigated by covering the rotor's NACA 0021 struts with cylinders. As
+expected, this modification drastically reduced the rotor power coefficient.
+Strut drag was also measured for the NACA 0021 and cylindrical configurations
+with the blades removed.
 

### 2016-01-18 paper.tex
Make Re plural

@@
 numerical models validated with physical model data obtained at low Reynolds
-number should be considered validated at all, since the scale at which the model
-will be applied for real world design problems is orders of magnitude larger.
-One way to overcome this uncertainty is to show that the scaled physical model
-test has become Reynolds number independent, and therefore validation efforts
-should be relevant at full-scale, which was the strategy employed here.
+numbers should be considered validated at all, since the scale at which the
+model will be applied for real world design problems is orders of magnitude
+larger. One way to overcome this uncertainty is to show that the scaled physical
+model test has become Reynolds number independent, and therefore validation
+efforts should be relevant at full-scale, which was the strategy employed here.
 

### 2016-01-18 paper.tex
Reword per @nearyvs suggestion

@@
 larger. One way to overcome this uncertainty is to show that the scaled physical
-model test has become Reynolds number independent, and therefore validation
-efforts should be relevant at full-scale, which was the strategy employed here.
+model test has become Reynolds number independent, so validation efforts are
+relevant at full-scale, which was the strategy employed here.
 

### 2016-01-18 paper.tex
Add 'The'

@@
 significant on the 2 m Sandia Research Darrieus turbine in wind tunnel testing
-\cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$, increased with
-Reynolds number, $Re_c$ (based on blade chord rather than diameter, though these
-are approximately proportional), along with a shift of the location of
+\cite{Blackwell1976}: The maximum power coefficient, $C_{P_{\max}}$, increased
+with Reynolds number, $Re_c$ (based on blade chord rather than diameter, though
+these are approximately proportional), along with a shift of the location of
 $C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The

### 2016-01-18 paper.tex
Some rewording per @nearyvs suggestion

@@
 
-The present task was to acquire a new experimental dataset for the lower
-solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
-modeling. It was hypothesized that the parasitic losses from rotor blade support
-struts could play an important role in overall turbine performance. Thus, the
-parasitic torque from strut drag was measured without blades, then deliberately
-and significantly increased in the physical model to provide data to help answer
-that question. The velocity field in the near-wake of the turbine was then
-measured to compare with measurements from a higher solidity rotor in the same
-experimental setup \cite{Bachant2015-JoT}, and provide validation data for
-numerical models that predict wake flows, which determine turbine--turbine
-interaction and optimal spacing for turbine arrays. This dataset, along with the
-code for processing and visualization, is publicly available (licensed via
-Creative Commons CC-BY for data and MIT license for code) as a Git repository on
-GitHub (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable
-archive with a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
+The present study was motivated by the need to acquire a new experimental
+dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
+relevant to full-scale modeling. It was hypothesized that the parasitic losses
+from rotor blade support struts could play an important role in overall turbine
+performance. Thus, the parasitic torque from strut drag was measured without
+blades, then deliberately and significantly increased in the physical model to
+provide data to investigate its importance. The velocity field in the near-wake
+of the turbine was then measured to compare with measurements from a higher
+solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
+provide validation data for numerical models that predict wake flows, which
+determine turbine--turbine interaction and optimal spacing for turbine arrays.
+This dataset, along with the code for processing and visualization, is publicly
+available (licensed via Creative Commons CC-BY for data and MIT license for
+code) as a Git repository on GitHub
+(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable archive with
+a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
 

### 2016-01-18 paper.tex
Remove first sentence of turbine model section

@@
 
-% For figure citations, please use "Fig." instead of "Figure".
-
-A 1:6 scale physical model of the RM2 rotor was designed and fabricated. Turbine
-geometric parameters were scaled from the RM2 design report \cite{Barone2011},
-with the exception of the shaft diameter, which was scaled from the SAFL RM2
-model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
-which may aid in comparison of the results, though this was not a top priority.
-Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
-turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
-components---blades, struts, shaft, and center hub sections---were fabricated
-from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
-class 2 specifications. CAD models of the turbine are available from
-\cite{Bachant2015-RM2-CAD}.
+Geometric parameters for the 1:6 scale RM2 rotor were taken from the RM2 design
+report \cite{Barone2011}, with the exception of the shaft diameter, which was
+scaled from the SAFL RM2 model \cite{Hill2014}. The hubs were designed to be
+similar to the SAFL model, which may aid in comparison of the results, though
+this was not a top priority. Geometric parameters are shown in
+Tab.~\ref{tab:turb-geom} and a drawing of the turbine design is shown in
+Fig.~\ref{fig:turbine-drawing}. The turbine model components---blades, struts,
+shaft, and center hub sections---were fabricated from 6061-T6 aluminum, which
+was hardcoat anodized per MIL-8625-A, type III, class 2 specifications. CAD
+models of the turbine are available from \cite{Bachant2015-RM2-CAD}.
 

### 2016-01-18 paper.tex
Simplify turbine model paragraph

@@
 report \cite{Barone2011}, with the exception of the shaft diameter, which was
-scaled from the SAFL RM2 model \cite{Hill2014}. The hubs were designed to be
-similar to the SAFL model, which may aid in comparison of the results, though
-this was not a top priority. Geometric parameters are shown in
-Tab.~\ref{tab:turb-geom} and a drawing of the turbine design is shown in
-Fig.~\ref{fig:turbine-drawing}. The turbine model components---blades, struts,
-shaft, and center hub sections---were fabricated from 6061-T6 aluminum, which
-was hardcoat anodized per MIL-8625-A, type III, class 2 specifications. CAD
-models of the turbine are available from \cite{Bachant2015-RM2-CAD}.
+scaled from the SAFL RM2 model \cite{Hill2014}. Values for both the 1:6 and
+full-scale designs are presented in Tab.~\ref{tab:turb-geom} and a drawing of
+the turbine is shown in Fig.~\ref{fig:turbine-drawing}. The rotor
+components---blades, struts, shaft, and center hub sections---were fabricated
+from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
+class 2 specifications. CAD models of the turbine are available from
+\cite{Bachant2015-RM2-CAD}.
 

### 2016-01-18 paper.tex
Simplify wording in facility section

@@
 
-Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
-3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
-pictured in Fig.~\ref{fig:exp-setup}. The blockage ratio based on the rotor
-frontal and tank cross-sectional area was 10\%. The turbine was mounted in a
-frame built from NACA 0020 struts, attached to the tow carriage by four linear
-bearings, which transfer all streamwise force to a pair of 500 lbf capacity
-Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft RPM was
-controlled by a servo motor system, which allowed precise control of the turbine
-tip speed ratio. The load torque was measured by an Interface T8 200 Nm capacity
-inline rotary torque transducer \cite{InterfaceT8}. An additional Sentran ZB
-load cell mounted at a fixed distance from the servo motor via a moment arm
-provided a redundant torque measurement. Turbine shaft angle was measured using
-the Kollmorgen AKD servo drive's emulated encoder output \cite{KollmorgenAKD},
-set to $10^5$ counts per turbine shaft revolution. Carriage speed, and therefore
-inflow velocity was measured using a Renishaw LM15 linear encoder with 10 $\mu$m
-resolution \cite{RenishawLM15}. All of these performance-related quantities were
-sampled at 2 kHz, while the tow tank's motion controller provided redundant
-measurements of the carriage speed turbine angular velocity sampled at 1 kHz.
-Turbine wake measurements at 1 meter downstream were measured with a Nortek
-Vectrino+ acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200
-Hz. A photo and drawing of the experimental setup are shown in
-Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
+Measurements were conducted in the UNH tow/wave tank, pictured in
+Fig.~\ref{fig:exp-setup}, a 36 m long facility with a 3.66 m wide by 2.44 m deep
+cross-section, capable of tow speeds up to 3 m/s. The blockage ratio based on
+the rotor frontal and tank cross-sectional area was 10\%. The turbine was
+mounted in a frame built from NACA 0020 struts, attached to the tow carriage by
+four linear bearings, which transfer all streamwise force to a pair of 500 lbf
+capacity Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft RPM
+was controlled by a servo motor system, which allowed precise control of the
+turbine tip speed ratio. The load torque was measured by an Interface T8 200 Nm
+capacity inline rotary torque transducer \cite{InterfaceT8}. An additional
+Sentran ZB load cell mounted at a fixed distance from the servo motor via a
+moment arm provided a redundant torque measurement. Turbine shaft angle was
+measured using the Kollmorgen AKD servo drive's emulated encoder output
+\cite{KollmorgenAKD}, set to $10^5$ counts per turbine shaft revolution.
+Carriage speed, and therefore inflow velocity was measured using a Renishaw LM15
+linear encoder with 10 $\mu$m resolution \cite{RenishawLM15}. All of these
+performance-related quantities were sampled at 2 kHz, while the tow tank's
+motion controller provided redundant measurements of the carriage speed turbine
+angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
+downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter
+\cite{NortekVectrino}, sampling at 200 Hz. A photo and drawing of the
+experimental setup are shown in Fig.~\ref{fig:exp-setup-photo} and
+Fig.~\ref{fig:exp-setup}, respectively.
 

### 2016-01-18 paper.tex
Remove 'TTL' and describe as digital signal edge

@@
 (wake velocity measurements)---started sampling at precisely the same time each
-tow, after being triggered by a TTL pulse created by the motion controller. This
-strategy retained synchronization for all performance signal samples (tow speed,
-torque, drag, angular velocity), ensuring precise calculation of, e.g., power
-coefficient. Since there was also synchronization of the initial sample from
-each of the three subsystems, correlation of events in the performance and wake
-signals is also possible.
+tow, after being triggered by a digital signal edge from the motion controller.
+This strategy retained synchronization for all performance signal samples (tow
+speed, torque, drag, angular velocity), ensuring precise calculation of, e.g.,
+power coefficient. Since there was also synchronization of the initial sample
+from each of the three subsystems, correlation of events in the performance and
+wake signals is also possible.
 

### 2016-01-18 paper.tex
Don't start sentence with math symbol per @nearyvs suggestion
Past tense
Add comma per @nearyvs

@@
 $\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
-samples (or turbine revolutions). $\nu_{b_k}$ was estimated as
+samples (or turbine revolutions). The degrees of freedom parameter $\nu_{b_k}$
+was estimated as
 \begin{equation}
@@
 inspecting a plot of the $C_P$ time series, and then truncated to include a
-whole number of blade passages. Over this duration relevant statistics are
+whole number of blade passages. Over this duration relevant statistics were
 calculated.
@@
 
-All data processing and plotting code, along with the reduced dataset are
+All data processing and plotting code, along with the reduced dataset, are
 available from \cite{Bachant2015-RM2-data}. Note that this code will

### 2016-01-19 paper.tex
Reword Re dependence of C_P curves
Remove 'we see that' per @nearyvs suggestion

@@
 
-Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
-not collapse exactly onto each other. Note that the data collection was limited
-at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
-the tow carriage drive belt. However, in contrast to the power coefficient data,
-the rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge
-0.6 \times 10^6$.
+The power coefficient curves do not collapse exactly onto each other, indicating
+Reynolds number dependence, though the differences become relatively small as
+$Re$ is increased. Note that the data collection was limited at higher $Re$ and
+$\lambda$ due to the unsteady turbine force resonating with the tow carriage
+drive belt. However, in contrast to the power coefficient data, the rotor drag
+coefficient curves nearly collapse onto each other for $Re_D \ge 0.6 \times
+10^6$.
 
@@
 Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
-of $C_D$ was observed. We see that the power coefficient of the turbine
-increases dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda
-U_\infty c / \nu \approx 2 \times 10^5$, beyond which there appears to be a
-small, linear, positive trend. The tendency of $C_P$ to continue increasing
-slightly could be an effect of lower ``virtual camber''---or flow curvature
+of $C_D$ was observed. The power coefficient of the turbine increases
+dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
+\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
+positive trend. The tendency of $C_P$ to continue increasing slightly could be
+an effect of lower ``virtual camber''---or flow curvature
 \cite{Migliore1980}---when compared to the strong $Re$-independence of the

### 2016-01-19 paper.tex
Name subsection 'near-wake...' per @nearyvs suggestion
Thanks --> due

@@
 
-\subsection*{Wake characteristics}
+\subsection*{Near-wake characteristics}
 
@@
 velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
-lower acceleration around the turbine thanks to lower rotor drag coefficient and
-blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
-vortex shedding are relatively weaker, which is likely an effect of the RM2's
-lower solidity and tapered blades.
+lower acceleration around the turbine due to the lower rotor drag coefficient
+and blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade
+tip vortex shedding are relatively weaker, which is likely an effect of the
+RM2's lower solidity and tapered blades.
 

### 2016-01-19 paper.tex
Remove 'we also see'
Thanks --> due

@@
 lower acceleration around the turbine due to the lower rotor drag coefficient
-and blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade
-tip vortex shedding are relatively weaker, which is likely an effect of the
-RM2's lower solidity and tapered blades.
+and blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is relatively
+weaker, which is likely an effect of the RM2's smaller blade chord length and
+tapered blades.
 
@@
 this experiment. However, the differences observed are beyond this discrepancy.
-We also see relatively lower levels of cross-stream turbulent transport thanks
-to the lack of blade stall vortex shedding. These results may have interesting
+We also see relatively lower levels of cross-stream turbulent transport due to
+the lack of blade stall vortex shedding. These results may have interesting
 implications regarding the application of turbines with lower power coefficient

### 2016-01-19 paper.tex
Adjust wording per @nearyvs

@@
 to possibly improve overall array performance through enhanced transport of
-kinetic energy from the free stream, though a detailed anaylsis of the
-downstream evolution and turbine interaction will be necessary.
+kinetic energy from the free stream, though evaluating these trade-offs will
+require a detailed analysis of the downstream evolution and turbine--wake
+interaction.
 

### 2016-01-19 paper.tex
Worsens --> is more pronounced

@@
 shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
-struts reduce performance dramatically, which worsens as $\lambda$ increases.
-This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
-though the strut losses in this case are larger due to the very high drag profile.
+struts reduce performance dramatically, which is more pronounced as $\lambda$
+increases. This is in accordance with the measurements of Rawlings
+\cite{Rawlings2008}, though the strut losses in this case are larger due to the
+very high drag profile.
 

### 2016-01-20 paper.tex
Add K transport derivation and motivation; resolves #6

@@
 \newcommand{\ipsum}{{\bf IPSUM}}
+\def \p{\partial}
+\def \d{\mathrm{d}}
+\def \D{\mathrm{D}}
 
@@
 
-Weighted averages for the transport terms in the mean kinetic energy
-equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
-Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
+Analysis of the near-wake of the higher solidity UNH-RVAT turbine revealed that
+vertical advection was the largest contributer to streamwise recovery
+\cite{Bachant2015-JoT}, a trait which is considered an advantage of cross-flow
+over axial-flow rotors in arrays \cite{Kinzel2012}. A similar analysis was
+undertaken for the RM2, starting with the transport equation for mean kinetic
+energy, rearranged to isolate the streamwise partial derivative (indices follow
+the Einsteinian convention):
+\begin{equation}
+    \begin{split}
+        \frac{\p K}{\p x}
+        =
+        \frac{1}{U}
+        \bigg{[}
+        & - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.}}
+        - \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
+        % Pressure work:
+        - \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
+        % Work by viscous forces
+        + \frac{\p}{\p x_j} 2 \nu U_i S_{ij}
+        % Turbulent transport of K
+        - \underbrace{
+            \frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
+        }_{\text{Turb. trans.}} \\
+        % Production of k
+        & + 
+        \underbrace{
+            \overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
+        }_{k\text{-prod.}}
+        % Mean dissipation
+        - 
+        \underbrace{
+            2 \nu S_{ij}S_{ij}
+        }_{\text{Mean diss.}}
+        \bigg{]}.
+    \end{split}
+    \label{eq:K-full}
+\end{equation}
+
+Terms that were able to be calculated from the experimental data are those that
+do not involve $x$-derivatives, since all wake measurement locations were at a
+fixed downstream distance. The available terms are the cross-stream advection
+($y$-adv.), vertical advection ($z$-adv.), transport due to turbulent
+fluctuations ($y$-turb. and $z$-turb., separated by the direction of the
+derivative), production of turbulence kinetic energy ($k$-prod.), and the
+dissipation due to the mean velocity gradient (Mean diss.).
+
+Derivatives were computed with a second order central difference scheme for
+interior points, and a second order inward-facing scheme for the edges,
+identical to \cite{Bachant2015-JoT}. Weighted averages for these computation are
+shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding,
 transport due to vertical advection at this point in the wake is approximately 3

### 2016-01-20 paper.tex
Add McMasters1980 reference

@@
 layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
-    Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer as it moves
-against the adverse pressure gradient on the suction side of the foil. Note how
-at lower tip speed ratios and Reynolds numbers, $C_P$ becomes significantly
-negative, which is possible thanks to the speed control of the experimental
-setup's servo motor applying negative torque to the rotor.
+    McMasters1980, Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer
+as it moves against the adverse pressure gradient on the suction side of the
+foil. Note how at lower tip speed ratios and Reynolds numbers, $C_P$ becomes
+significantly negative, which is possible thanks to the speed control of the
+experimental setup's servo motor applying negative torque to the rotor.
 

### 2016-01-20 paper.tex
for --> of
Tense consistency; resolves #50

@@
 
-To calculate turbine RPM from shaft angle, the encoder signal is differentiated
+To calculate turbine RPM from shaft angle, the encoder signal was differentiated
 using a second order central difference scheme, after which an 8 sample wide
-moving average smoothing filter is applied to match the noise level present in
+moving average smoothing filter was applied to match the noise level present in
 the redundant turbine RPM measurement from the motion controller. A similar
-approach is used for calculating tow carriage speed $U_\infty$ from carriage
+approach was used for calculating tow carriage speed $U_\infty$ from carriage
 position measurements. Power and drag coefficients are calculated as
@@
 Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
-tip speed ratio in Fig.~\ref{fig:cp-curves}. $C_P$ is shown to increase in
-general with $Re$, along with a reduction in the optimal tip speed ratio, due to
-the tendency of foils to stall at higher angles of attack at higher $Re$, and
-the higher angle of attack ranges seen by the blades at lower $\lambda$. These
-effects diminish with increasing $Re$, which is expected as the blade boundary
-layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
+tip speed ratio in Fig.~\ref{fig:cp-curves}. In general, $C_P$ increases with
+$Re$, along with a reduction in the optimal tip speed ratio, due to the tendency
+of foils to stall at higher angles of attack at higher $Re$, and the higher
+angle of attack ranges seen by the blades at lower $\lambda$. These effects
+diminish with increasing $Re$, which is expected as the blade boundary layers
+transition to turbulence closer to the leading edge \cite{Lissaman1983,
     McMasters1980, Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer
@@
 foil. Note how at lower tip speed ratios and Reynolds numbers, $C_P$ becomes
-significantly negative, which is possible thanks to the speed control of the
+significantly negative, which was possible thanks to the speed control of the
 experimental setup's servo motor applying negative torque to the rotor.
@@
 
-Strut drag losses do not change much for the streamlined NACA 0021 struts in the
-towed versus stationary configuration, which helps explain why overall rotor
-drag coefficients remain relatively constant even at low Reynolds number, were
-$C_P$ is dramatically reduced, or even negative. For the cylindrical struts,
-losses increase significantly when towed and operating in the mid range of tip
-speed ratios. Though a real turbine would never use such high drag struts, with
-respect to numerical modeling, these measurements will allow support struts to
-be simulated without blades, to isolate and evaluate the ability to predict
-these losses independent of the blade loading.
+Strut drag losses did not change much for the streamlined NACA 0021 struts in
+the towed versus stationary configuration, which helps explain why overall rotor
+drag coefficients remained relatively constant even at low Reynolds number,
+where $C_P$ was dramatically reduced, or even negative. For the cylindrical
+struts, losses increased significantly when towed and operating in the mid range
+of tip speed ratios. Though a real turbine would never use such high drag
+struts, with respect to numerical modeling, these measurements will allow
+support struts to be simulated without blades, to isolate and evaluate the
+ability to predict these losses independent of the blade loading.
 
@@
 shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding,
-transport due to vertical advection at this point in the wake is approximately 3
-times lower than the higher solidity UNH-RVAT. Note that direct comparison is
-somewhat invalid, since the total measurement plane area is about 5\% lower for
+transport due to vertical advection at this point in the wake was approximately
+3 times lower than the higher solidity UNH-RVAT. Note that direct comparison is
+somewhat invalid, since the total measurement plane area was about 5\% lower for
 this experiment. However, the differences observed are beyond this discrepancy.
@@
 
-The performance and near-wake for a 1:6 scale DOE Reference Model 2 cross-flow
+The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
 turbine was measured in a towing tank. Performance was assessed for Reynolds
@@
 the vertical advection compared with turbulent transport terms at this location.
-It is interesting to note that though the turbine is a more effective energy
+It is interesting to note that though the RM2 is a more effective energy
 converter than the UNH-RVAT, its wake recovery may in fact be slower due to
-weaker blade tip vortex shedding.
+weaker blade tip vortex shedding and lower levels of turbulence in the
+near-wake.
 
@@
 validation data for both high and low fidelity numerical performance prediction
-models, allowing researchers to test models without blade effects.
+models, allowing researchers and engineers to test predictions without blade
+effects.
 

### 2016-01-20 paper.tex
Move wake paragraph in conclusion after strut drag
Remove unnecessary words

@@
 
+The effects of parasitic drag from blade support struts on turbine performance
+were measured by rotating the turbine without blades while stationary and while
+towing. These losses---even for a streamlined hydrofoil strut---can become
+significant at higher tip speed ratios---up to an approximate 5 percentage point
+decrease in power coefficient at a tip speed ratio of 5. These measurements were
+repeated with a set of high-drag cylindrical struts, which as expected,
+prevented the turbine from producing any mechanical power at any tip speed
+ratio. Nevertheless these measurements provide important validation data for
+both high and low fidelity numerical performance prediction models, allowing
+researchers and engineers to test predictions without blade effects.
+
 The wake at $x/D=0.93$ downstream was shown to be relatively symmetrical and
@@
 near-wake.
-
-The effects of parasitic drag from blade support struts on turbine performance
-were measured by rotating the turbine without blades while stationary and while
-towing. It is shown that these losses---even for a streamlined hydrofoil
-strut---can become significant quickly at higher tip speed ratios---up to an
-approximate 5 percentage point decrease in power coefficient at a tip speed
-ratio of 5. These measurements were repeated with a set of high-drag cylindrical
-struts, which as expected, prevented the turbine from producing any mechanical
-power at any tip speed ratio. Nevertheless these measurements provide important
-validation data for both high and low fidelity numerical performance prediction
-models, allowing researchers and engineers to test predictions without blade
-effects.
 

### 2016-01-20 paper.tex
Make first sentence of conclusion its own paragraph as suggested by @nearyvs

@@
 The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
-turbine was measured in a towing tank. Performance was assessed for Reynolds
-number dependence, showing a convergence to a weakly $Re$-dependent linear
-regime at approximately $Re_D \approx 1 \times 10^6$ or $Re_{c,\mathrm{ave}}
-\approx 2 \times 10^5$. Comparison was made between this turbine and the higher
-solidity UNH-RVAT, tested in nearly identical conditions, which showed similar
-Reynold number thresholds but a flatter linear regime, likely to due virtual
-camber of the higher chord-to-radius ratio of the UNH-RVAT blades.
+turbine was measured in a towing tank.
+
+Performance was assessed for Reynolds number dependence, showing a convergence
+to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
+10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
+between this turbine and the higher solidity UNH-RVAT, tested in nearly
+identical conditions, which showed similar Reynold number thresholds but a
+flatter linear regime, likely to due virtual camber of the higher
+chord-to-radius ratio of the UNH-RVAT blades.
 

### 2016-01-20 paper.tex
Last of @nearyvs suggestions; resolves #46

@@
 
-The wake at $x/D=0.93$ downstream was shown to be relatively symmetrical and
-lacked the evidence of strong blade stall, which once again differentiates this
-turbine from the UNH-RVAT. Terms from the mean kinetic energy transport equation
-were also computed in this $y$--$z$ plane, showing the relative importance of
-the vertical advection compared with turbulent transport terms at this location.
-It is interesting to note that though the RM2 is a more effective energy
-converter than the UNH-RVAT, its wake recovery may in fact be slower due to
-weaker blade tip vortex shedding and lower levels of turbulence in the
-near-wake.
+While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
+$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
+evidence of strong blade stall, both of which differentiate this near-wake from
+the higher solidity, lower optimal $\lambda$ UNH-RVAT. Terms from the mean
+kinetic energy transport equation were also computed in this $y$--$z$ plane,
+showing the relative importance of the vertical advection compared with
+turbulent transport terms at this location. It is interesting to note that
+though the RM2 is a more effective energy converter than the UNH-RVAT, its wake
+recovery may in fact be delayed due to weaker blade tip vortex shedding and
+lower levels of turbulence in the near-wake.
 
-This data, along with the code for processing and visualization, is provided
+This dataset, along with the code for processing and visualization, is provided
 openly via a Creative Commons license (MIT license for code), and is available
 as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
-citeable archive \cite{Bachant2015-RM2-data}. The authors hope that this can
-provide opportunities for extensive validation of predictive tools for the
-complex unsteady flow physics of cross-flow turbines.
+citeable archive \cite{Bachant2015-RM2-data}.
 

### 2016-01-20 paper.tex
Note nearly identical measurements from the torque arm; resolves #24

@@
 capacity inline rotary torque transducer \cite{InterfaceT8}. An additional
-Sentran ZB load cell mounted at a fixed distance from the servo motor via a
-moment arm provided a redundant torque measurement. Turbine shaft angle was
-measured using the Kollmorgen AKD servo drive's emulated encoder output
-\cite{KollmorgenAKD}, set to $10^5$ counts per turbine shaft revolution.
-Carriage speed, and therefore inflow velocity was measured using a Renishaw LM15
-linear encoder with 10 $\mu$m resolution \cite{RenishawLM15}. All of these
-performance-related quantities were sampled at 2 kHz, while the tow tank's
-motion controller provided redundant measurements of the carriage speed turbine
-angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
-downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter
-\cite{NortekVectrino}, sampling at 200 Hz. A photo and drawing of the
-experimental setup are shown in Fig.~\ref{fig:exp-setup-photo} and
-Fig.~\ref{fig:exp-setup}, respectively.
+Sentran ZB3 load cell mounted at a fixed distance from the servo motor via a
+moment arm provided a redundant torque measurement, measurements from which were
+nearly identical to the inline transducer, providing additional confidence in
+the results. Turbine shaft angle was measured using the Kollmorgen AKD servo
+drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
+turbine shaft revolution. Carriage speed, and therefore inflow velocity was
+measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
+\cite{RenishawLM15}. All of these performance-related quantities were sampled at
+2 kHz, while the tow tank's motion controller provided redundant measurements of
+the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
+measurements at 1 meter downstream were measured with a Nortek Vectrino+
+acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
+and drawing of the experimental setup are shown in
+Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
 

### 2016-01-20 paper.tex
Investigation --> study; resolves #37

@@
 
-{\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
-        turbine at transitional Reynolds numbers: Power production, strut losses, and
-        near-wake dynamics}} \newline % Insert author names, affiliations
+{\Large \textbf\newline{Experimental study of a low solidity cross-flow turbine
+        at transitional Reynolds numbers: Power production, strut losses, and near-wake
+        dynamics}} \newline % Insert author names, affiliations
 % and corresponding author email (do not

### 2016-01-20 paper.tex
Simplify wording

@@
 efforts can easily incorporate finite domains, meaning blockage corrections
-could create an additional variable to obfuscate validation efforts.
+could complicate validation efforts.
 

### 2016-01-20 paper.tex
Blockage ratio is slightly lower

@@
 lower acceleration around the turbine due to the lower rotor drag coefficient
-and blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is relatively
-weaker, which is likely an effect of the RM2's smaller blade chord length and
-tapered blades.
+and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
+relatively weaker, which is likely an effect of the RM2's smaller blade chord
+length and tapered blades.
 

### 2016-01-20 paper.tex
Remove repeated word

@@
 which indicates that the RM2 blades are operating further from
-stall---consistent with the higher tip speed ratio operation.
+stall---consistent with its higher optimal tip speed ratio.
 

### 2016-01-20 paper.tex
Fix typo
Reynold --> Reynolds

@@
 Analysis of the near-wake of the higher solidity UNH-RVAT turbine revealed that
-vertical advection was the largest contributer to streamwise recovery
+vertical advection was the largest contributor to streamwise recovery
 \cite{Bachant2015-JoT}, a trait which is considered an advantage of cross-flow
@@
 between this turbine and the higher solidity UNH-RVAT, tested in nearly
-identical conditions, which showed similar Reynold number thresholds but a
+identical conditions, which showed similar Reynolds number thresholds but a
 flatter linear regime, likely to due virtual camber of the higher

### 2016-01-20 paper.tex
Use lambda_0 for optimal TSR

@@
 evidence of strong blade stall, both of which differentiate this near-wake from
-the higher solidity, lower optimal $\lambda$ UNH-RVAT. Terms from the mean
-kinetic energy transport equation were also computed in this $y$--$z$ plane,
-showing the relative importance of the vertical advection compared with
-turbulent transport terms at this location. It is interesting to note that
-though the RM2 is a more effective energy converter than the UNH-RVAT, its wake
-recovery may in fact be delayed due to weaker blade tip vortex shedding and
-lower levels of turbulence in the near-wake.
+the higher solidity, lower $\lambda_0$ UNH-RVAT. Terms from the mean kinetic
+energy transport equation were also computed in this $y$--$z$ plane, showing the
+relative importance of the vertical advection compared with turbulent transport
+terms at this location. It is interesting to note that though the RM2 is a more
+effective energy converter than the UNH-RVAT, its wake recovery may in fact be
+delayed due to weaker blade tip vortex shedding and lower levels of turbulence
+in the near-wake.
 

### 2016-01-20 paper.tex
Add point about scale threshold for numerical model validation
Near wake velocity was measured

@@
 
-The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
+The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
 physical reference model vertical-axis cross-flow turbine were measured
@@
 
-The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
-turbine was measured in a towing tank.
+The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
+cross-flow turbine was measured in a towing tank.
 
@@
 flatter linear regime, likely to due virtual camber of the higher
-chord-to-radius ratio of the UNH-RVAT blades.
+chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results
+indicate an important transitional scale threshold beyond which data should be
+taken for numerical model validation, in order to stay relevant to full scale
+devices.
 

### 2016-01-20 paper.tex
Move strut drag before wake in abstract
Use lambda_0
Add Martin's email address and complete addresses; resolves #47

@@
 % titles, positions, or degrees).
-\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
+\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
 Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
 \bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
-NH, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
-Box 5800, Albuquerque, New Mexico 87185-MS1124 \\ \bigskip
+NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
+Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip
 
@@
 % in note below.
-* pxL3@unh.edu
+*pxL3@unh.edu (PB), *martin.wosnik@unh.edu (MW)
 
@@
 numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
-at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
-ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
-at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
-mean kinetic energy transport were compared with results from a high solidity
-turbine acquired with the same test apparatus. Overall, lower levels of
-streamwise wake recovery were calculated for the RM2 case---a consequence of
-both the relatively low solidity and tapered blades reducing blade tip vortex
-shedding---responsible for mean vertical advection---and lower levels of
-turbulence caused by higher operating tip speed ratio and therefore reduced
-dynamic stall. The effects of blade support strut drag on turbine performance
-were investigated by covering the rotor's NACA 0021 struts with cylinders. As
-expected, this modification drastically reduced the rotor power coefficient.
-Strut drag was also measured for the NACA 0021 and cylindrical configurations
-with the blades removed.
+at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of blade
+support strut drag on turbine performance were investigated by covering the
+rotor's NACA 0021 struts with cylinders. As expected, this modification
+drastically reduced the rotor power coefficient. Strut drag was also measured
+for the NACA 0021 and cylindrical configurations with the blades removed. An
+optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake
+velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence
+kinetic energy, and mean kinetic energy transport were compared with results
+from a high solidity turbine acquired with the same test apparatus. Overall,
+lower levels of streamwise wake recovery were calculated for the RM2 case---a
+consequence of both the relatively low solidity and tapered blades reducing
+blade tip vortex shedding---responsible for mean vertical advection---and lower
+levels of turbulence caused by higher operating tip speed ratio and therefore
+reduced dynamic stall.
 
@@
 
-The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
-($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
-velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
-lower acceleration around the turbine due to the lower rotor drag coefficient
-and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
-relatively weaker, which is likely an effect of the RM2's smaller blade chord
-length and tapered blades.
+The mean velocity field at the chosen optimal tip speed ratio $\lambda_0=3.1$, 1
+m downstream ($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean
+streamwise velocity deficit is markedly more symmetric than that of the
+UNH-RVAT, with lower acceleration around the turbine due to the lower rotor drag
+coefficient and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex
+shedding is relatively weaker, which is likely an effect of the RM2's smaller
+blade chord length and tapered blades.
 

### 2016-01-21 paper.tex
Add pertinent results to abstract and conclusion; resolves #33

@@
 validating numerical models. Performance was measured at multiple Reynolds
-numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
-at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of blade
-support strut drag on turbine performance were investigated by covering the
-rotor's NACA 0021 struts with cylinders. As expected, this modification
-drastically reduced the rotor power coefficient. Strut drag was also measured
-for the NACA 0021 and cylindrical configurations with the blades removed. An
-optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake
-velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence
-kinetic energy, and mean kinetic energy transport were compared with results
-from a high solidity turbine acquired with the same test apparatus. Overall,
-lower levels of streamwise wake recovery were calculated for the RM2 case---a
-consequence of both the relatively low solidity and tapered blades reducing
-blade tip vortex shedding---responsible for mean vertical advection---and lower
-levels of turbulence caused by higher operating tip speed ratio and therefore
-reduced dynamic stall.
+numbers by varying tow carriage speed. A peak power coefficient $C_P = 0.37$ and
+rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
+$\lambda_0 = 3.1$. Weak linear $Re$-dependence was achieved at a turbine
+diameter Reynolds number $Re_D \approx 10^6$. The effects of blade support strut
+drag on turbine performance were investigated by covering the rotor's NACA 0021
+struts with cylinders. As expected, this modification drastically reduced the
+rotor power coefficient. Strut drag was also measured for the NACA 0021 and
+cylindrical configurations with the blades removed. For $\lambda=\lambda_0$,
+wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
+turbulence kinetic energy, and mean kinetic energy transport were compared with
+results from a high solidity turbine acquired with the same test apparatus. Like
+the high solidity case, mean vertical advection was calculated to be the largest
+contributor to near-wake recovery. However, overall, lower levels of streamwise
+wake recovery were calculated for the RM2 case---a consequence of both the
+relatively low solidity and tapered blades reducing blade tip vortex
+shedding---responsible for mean vertical advection---and lower levels of
+turbulence caused by higher operating tip speed ratio and therefore reduced
+dynamic stall. However,
 
@@
 The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
-cross-flow turbine was measured in a towing tank.
+cross-flow turbine was measured in a towing tank. A maximum power coefficient
+$C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were observed at an optimal
+tip speed ratio $\lambda_0 = 3.1$.
 
@@
 relative importance of the vertical advection compared with turbulent transport
-terms at this location. It is interesting to note that though the RM2 is a more
-effective energy converter than the UNH-RVAT, its wake recovery may in fact be
-delayed due to weaker blade tip vortex shedding and lower levels of turbulence
-in the near-wake.
+terms at this location, which is qualitatively similar to the UNH-RVAT wake
+data. However, lower wake recover totals were calculated. This indicates that
+although the RM2 is a more effective energy converter than the UNH-RVAT, its
+wake recovery may in fact be delayed due to weaker blade tip vortex shedding and
+lower levels of turbulence in the near-wake, which may present a trade-off when
+considering optimal array layouts.
 

### 2016-01-22 paper.tex
Update BibTeX key

@@
 $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
-Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that performance and
+Wosnik \cite{Bachant2014, Bachant2016-RVAT-Re-dep} showed that performance and
 near-wake characteristics of a high solidity cross-flow turbine become Reynolds
@@
 transition to turbulence closer to the leading edge \cite{Lissaman1983,
-    McMasters1980, Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer
+    McMasters1980, Bachant2016-RVAT-Re-dep}, which helps flow remain attached longer
 as it moves against the adverse pressure gradient on the suction side of the
@@
 \cite{Migliore1980}---when compared to the strong $Re$-independence of the
-higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
+higher $c/R$ UNH-RVAT \cite{Bachant2016-RVAT-Re-dep}.
 

### 2016-02-18 paper.tex
Start summary of validation datasets

@@
 a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
+
+\subsection*{Survey of Validation Data Usage}
+
+A selection of measured performance data in the literature and its usage in
+numerical model validation is presented in Table~\ref{tab:validation-data}.
+
+\begin{table}
+    \centering
+
+    \begin{tabular}{c|c|c|c|c|c}
+        Name & Rotor type & $N_\mathrm{b}$ & $c/R$ & $Re_D$ & Used in \\ 
+        \hline
+        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013} \\ 
+        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008} \\ 
+        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015} \\ 
+        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011}  \\ 
+        Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\ 
+        Laneville and Vitecoq \cite{Laneville1986} & H & 2 & 0.13 & $\sim 10^6$ & \cite{Amet2009} \\ 
+        Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\ 
+        Penna QR5 \cite{Penna2008} & Helical & 3 & ? & $\sim 10^6$ & \cite{Scheurich2011} \\ 
+        Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\ 
+        VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\ 
+        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014}
+    \end{tabular}
+
+    \caption{\textbf{Performance validation data.} Selected measured performance
+        data and its usage for numerical model validation. Note that individual
+        blade forces were measured in the Strickland \emph{et al.} and Laneville and
+        Vitecoq experiments.}
+
+    \label{tab:validation-data}
+\end{table}
 

### 2016-02-18 paper.tex
Add some turbine geometry details
Add some commentary on existing data

@@
 numerical model validation is presented in Table~\ref{tab:validation-data}.
+Turbine diameter Reynolds numbers spanned from small laboratory scale ($Re_D
+\sim 10^5$) all the way to full scale ($Re_D \sim 10^7$). Individual blade
+forces were only measured in two of the experiments---Strickland \emph{et al.}
+\cite{Strickland1981} and Laneville and Vitecoq \cite{Laneville1986}. There has
+been nearly equal attention given to the eggbeater-shaped Darrieus rotor and the
+straight-bladed H-rotor. The two additional rotors studied were the large scale
+tapered H-rotor VAWT 850 \cite{Mays1990} and the helical Quiet Revolution QR5
+measured by Penna \cite{Penna2008}, the exact geometry for which is unknown.
 
@@
 \end{table}
+
+In general, there have been more experiments done with rotors of low $c/R$,
+which makes them easier to model, since unsteady dynamic effects are less
+influential on the overall performance \cite{Strickland1981}. This is apparent
+when examining the effectiveness of numerical models that rely on static foil
+coefficient input data, e.g., streamtube and vortex models, which seem to be
+most applicable for $c/R \leq 0.1$.
 
@@
 \end{figure}
+
+The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
+taper from 0.04 m at the tips to 0.067 m at the roots, or half-span. Mean
+chord-to-radius ratio $c/R$ was 0.1, which is approximately at the threshold
+between high and low solidity \cite{Strickland1981,Fiedler2009}. This rotor
+geometry presents a unique validation case not yet seen in the literature,
+similar in concept to the VAWT 850 \cite{Mays1990} with its tapered blades, but
+with a moderately high $c/R$ to more accurately represent typical MHK rotors,
+which presents a challenge for numerical modeling.
 

### 2016-02-18 paper.tex
Add 'and' to heading
Elaborate on effects of virtual camber; resolves #27

@@
 
-\subsection*{Survey of Validation Data Usage}
+\subsection*{Survey of Validation Data and Usage}
 
@@
 positive trend. The tendency of $C_P$ to continue increasing slightly could be
-an effect of lower ``virtual camber''---or flow curvature
-\cite{Migliore1980}---when compared to the strong $Re$-independence of the
-higher $c/R$ UNH-RVAT \cite{Bachant2016-RVAT-Re-dep}.
+an effect of flow curvature---caused by the finite $c/R$---which imparts a
+``virtual camber'' \cite{Migliore1980}, or can be thought of as producing a
+``lead'' in angle of attack since cambered airfoils have non-zero lift at zero
+angle of attack \cite{Goude2012}. The weaker $Re$-independence of the RM2
+compared to that of the higher $c/R$ UNH-RVAT could be due to this virtual
+camber effect, since camber has been shown to cause earlier $Re$-convergence of
+the CFT's geometric torque coefficient when calculated from static foil
+coefficients given by a viscous panel method, whereas characteristics like
+lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.
 

### 2016-02-18 paper.tex
Discuss Bedon et al (2014) a bit; resolves #61

@@
         \hline
-        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013} \\ 
-        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008} \\ 
-        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015} \\ 
-        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011}  \\ 
+        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013,Bedon2014} \\ 
+        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008,Bedon2014} \\ 
+        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015,Bedon2014} \\ 
+        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011,Bedon2014}  \\ 
         Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\ 
@@
 coefficient input data, e.g., streamtube and vortex models, which seem to be
-most applicable for $c/R \leq 0.1$.
+most applicable for $c/R \leq 0.1$. For example, Bedon \emph{et al.}
+\cite{Bedon2014} used a double multiple streamtube momentum model without
+dynamic stall corrections to evaluate the effectiveness of various foil
+coefficient databases against the Sandia Darrieus turbine experimental data.
+Despite using such a simple model, performance predictions were quite accurate
+in most conditions except at low tip speed ratio for the 2 m turbine, which had
+the highest $c/R$ of all the Sandia rotors, making the dynamic effects more
+important. This point highlights the need for more validation data for higher
+solidity rotors to ensure numerical models are robust enough to explore unique
+cross-flow turbine designs.
 

### 2016-02-19 paper.tex
Title case

@@
 
-{\Large \textbf\newline{Experimental study of a low solidity cross-flow turbine
-        at transitional Reynolds numbers: Power production, strut losses, and near-wake
-        dynamics}} \newline % Insert author names, affiliations
+{\Large \textbf\newline{Experimental Study of a Low Solidity Cross-Flow Turbine
+        at Transitional Reynolds Numbers: Power Production, Strut Losses, and Near-Wake
+        Dynamics}} \newline % Insert author names, affiliations
 % and corresponding author email (do not
@@
 \bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
-NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
-Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip
+NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
+P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip
 

### 2016-02-19 paper.tex
Clean up abstract

@@
 rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
-$\lambda_0 = 3.1$. Weak linear $Re$-dependence was achieved at a turbine
-diameter Reynolds number $Re_D \approx 10^6$. The effects of blade support strut
-drag on turbine performance were investigated by covering the rotor's NACA 0021
-struts with cylinders. As expected, this modification drastically reduced the
-rotor power coefficient. Strut drag was also measured for the NACA 0021 and
-cylindrical configurations with the blades removed. For $\lambda=\lambda_0$,
-wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
-turbulence kinetic energy, and mean kinetic energy transport were compared with
-results from a high solidity turbine acquired with the same test apparatus. Like
-the high solidity case, mean vertical advection was calculated to be the largest
-contributor to near-wake recovery. However, overall, lower levels of streamwise
-wake recovery were calculated for the RM2 case---a consequence of both the
-relatively low solidity and tapered blades reducing blade tip vortex
-shedding---responsible for mean vertical advection---and lower levels of
-turbulence caused by higher operating tip speed ratio and therefore reduced
-dynamic stall. However,
+$\lambda_0 = 3.1$. Weak linear $Re$-dependence of the power coefficient was
+achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects
+of blade support strut drag on turbine performance were investigated by covering
+the rotor's NACA 0021 struts with cylinders. As expected, this modification
+drastically reduced the rotor power coefficient. Strut drag losses were also
+measured for the NACA 0021 and cylindrical configurations with the blades
+removed. For $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$
+downstream. Mean velocity, turbulence kinetic energy, and mean kinetic energy
+transport were compared with results from a high solidity turbine acquired with
+the same test apparatus. Like the high solidity case, mean vertical advection
+was calculated to be the largest contributor to near-wake recovery. However,
+overall, lower levels of streamwise wake recovery were calculated for the RM2
+case---a consequence of both the relatively low solidity and tapered blades
+reducing blade tip vortex shedding---responsible for mean vertical
+advection---and lower levels of turbulence caused by higher operating tip speed
+ratio and therefore reduced dynamic stall.
 

### 2016-02-19 paper.tex
Discuss the fact that MHK rotors are usually more solid

@@
 produced six marine hydrokinetic (MHK) technology point designs as reference
-models (RM) to serve as non-proprietary test articles for open research
+models (RMs) to serve as non-proprietary test articles for open research
 development, and to benchmark performance and costs for technology developers
@@
 RM device to allow exact replication for physical and numerical modeling
-studies; Resource site information used to design each RM device; and references
+studies; resource site information used to design each RM device; and references
 to physical modeling data sets that can be used to validate numerical modeling
@@
 3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
-and radius, respectively. An initial experimental measurement campaign with a
-1:15 scale RM2 rotor conducted at the Saint Anthony Falls Laboratory (SAFL) at
-the University of Minnesota resulted in maximum power coefficient of
-approximately 5\% at $\lambda = 2.2$. This discrepancy between numerical and
-physical model performance prompted the experimental measurements presented
-here, namely due to the low Reynolds number---$Re_D = U_\infty D / \nu$, where
-$U_\infty$ is the free stream velocity, $D$ is the rotor diameter, and $\nu$ is
-the fluid kinematic viscosity---of the 1:15 scale tests, which were performed at
-$Re_D \sim 10^5$ \cite{Hill2014}.
+and radius, respectively. Note that the RM2 rotor solidity would be considered
+moderate to high for a wind turbine, but MHK rotors are typically higher
+solidity since they must withstand approximately an order of magnitude higher
+torque in typical flows, necessitating relatively larger blades to meet strength
+and fatigue life requirements.
+
+An initial experimental measurement campaign with a 1:15 scale RM2 rotor
+conducted at the Saint Anthony Falls Laboratory (SAFL) at the University of
+Minnesota resulted in maximum power coefficient of approximately 5\% at $\lambda
+= 2.2$. This discrepancy between numerical and physical model performance
+prompted the experimental measurements presented here, namely due to the low
+Reynolds number---$Re_D = U_\infty D / \nu$, where $U_\infty$ is the free stream
+velocity, $D$ is the rotor diameter, and $\nu$ is the fluid kinematic
+viscosity---of the 1:15 scale tests, which were performed at $Re_D \sim 10^5$
+\cite{Hill2014}.
 

### 2016-02-19 paper.tex
Note how lower solidity turbines will operate at higher TSR

@@
 from rotor blade support struts could play an important role in overall turbine
-performance. Thus, the parasitic torque from strut drag was measured without
+performance, especially for a lower solidity turbine that operates at higher tip
+speed ratios. Thus, the parasitic torque from strut drag was measured without
 blades, then deliberately and significantly increased in the physical model to

### 2016-02-19 paper.tex
Add another comment about importance to MHK

@@
 tapered H-rotor VAWT 850 \cite{Mays1990} and the helical Quiet Revolution QR5
-measured by Penna \cite{Penna2008}, the exact geometry for which is unknown.
+measured by Penna \cite{Penna2008}, the exact geometrical details for which are
+not available.
+
+\todo[inline]{Remove QR5 data, since without geometry, no one else can use the
+    data for validation?}
 
@@
 when examining the effectiveness of numerical models that rely on static foil
-coefficient input data, e.g., streamtube and vortex models, which seem to be
-most applicable for $c/R \leq 0.1$. For example, Bedon \emph{et al.}
-\cite{Bedon2014} used a double multiple streamtube momentum model without
-dynamic stall corrections to evaluate the effectiveness of various foil
-coefficient databases against the Sandia Darrieus turbine experimental data.
-Despite using such a simple model, performance predictions were quite accurate
-in most conditions except at low tip speed ratio for the 2 m turbine, which had
-the highest $c/R$ of all the Sandia rotors, making the dynamic effects more
-important. This point highlights the need for more validation data for higher
-solidity rotors to ensure numerical models are robust enough to explore unique
-cross-flow turbine designs.
+coefficient input data, e.g., streamtube and vortex models, which are most
+applicable for $c/R \leq 0.1$. For example, Bedon \emph{et al.}~\cite{Bedon2014}
+used a double multiple streamtube momentum model without dynamic stall
+corrections to evaluate the effectiveness of various foil coefficient databases
+against the Sandia Darrieus turbine experimental data. Despite using such a
+simple model, performance predictions were quite accurate in most conditions
+except at low tip speed ratio for the 2 m turbine, which had the highest $c/R$
+of all the Sandia rotors, making the dynamic effects more important. This point
+highlights the need for more validation data for higher solidity rotors to
+ensure numerical models are robust enough to explore unique cross-flow turbine
+designs, especially as the MHK concepts mature.
 

### 2016-02-19 scripts/makefigs.sh
Correct no-show arg in makefigs script

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
 
 cd RM2-tow-tank
-python plot.py --all --save --noshow
+python plot.py --all --save --no-show
 cd ..
 python scripts/getfigs.py

### 2016-02-19 scripts/getfigs.py
Add script to make/copy figures from RVAT-Re-dep submodule

@@ -1,20 +1,42 @@
 #!/usr/bin/env python
-"""This script copies figures from the RM2 tow tank experiment directory."""
+"""This script copies figures into the figures directory."""
 
 import os
 import sys
 import shutil
 
-figdir = os.path.join("RM2-tow-tank", "Figures")
 
-figlist = ["cp_curves.eps",
-           "cd_curves.eps",
-           "perf_re_dep.eps",
-    	   "meancontquiv.eps",
-           "k_contours.eps",
-    	   "K_trans_bar_graph.eps",
-    	   "no_blades_all.eps",
-    	   "perf_covers.eps"]
+def fix_eps(fpath):
+    """Fix carriage returns in EPS files caused by Arial font."""
+    txt = b""
+    with open(fpath, "rb") as f:
+        for line in f:
+            if b"\r\rHebrew" in line:
+                line = line.replace(b"\r\rHebrew", b"Hebrew")
+            txt += line
+    with open(fpath, "wb") as f:
+        f.write(txt)
 
-for fig in figlist:
-    shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))
+
+if __name__ == "__main__":
+    # Get RM2 figs
+    figdir = os.path.join("RM2-tow-tank", "Figures")
+    figlist = ["cp_curves.eps",
+               "cd_curves.eps",
+               "perf_re_dep.eps",
+        	   "meancontquiv.eps",
+               "k_contours.eps",
+        	   "K_trans_bar_graph.eps",
+        	   "no_blades_all.eps",
+        	   "perf_covers.eps"]
+    for fig in figlist:
+        shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fig))
+
+    # Get RVAT-Re-dep figs
+    figdir = os.path.join("RVAT-Re-dep", "Figures")
+    figlist = ["meancontquiv_10.eps", "k_contours_10.eps"]
+
+    for fig in figlist:
+        fix_eps(os.path.join(figdir, fig))
+        fign = "RVAT-Re-dep-" + fig
+        shutil.copy2(os.path.join(figdir, fig), os.path.join("figures", fign))

### 2016-02-19 scripts/make-rvat-figs.sh

@@ -1,0 +1,6 @@
+#!/usr/bin/env bash
+
+cd RVAT-Re-dep
+python plot.py all_meancontquiv all_kcont --save --savetype .eps --no-show
+cd ..
+python scripts/getfigs.py

### 2016-02-19 paper.tex
Allow automatic float placement
Add RVAT description and wake figs; resolves #28

@@
 
+The UNH-RVAT, for which the performance, near-wake, and Reynolds number
+dependence of was investigated using the same experimental setup as the study
+here \cite{Bachant2015-JoT, Bachant2016-Energies}, was an H-rotor of 1 m height
+and 1 m diameter. The UNH-RVAT experimental datasets are also openly available
+\cite{Bachant2014-RVAT-baseline, Bachant2016-RVAT-Re-dep}, and provide an
+interesting comparison for the near-wake dynamics of a rotor similar in scale to
+the 1:6 RM2, but with non-tapered blades and a high solidity $c/R = 0.28$.
+
 \section*{Materials and Methods}
@@
 
-\begin{figure}[h]
+\begin{figure}
     \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
@@
 
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
 
-\begin{table}[ht]
+\begin{table}
 \centering
@@
 
-\begin{figure}[h]
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
@@
 
-\begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/cp_curves.eps}
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}
 
@@
 
-\begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/cd_curves.eps}
+\begin{figure}
+    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}
 
@@
 
-\begin{figure}[h]
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/perf_covers.eps}
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
@@
 streamwise velocity deficit is markedly more symmetric than that of the
-UNH-RVAT, with lower acceleration around the turbine due to the lower rotor drag
-coefficient and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex
-shedding is relatively weaker, which is likely an effect of the RM2's smaller
-blade chord length and tapered blades.
+UNH-RVAT, shown in Fig.~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower
+acceleration around the turbine due to the lower rotor drag coefficient and a
+slightly lower blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
+relatively weaker, which is likely an effect of the RM2's smaller blade chord
+length and tapered blades.
 
-\begin{figure}[h]
+\begin{figure}
+    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
+
+    \caption{{\bf UNH-RVAT Near-Wake Mean Velocity.} UNH-RVAT near-wake mean
+        velocity field (looking upstream) at 1 m downstream ($x/D=1.0$),
+        $U_\infty=1.0$ m/s, and $\lambda=1.9$, from \cite{Bachant2016-Energies}.
+        Solid dark gray lines indicate turbine frontal area.}
+
+    \label{fig:rvat-meancontquiv}
+\end{figure}
+
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
 
-    \caption{{\bf Mean Velocity.} Mean velocity field (looking upstream) at 1 m
-    downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Refer to
-    Fig.~\ref{fig:coordinates} for turbine axis orientation. Solid dark gray
-    lines indicate turbine frontal area.}
+    \caption{{\bf RM2 Near-Wake Mean Velocity.} RM2 near-wake mean velocity
+        field (looking upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s,
+        and $\lambda=3.1$. Refer to Fig.~\ref{fig:coordinates} for turbine axis
+        orientation. Solid dark gray lines indicate turbine frontal area.}
 
@@
 mainly see unsteadiness in the flow generated by the blade tip vortex shedding
-(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
-generation is lower overall, without the intense vertical band around $y/R=-1$,
-which indicates that the RM2 blades are operating further from
-stall---consistent with its higher optimal tip speed ratio.
+(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, shown in
+Fig.~\ref{fig:rvat-kcont}, turbulence generation is lower overall, without the
+intense vertical band around $y/R=-1$, which indicates that the RM2 blades are
+operating further from stall---consistent with its higher optimal tip speed
+ratio.
 
-\begin{figure}[h]
+\begin{figure}
+    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
+
+    \caption{{\bf UNH-RVAT Near-Wake Turbulence Kinetic Energy.} Turbulence
+        kinetic energy in the UNH-RVAT's near-wake (looking upstream) at 1 m
+        downstream ($x/D=1.0$), $U_\infty=1.0$ m/s, and $\lambda=1.9$, from
+        \cite{Bachant2016-Energies}. Solid black lines indicate turbine frontal
+        area.}
+
+    \label{fig:rvat-kcont}
+\end{figure}
+
+\begin{figure}
     \includegraphics[width=\textwidth]{figures/k_contours.eps}
 
-    \caption{{\bf Turbulence Kinetic Energy.} Turbulence kinetic energy (looking
-    upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
-    $\lambda=3.1$. Solid black lines indicate turbine frontal area.}
+    \caption{{\bf RM2 near-wake Turbulence Kinetic Energy.} Turbulence kinetic
+        energy in the RM2's near-wake (looking upstream) at 1 m downstream
+        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
+        indicate turbine frontal area.}
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

### 2016-02-19 paper.tex
Title case

@@
 
-    \caption{{\bf RM2 near-wake Turbulence Kinetic Energy.} Turbulence kinetic
+    \caption{{\bf RM2 Near-Wake Turbulence Kinetic Energy.} Turbulence kinetic
         energy in the RM2's near-wake (looking upstream) at 1 m downstream

### 2016-02-22 paper.tex
Shorten title and call turbine medium solidity

@@
 
-{\Large \textbf\newline{Experimental Study of a Low Solidity Cross-Flow Turbine
-        at Transitional Reynolds Numbers: Power Production, Strut Losses, and Near-Wake
-        Dynamics}} \newline % Insert author names, affiliations
+{\Large \textbf\newline{Experimental Study of a Medium Solidity Cross-Flow
+        Turbine with Tapered Blades}} \newline % Insert author names,
+% affiliations
 % and corresponding author email (do not

### 2016-02-22 paper.tex
Discuss solidity range

@@
 The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
-taper from 0.04 m at the tips to 0.067 m at the roots, or half-span. Mean
-chord-to-radius ratio $c/R$ was 0.1, which is approximately at the threshold
-between high and low solidity \cite{Strickland1981,Fiedler2009}. This rotor
-geometry presents a unique validation case not yet seen in the literature,
-similar in concept to the VAWT 850 \cite{Mays1990} with its tapered blades, but
-with a moderately high $c/R$ to more accurately represent typical MHK rotors,
-which presents a challenge for numerical modeling.
+taper from 0.04 m at the tips to 0.067 m at the roots, or half-span, varying the
+chord-to-radius ratio $c/R$ from 0.07 to 0.12 (0.1 average). The rotor was
+therefore approximately at the threshold between high and low solidity
+\cite{Strickland1981,Fiedler2009}, which presents a unique validation case not
+yet seen in the literature, similar in concept to the VAWT 850 \cite{Mays1990}
+with its tapered blades, but with a moderately high $c/R$ to more accurately
+represent typical MHK rotors, which presents a challenge for numerical modeling.
 

### 2016-02-22 paper.tex
Add reference model to title
Add comment on how low Re results are consistent with SAFL

@@
 
-{\Large \textbf\newline{Experimental Study of a Medium Solidity Cross-Flow
+{\Large \textbf\newline{Experimental Study of a Reference Model Cross-Flow
         Turbine with Tapered Blades}} \newline % Insert author names,
@@
 \nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
-positive trend. The tendency of $C_P$ to continue increasing slightly could be
+positive trend. At the lowest Reynolds number, mean power coefficient even drops
+below zero, which is consistent with the low performance of the 1:15 scale RM2
+physical model study~\cite{Hill2014}.
+
+The tendency of $C_P$ to continue increasing slightly could be
 an effect of flow curvature---caused by the finite $c/R$---which imparts a

### 2016-02-22 paper.tex
Compare performance results with SAFL; resolves #35

@@
 below zero, which is consistent with the low performance of the 1:15 scale RM2
-physical model study~\cite{Hill2014}.
+physical model study~\cite{Hill2014}. However, the blades of the 1:15 scale RM2
+were mounted at approximately 58\% of the chord from the leading edge, versus
+50\% for the present model, which helps explain the 1:15 scale model's positive
+power output at $\lambda=2.2$ and $Re_D \sim 10^5$, since moving the blade mount
+point further back is equivalent to a ``toe-out'' preset pitch
+condition~\cite{Fiedler2009}.
 

### 2016-02-23 paper.tex
Refine RM2 description in intro

@@
 that was designed to operate in a reach of the lower Mississippi River near
-Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three blades,
-a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R$, and a
-preliminary analysis with Sandia's CACTUS vortex line numerical model
-\cite{Murray2011} predicted a full-scale performance coefficient of 47\% at 1
-m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
-3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
-and radius, respectively. Note that the RM2 rotor solidity would be considered
-moderate to high for a wind turbine, but MHK rotors are typically higher
-solidity since they must withstand approximately an order of magnitude higher
-torque in typical flows, necessitating relatively larger blades to meet strength
-and fatigue life requirements.
+Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three tapered
+blades and a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R
+\approx 0.1$. A preliminary analysis with Sandia's CACTUS vortex line numerical
+model \cite{Murray2011} predicted an individual rotor's full-scale performance
+coefficient to be 47\% at 1 m/s flow speed and a tip speed ratio $\lambda \equiv
+\frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where $\omega$ and $R$ are
+the rotor's angular velocity and radius, respectively. Note that the RM2 rotor
+solidity would be considered moderate to high for a wind turbine, but MHK rotors
+are typically higher solidity since they must withstand approximately an order
+of magnitude higher torque in typical flows, necessitating relatively larger
+blades to meet strength and fatigue life requirements.
 

### 2016-02-23 paper.tex
Spelling of the word 'citable'

@@
 code) as a Git repository on GitHub
-(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable archive with
-a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
+(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
+digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
 
@@
 as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
-citeable archive \cite{Bachant2015-RM2-data}.
+citable archive \cite{Bachant2015-RM2-data}.
 

### 2016-02-23 paper.tex
Add RVAT Re_D

@@
 near-wake characteristics of a high solidity cross-flow turbine become Reynolds
-number independent at $Re_c \approx 2 \times 10^5$.
+number independent at $Re_D \approx 10^6$ or $Re_c \approx 2 \times 10^5$.
 

### 2016-02-23 paper.tex
Remove the QR5 turbine since the data and geometry are not available

@@
 been nearly equal attention given to the eggbeater-shaped Darrieus rotor and the
-straight-bladed H-rotor. The two additional rotors studied were the large scale
-tapered H-rotor VAWT 850 \cite{Mays1990} and the helical Quiet Revolution QR5
-measured by Penna \cite{Penna2008}, the exact geometrical details for which are
-not available.
-
-\todo[inline]{Remove QR5 data, since without geometry, no one else can use the
-    data for validation?}
+straight-bladed H-rotor. The performance of a large scale H-rotor with tapered
+blades, the VAWT 850 \cite{Mays1990}, has also been measured.
 
@@
         Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\ 
-        Penna QR5 \cite{Penna2008} & Helical & 3 & ? & $\sim 10^6$ & \cite{Scheurich2011} \\ 
         Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\ 

### 2016-02-23 paper.tex
Add 'vertical-axis' to title and remove 'with tapered blades'
Refine objective in introduction

@@
 
-{\Large \textbf\newline{Experimental Study of a Reference Model Cross-Flow
-        Turbine with Tapered Blades}} \newline % Insert author names,
+{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
+        Cross-Flow Turbine}} \newline % Insert author names,
 % affiliations
@@
 
-The present study was motivated by the need to acquire a new experimental
-dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
-relevant to full-scale modeling. It was hypothesized that the parasitic losses
-from rotor blade support struts could play an important role in overall turbine
-performance, especially for a lower solidity turbine that operates at higher tip
-speed ratios. Thus, the parasitic torque from strut drag was measured without
-blades, then deliberately and significantly increased in the physical model to
-provide data to investigate its importance. The velocity field in the near-wake
-of the turbine was then measured to compare with measurements from a higher
-solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
-provide validation data for numerical models that predict wake flows, which
-determine turbine--turbine interaction and optimal spacing for turbine arrays.
-This dataset, along with the code for processing and visualization, is publicly
-available (licensed via Creative Commons CC-BY for data and MIT license for
-code) as a Git repository on GitHub
+The main objective of the present study was to acquire a new experimental
+dataset for the RM2 turbine at sufficient Reynolds numbers to be relevant to
+full-scale physical and numerical modeling. It was hypothesized that the
+parasitic losses from rotor blade support struts could play an important role in
+overall turbine performance, especially for a lower solidity turbine that
+operates at higher tip speed ratios. Thus, the parasitic torque from strut drag
+was measured without blades, then deliberately and significantly increased in
+the physical model to provide data to investigate its importance. The velocity
+field in the near-wake of the turbine was then measured to compare with
+measurements from a higher solidity rotor in the same experimental setup
+\cite{Bachant2015-JoT}, and to provide validation data for numerical models that
+predict wake flows, which determine turbine--turbine interaction and optimal
+spacing for turbine arrays. This dataset, along with the code for processing and
+visualization, has been made publicly available (licensed via Creative Commons
+CC-BY for data and MIT license for code) as a Git repository on GitHub
 (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a

### 2016-03-15 paper.tex
Fix ZIP code

@@
 \bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
-NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
+NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
 P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

### 2016-03-15 paper.tex
Add Wosnik suggestions for abstract

@@
 The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
-physical reference model vertical-axis cross-flow turbine were measured
-experimentally in a towing tank, to provide a comprehensive open dataset for
-validating numerical models. Performance was measured at multiple Reynolds
-numbers by varying tow carriage speed. A peak power coefficient $C_P = 0.37$ and
-rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
-$\lambda_0 = 3.1$. Weak linear $Re$-dependence of the power coefficient was
-achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects
-of blade support strut drag on turbine performance were investigated by covering
-the rotor's NACA 0021 struts with cylinders. As expected, this modification
-drastically reduced the rotor power coefficient. Strut drag losses were also
-measured for the NACA 0021 and cylindrical configurations with the blades
-removed. For $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$
-downstream. Mean velocity, turbulence kinetic energy, and mean kinetic energy
-transport were compared with results from a high solidity turbine acquired with
-the same test apparatus. Like the high solidity case, mean vertical advection
-was calculated to be the largest contributor to near-wake recovery. However,
-overall, lower levels of streamwise wake recovery were calculated for the RM2
-case---a consequence of both the relatively low solidity and tapered blades
-reducing blade tip vortex shedding---responsible for mean vertical
-advection---and lower levels of turbulence caused by higher operating tip speed
-ratio and therefore reduced dynamic stall.
+DOE/Sandia National Labs Reference Model 2 (RM2) vertical-axis cross-flow
+turbine were measured experimentally in a towing tank, to provide a
+comprehensive open dataset for validating numerical models. Performance was
+measured for a range of tip speed ratios and at multiple Reynolds numbers by
+varying the rotor's angular velocity and tow carriage speed, respectively. A
+peak power coefficient $C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were
+observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of weak linear
+$Re$-dependence of the power coefficient was observed above a turbine diameter
+Reynolds number $Re_D \approx 10^6$. The effects of support strut drag on
+turbine performance were investigated by covering the rotor's NACA 0021 struts
+with cylinders. As expected, this modification drastically reduced the rotor
+power coefficient. Strut drag losses were also measured for the NACA 0021 and
+cylindrical configurations with the rotor blades removed. For
+$\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.
+Mean velocity, turbulence kinetic energy, and mean kinetic energy transport were
+compared with results from a high solidity turbine acquired with the same test
+apparatus. Like the high solidity case, mean vertical advection was calculated
+to be the largest contributor to near-wake recovery. However, overall, lower
+levels of streamwise wake recovery were calculated for the RM2 case---a
+consequence of both the relatively low solidity and tapered blades reducing
+blade tip vortex shedding---responsible for mean vertical advection---and lower
+levels of turbulence caused by higher operating tip speed ratio and therefore
+reduced dynamic stall.
 

### 2016-03-15 paper.tex
Add Wosnik edits to introduction

@@
 
-The Reference Model Project (RMP), sponsored by the US Department of Energy,
-produced six marine hydrokinetic (MHK) technology point designs as reference
-models (RMs) to serve as non-proprietary test articles for open research
-development, and to benchmark performance and costs for technology developers
-\cite{Neary2014, Neary2014a}. Open-source RMP products, along with supporting
-documentation, are available at the RMP website
+The Reference Model Project (RMP), sponsored by the US Department of Energy
+(DOE), produced six marine hydrokinetic (MHK) technology point designs as
+reference models (RMs) to serve as non-proprietary test articles for open
+research development, and to benchmark performance and costs for technology
+developers \cite{Neary2014, Neary2014a}. Open-source RMP products, along with
+supporting documentation, are available at the RMP website
 \url{http://energy.sandia.gov/rmp} to facilitate their use in future R\&D
@@
 
-Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
-that was designed to operate in a reach of the lower Mississippi River near
-Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three tapered
-blades and a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R
-\approx 0.1$. A preliminary analysis with Sandia's CACTUS vortex line numerical
-model \cite{Murray2011} predicted an individual rotor's full-scale performance
-coefficient to be 47\% at 1 m/s flow speed and a tip speed ratio $\lambda \equiv
-\frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where $\omega$ and $R$ are
-the rotor's angular velocity and radius, respectively. Note that the RM2 rotor
-solidity would be considered moderate to high for a wind turbine, but MHK rotors
-are typically higher solidity since they must withstand approximately an order
-of magnitude higher torque in typical flows, necessitating relatively larger
-blades to meet strength and fatigue life requirements.
+Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow hydrokinetic
+(river) turbine that was designed to operate in a reach of the lower Mississippi
+River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has
+three tapered blades and a relatively low solidity $Nc/(\pi D)$ or
+chord-to-radius ratio $c/R \approx 0.1$. A preliminary analysis with Sandia's
+CACTUS vortex line numerical model \cite{Murray2011} predicted an individual
+rotor's full-scale performance coefficient to be $C_P=0.47$ at 1 m/s flow speed
+and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$
+\cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity and
+radius, respectively. Note that the RM2 rotor solidity would be considered
+moderate to high for a wind turbine, whose $c/R$ values typically range from
+0.05 to 0.09, but MHK rotors are typically higher solidity since they must
+withstand approximately an order of magnitude higher torque in typical flows,
+necessitating relatively larger blades to meet strength and fatigue life
+requirements.
 
@@
 Minnesota resulted in maximum power coefficient of approximately 5\% at $\lambda
-= 2.2$. This discrepancy between numerical and physical model performance
-prompted the experimental measurements presented here, namely due to the low
-Reynolds number---$Re_D = U_\infty D / \nu$, where $U_\infty$ is the free stream
-velocity, $D$ is the rotor diameter, and $\nu$ is the fluid kinematic
-viscosity---of the 1:15 scale tests, which were performed at $Re_D \sim 10^5$
-\cite{Hill2014}.
+= 2.2$ \cite{Hill2014}. This discrepancy between numerical and physical model
+performance prompted the experimental measurements presented here, namely due to
+the low Reynolds number---$Re_D = U_\infty D / \nu$, where $U_\infty$ is the
+free stream velocity, $D$ is the rotor diameter, and $\nu$ is the fluid
+kinematic viscosity---of the 1:15 scale tests, which were performed at $Re_D
+\sim 10^5$.
 
@@
 \cite{Blackwell1976}: The maximum power coefficient, $C_{P_{\max}}$, increased
-with Reynolds number, $Re_c$ (based on blade chord rather than diameter, though
-these are approximately proportional), along with a shift of the location of
-$C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
-effects of Reynolds number were quite dramatic over a relatively small range of
-$Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
-Wosnik \cite{Bachant2014, Bachant2016-RVAT-Re-dep} showed that performance and
-near-wake characteristics of a high solidity cross-flow turbine become Reynolds
-number independent at $Re_D \approx 10^6$ or $Re_c \approx 2 \times 10^5$.
+with Reynolds number, $Re_c=\lambda U_\infty c / \nu$ (based on blade chord
+rather than diameter, though these are approximately proportional since optimal
+tip speed ratio correlates inversely with solitidy and therefore chord length),
+along with a shift of the location of $C_{P_{\max}}$ toward lower tip speed
+ratios due to delayed blade stall. The effects of Reynolds number were quite
+dramatic over a relatively small range of $Re_c \approx 1.1 \times 10^5$--$2.9
+\times 10^5$. More recently, Bachant and Wosnik \cite{Bachant2014,
+    Bachant2016-RVAT-Re-dep} showed that performance and near-wake characteristics
+of a high solidity cross-flow turbine become Reynolds number independent at
+$Re_D \approx 10^6$ or $Re_c \approx 2 \times 10^5$.
 
@@
 The main objective of the present study was to acquire a new experimental
-dataset for the RM2 turbine at sufficient Reynolds numbers to be relevant to
-full-scale physical and numerical modeling. It was hypothesized that the
+dataset for the RM2 turbine at sufficiently high Reynolds numbers to be relevant
+to full-scale physical and numerical modeling. It was hypothesized that the
 parasitic losses from rotor blade support struts could play an important role in
@@
         VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\ 
-        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014}
+        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014} \\
+        RM2 (present) & Tapered H & 3 & 0.07--0.12 & $\sim 10^6$ & 
     \end{tabular}
@@
 
-In general, there have been more experiments done with rotors of low $c/R$,
-which makes them easier to model, since unsteady dynamic effects are less
-influential on the overall performance \cite{Strickland1981}. This is apparent
-when examining the effectiveness of numerical models that rely on static foil
+In general, there have been more experiments done with low $c/R$ rotors. These
+rotors are easier to model, since unsteady dynamic effects are less influential
+on the overall performance \cite{Strickland1981}. This is apparent when
+examining the effectiveness of numerical models that rely on static foil
 coefficient input data, e.g., streamtube and vortex models, which are most
@@
 except at low tip speed ratio for the 2 m turbine, which had the highest $c/R$
-of all the Sandia rotors, making the dynamic effects more important. This point
+of all the Sandia rotors, making the dynamic effects more important. This
 highlights the need for more validation data for higher solidity rotors to
@@
 \cite{Bachant2014-RVAT-baseline, Bachant2016-RVAT-Re-dep}, and provide an
-interesting comparison for the near-wake dynamics of a rotor similar in scale to
-the 1:6 RM2, but with non-tapered blades and a high solidity $c/R = 0.28$.
+interesting comparison for the near-wake dynamics of a rotor similar in size to
+the 1:6 scale RM2, but with non-tapered blades and a high solidity $c/R = 0.28$.
 

### 2016-03-15 paper.tex
Add Wosnik edits to Materials and Methods section

@@
 The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
-taper from 0.04 m at the tips to 0.067 m at the roots, or half-span, varying the
-chord-to-radius ratio $c/R$ from 0.07 to 0.12 (0.1 average). The rotor was
+taper from 0.067 m at the roots, or half-span, to 0.04 m at the tips, varying
+the chord-to-radius ratio $c/R$ from 0.12 to 0.07 (0.1 average). The rotor was
 therefore approximately at the threshold between high and low solidity
 \cite{Strickland1981,Fiedler2009}, which presents a unique validation case not
-yet seen in the literature, similar in concept to the VAWT 850 \cite{Mays1990}
-with its tapered blades, but with a moderately high $c/R$ to more accurately
-represent typical MHK rotors, which presents a challenge for numerical modeling.
+yet seen in the literature. The RM2 is conceptually similar to the VAWT 850
+\cite{Mays1990} which also had tapered blades, but the RM2 has a moderately high
+$c/R$ to more accurately represent typical MHK rotors, which presents a
+challenge for numerical modeling.
 
 For investigating the effects of support strut drag losses, a set of cylindrical
-covers were designed to slip over the struts, which provided a significant
-increase in strut drag. Endcaps were also fabricated to allow the high drag
-strut cover configuration to be operated without blades. A drawing of the strut
-covers is shown in Fig.~\ref{fig:covers}.
+covers were designed to slip over the struts, which provided a deliberate and
+significant increase in strut drag. Endcaps were also fabricated to allow the
+high drag strut cover configuration to be operated without blades. A drawing of
+the strut covers is shown in Fig.~\ref{fig:covers}.
 
@@
 (wake velocity measurements)---started sampling at precisely the same time each
-tow, after being triggered by a digital signal edge from the motion controller.
-This strategy retained synchronization for all performance signal samples (tow
-speed, torque, drag, angular velocity), ensuring precise calculation of, e.g.,
-power coefficient. Since there was also synchronization of the initial sample
-from each of the three subsystems, correlation of events in the performance and
-wake signals is also possible.
+tow, after being triggered by a digital signal edge sent from the motion
+controller. This strategy retained synchronization for all performance signal
+samples (tow speed, torque, drag, angular velocity), ensuring precise
+calculation of, e.g., power coefficient. Since there was also synchronization of
+the initial sample from each of the three subsystems, correlation of events in
+the performance and wake signals is also possible.
 
@@
 $x/D = 0.93$. The cross-stream and vertical coordinates are shown in
-Fig.~\ref{fig:coordinates}.
+Fig.~\ref{fig:coordinates}. Altogether 750 tows were performed and included in
+the experimental database.
 
@@
 For each tow speed, a relevant quasi-steady duration was selected by manually
-inspecting a plot of the $C_P$ time series, and then truncated to include a
-whole number of blade passages. Over this duration relevant statistics were
-calculated.
+inspecting a plot of the $C_P$ time series. This interval was then truncated to
+include a whole number of blade passages. Relevant statistics were then
+calculated over this duration.
 
@@
 blockage effects were not corrected for. Furthermore, most numerical modeling
-efforts can easily incorporate finite domains, meaning blockage corrections
-could complicate validation efforts.
+efforts can easily incorporate finite domains. Therefore, applying blockage
+corrections to experimental data could actually complicate validation efforts.
 
@@
 \end{equation}
-where $\rho$ is the fluid density (1000 kg/m\textsuperscript{3}) and $A$ is
-the turbine frontal area $DH$.
+where $\rho$ is the fluid density (assumed to be a nominal 1000
+kg/m\textsuperscript{3}) and $A$ is the turbine frontal area $DH$.
 

### 2016-03-15 paper.tex
Add Wosnik edits to results section

@@
 as it moves against the adverse pressure gradient on the suction side of the
-foil. Note how at lower tip speed ratios and Reynolds numbers, $C_P$ becomes
-significantly negative, which was possible thanks to the speed control of the
-experimental setup's servo motor applying negative torque to the rotor.
+foil. For the experiment reported here, a maximum power coefficient $C_P=0.37$
+was reached at $Re_D=1.3 \times 10^6$. Note how at lower tip speed ratios and
+Reynolds numbers, $C_P$ becomes significantly negative, which was possible
+thanks to the speed control of the experimental setup's servo motor applying
+negative torque to the rotor.
 
@@
 Mean rotor drag coefficients are plotted versus tip speed ratio in
-Fig.~\ref{fig:cd-curves}. These $C_D$ curves show fewer differences compared to
+Fig.~\ref{fig:cd-curves}. These $C_D$ curves show little difference compared to
 the power coefficient curves, which is most noticeable at low $\lambda$ and low
@@
 the total resultant force due to high blade drag retains a similar component in
-the streamwise direction.
+the streamwise direction. When operating at maximum power coefficient,
+$\lambda_0=3.1$, and $Re_D=1.3 \times 10^6$, a rotor drag coefficient $C_D=0.84$
+was measured.
 
@@
 
-The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
-Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
-of $C_D$ was observed. The power coefficient of the turbine increases
-dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
-\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
-positive trend. At the lowest Reynolds number, mean power coefficient even drops
-below zero, which is consistent with the low performance of the 1:15 scale RM2
-physical model study~\cite{Hill2014}. However, the blades of the 1:15 scale RM2
-were mounted at approximately 58\% of the chord from the leading edge, versus
-50\% for the present model, which helps explain the 1:15 scale model's positive
-power output at $\lambda=2.2$ and $Re_D \sim 10^5$, since moving the blade mount
-point further back is equivalent to a ``toe-out'' preset pitch
+The effects of Reynolds number on the power and drag coefficients at
+$\lambda=3.1$ are shown in Fig.~\ref{fig:perf-re-dep}. The rotor drag
+coefficient $C_D$ became more or less Reynolds number independent for $Re_D \ge
+0.6 \times 10^6$. The power coefficient of the turbine increased dramatically
+below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c / \nu \approx 2
+\times 10^5$, beyond which there appears to be a small, linear, positive trend.
+At the lowest Reynolds number, mean power coefficient even dropped below zero,
+which is consistent with the low performance of the 1:15 scale RM2 physical
+model study~\cite{Hill2014}. However, the blades of the 1:15 scale RM2 were
+mounted at approximately 58\% of the chord from the leading edge, versus 50\%
+for the present model, which helps explain the 1:15 scale model's positive power
+output at $\lambda=2.2$ and $Re_D \sim 10^5$, since moving the blade mount point
+further back is equivalent to a ``toe-out'' preset pitch
 condition~\cite{Fiedler2009}.
 
-The tendency of $C_P$ to continue increasing slightly could be
-an effect of flow curvature---caused by the finite $c/R$---which imparts a
-``virtual camber'' \cite{Migliore1980}, or can be thought of as producing a
-``lead'' in angle of attack since cambered airfoils have non-zero lift at zero
-angle of attack \cite{Goude2012}. The weaker $Re$-independence of the RM2
-compared to that of the higher $c/R$ UNH-RVAT could be due to this virtual
+The tendency of $C_P$ to continue increasing slightly could be an effect of flow
+curvature---caused by the finite $c/R$---which imparts a ``virtual camber''
+\cite{Migliore1980}, or can be thought of as producing a ``lead'' in angle of
+attack since cambered airfoils have non-zero lift at zero angle of attack
+\cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
+$Re$-independence of the higher $c/R$ UNH-RVAT could be due to this virtual
 camber effect, since camber has been shown to cause earlier $Re$-convergence of
@@
 shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
-struts reduce performance dramatically, which is more pronounced as $\lambda$
-increases. This is in accordance with the measurements of Rawlings
-\cite{Rawlings2008}, though the strut losses in this case are larger due to the
-very high drag profile.
+struts reduce performance dramatically, producing an entirely negative $C_P$
+curve. The detrimental effects of the strut drag were more pronounced at higher
+$\lambda$. This is in accordance with the measurements of Rawlings
+\cite{Rawlings2008}, though the strut losses in this case were larger due to the
+very high drag circular profile. In contrast to the dramatic effect strut drag
+had on $C_P$, overall rotor drag measurements were relatively similar for both
+the cylindrical and NACA 0021 strut cases.
 
@@
 struts---both in towed and stationary conditions. These are computed in the same
-fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the blades removed.
-We see that strut drag losses increase with tip speed ratio to the power 2--3,
-which makes streamlined struts much more important for low solidity turbines,
-given the inverse correlation between solidity and $\lambda_0$
+fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the rotor blades
+removed. We see that strut drag losses increase with tip speed ratio to the
+power 2--3, which makes streamlined struts much more important for low solidity
+turbines, given the inverse correlation between solidity and $\lambda_0$
 \cite{Templin1974}.
@@
 the towed versus stationary configuration, which helps explain why overall rotor
-drag coefficients remained relatively constant even at low Reynolds number,
+drag coefficients remained of comparable magnitude even at low Reynolds number,
 where $C_P$ was dramatically reduced, or even negative. For the cylindrical
 struts, losses increased significantly when towed and operating in the mid range
-of tip speed ratios. Though a real turbine would never use such high drag
-struts, with respect to numerical modeling, these measurements will allow
-support struts to be simulated without blades, to isolate and evaluate the
-ability to predict these losses independent of the blade loading.
+of tip speed ratios.
+
+Though a real turbine would never use such high drag struts, with respect to
+numerical modeling, these measurements provide some interesting validation
+cases. Modelers can isolate and evaluate the ability to predict these losses
+independent of the blade loading by modeling combinations of the rotor with the
+high/low drag struts and with/without blades.
 
@@
 The mean velocity field at the chosen optimal tip speed ratio $\lambda_0=3.1$, 1
-m downstream ($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean
-streamwise velocity deficit is markedly more symmetric than that of the
-UNH-RVAT, shown in Fig.~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower
-acceleration around the turbine due to the lower rotor drag coefficient and a
-slightly lower blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
-relatively weaker, which is likely an effect of the RM2's smaller blade chord
-length and tapered blades.
+m downstream ($x/D=0.93$) from the rotor axis is plotted in
+Fig.~\ref{fig:meancontquiv}. The mean streamwise velocity deficit is markedly
+more symmetric than that of the higher solidity UNH-RVAT, shown in
+Fig.~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower acceleration
+around the turbine due to the lower rotor drag coefficient and a slightly lower
+blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is relatively weaker,
+which is likely an effect of the RM2's smaller blade chord length and tapered
+blades.
 
@@
 energy, rearranged to isolate the streamwise partial derivative (indices follow
-the Einsteinian convention):
+the Einstein summation convention):
 \begin{equation}
@@
 interior points, and a second order inward-facing scheme for the edges,
-identical to \cite{Bachant2015-JoT}. Weighted averages for these computation are
-shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding,
-transport due to vertical advection at this point in the wake was approximately
-3 times lower than the higher solidity UNH-RVAT. Note that direct comparison is
-somewhat invalid, since the total measurement plane area was about 5\% lower for
-this experiment. However, the differences observed are beyond this discrepancy.
-We also see relatively lower levels of cross-stream turbulent transport due to
-the lack of blade stall vortex shedding. These results may have interesting
-implications regarding the application of turbines with lower power coefficient
-to possibly improve overall array performance through enhanced transport of
-kinetic energy from the free stream, though evaluating these trade-offs will
-require a detailed analysis of the downstream evolution and turbine--wake
-interaction.
+following the methodology in \cite{Bachant2015-JoT}. Weighted averages for these
+calculations are shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade
+vortex shedding, transport due to vertical advection at this point in the wake
+was approximately 3 times lower than the higher solidity UNH-RVAT. Note that
+direct comparison is somewhat invalid, since the total measurement plane area
+was about 5\% lower for this experiment. However, the differences observed are
+larger than the area ratio between the two experiments. We also see relatively
+lower levels of cross-stream turbulent transport due to the lack of blade stall
+vortex shedding. These results may have interesting implications regarding the
+application of turbines with lower power coefficient to possibly improve overall
+array performance through enhanced transport of kinetic energy from the free
+stream, though evaluating these trade-offs will require a detailed analysis of
+the downstream evolution and turbine--wake interaction.
 

### 2016-03-15 paper.tex
Add Wosnik edits to conclusions and acknowledgments

@@
 The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
-cross-flow turbine was measured in a towing tank. A maximum power coefficient
+cross-flow turbine were measured in a towing tank. A maximum power coefficient
 $C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were observed at an optimal
@@
 prevented the turbine from producing any mechanical power at any tip speed
-ratio. Nevertheless these measurements provide important validation data for
-both high and low fidelity numerical performance prediction models, allowing
+ratio. Nevertheless these measurements provide useful validation data for both
+high and low fidelity numerical performance prediction models, allowing
 researchers and engineers to test predictions without blade effects.
@@
 terms at this location, which is qualitatively similar to the UNH-RVAT wake
-data. However, lower wake recover totals were calculated. This indicates that
+data. However, lower wake recovery totals were calculated. This indicates that
 although the RM2 is a more effective energy converter than the UNH-RVAT, its
@@
 Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
-(WWPTO). Sandia National Laboratories is a multi-program laboratory managed and
-operated by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
-Corporation, for the U.S. Department of Energy's National Nuclear Security
-Administration under contract DE-AC04-94AL85000.
+(WWPTO). Authors Bachant and Wosnik acknowledge additional support from the
+National Science Foundation, award 1150797. Sandia National Laboratories is a
+multi-program laboratory managed and operated by Sandia Corporation, a wholly
+owned subsidiary of Lockheed Martin Corporation, for the U.S. Department of
+Energy's National Nuclear Security Administration under contract
+DE-AC04-94AL85000.
 

### 2016-03-15 paper.tex
Update RM2 figshare repo

@@
 (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
-digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
+digital object identifier (DOI) \cite{Bachant2016-RM2-data}.
 
@@
 matrix section names and descriptions are provided in the \texttt{README.md}
-file of the experimental data and code repository \cite{Bachant2015-RM2-data}.
+file of the experimental data and code repository \cite{Bachant2016-RM2-data}.
 Tow speed and their corresponding turbine diameter and blade chord Reynolds
@@
 All data processing and plotting code, along with the reduced dataset, are
-available from \cite{Bachant2015-RM2-data}. Note that this code will
+available from \cite{Bachant2016-RM2-data}. Note that this code will
 automatically download raw data as necessary so users can perform a full
@@
 as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
-citable archive \cite{Bachant2015-RM2-data}.
+citable archive \cite{Bachant2016-RM2-data}.
 

### 2016-03-15 paper.tex
Add 1:6 scale diameter

@@
 The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
-DOE/Sandia National Labs Reference Model 2 (RM2) vertical-axis cross-flow
-turbine were measured experimentally in a towing tank, to provide a
-comprehensive open dataset for validating numerical models. Performance was
-measured for a range of tip speed ratios and at multiple Reynolds numbers by
-varying the rotor's angular velocity and tow carriage speed, respectively. A
-peak power coefficient $C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were
-observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of weak linear
-$Re$-dependence of the power coefficient was observed above a turbine diameter
-Reynolds number $Re_D \approx 10^6$. The effects of support strut drag on
-turbine performance were investigated by covering the rotor's NACA 0021 struts
-with cylinders. As expected, this modification drastically reduced the rotor
-power coefficient. Strut drag losses were also measured for the NACA 0021 and
-cylindrical configurations with the rotor blades removed. For
+(1.075 m diameter) DOE/Sandia National Labs Reference Model 2 (RM2)
+vertical-axis cross-flow turbine were measured experimentally in a towing tank,
+to provide a comprehensive open dataset for validating numerical models.
+Performance was measured for a range of tip speed ratios and at multiple
+Reynolds numbers by varying the rotor's angular velocity and tow carriage speed,
+respectively. A peak power coefficient $C_P = 0.37$ and rotor drag coefficient
+$C_D = 0.84$ were observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of
+weak linear $Re$-dependence of the power coefficient was observed above a
+turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of support
+strut drag on turbine performance were investigated by covering the rotor's NACA
+0021 struts with cylinders. As expected, this modification drastically reduced
+the rotor power coefficient. Strut drag losses were also measured for the NACA
+0021 and cylindrical configurations with the rotor blades removed. For
 $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.

### 2016-03-15 paper.tex
Use initials in aknowledgments
Comment out all graphics in manuscript

@@
 \begin{figure}[h]
-    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
+    % \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
+    % \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
 
@@
 
-    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}
+    % \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}
 
@@
 
-    \includegraphics[clip,trim=0.01in 0 0 0,
-    width=\textwidth]{figures/tank_cross_section}
+    % \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
+    % \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}
+    % \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}
+    % \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
+    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
+    % \includegraphics[width=\textwidth]{figures/perf_covers.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
+    % \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
+    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
+    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
+    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/k_contours.eps}
+    % \includegraphics[width=\textwidth]{figures/k_contours.eps}
 
@@
 \begin{figure}
-    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
+    % \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
 
@@
 Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
-(WWPTO). Authors Bachant and Wosnik acknowledge additional support from the
-National Science Foundation, award 1150797. Sandia National Laboratories is a
+(WWPTO). Authors PB and MW acknowledge additional support from the National
+Science Foundation, award 1150797. Sandia National Laboratories is a
 multi-program laboratory managed and operated by Sandia Corporation, a wholly

### 2016-03-15 paper.tex
Copy all references into paper.tex; resolves #15

@@
 \bibliographystyle{plos2015}
-\bibliography{library}
+\begin{thebibliography}{10}
+
+    \bibitem{Neary2014}
+    Neary VS, Previsic M, Jepsen RA, Lawson MJ, Yu YH, Copping AE, et~al.
+    \newblock Methodology for Design and Economic Analysis of Marine Energy
+    Conversion ({MEC}) Technologies.
+    \newblock Albuquerque, NM, USA: Sandia National Laboratories; 2014.
+    SAND2014-9040.
+
+    \bibitem{Neary2014a}
+    Neary VS, Lawson M, Previsic M, Copping A, Hallett KC, A L, et~al.
+    \newblock Methodology for design and economic analysis of marine energy
+    conversion (MEC) technologies.
+    \newblock In: Proceedings of the Marine Energy Technology Symposium (METS2014).
+    Seattle, WA; 2014. .
+
+    \bibitem{Barone2011}
+    Barone M, Griffith T, Berg J.
+    \newblock Reference Model 2: ``Rev 0'' Rotor Design.
+    \newblock Sandia National Laboratories; 2011. SAND2011-9306.
+
+    \bibitem{Neary2011}
+    Neary VS.
+    \newblock Reference inflow characterization for river resource reference model
+    (RM2).
+    \newblock Oak Ridge National Laboratory; 2011. ORNL/TM-2011/360.
+    \newblock Available from:
+    \url{http://info.ornl.gov/sites/publications/files/Pub32455.pdf}.
+
+    \bibitem{Murray2011}
+    Murray J, Barone M.
+    \newblock The Development of CACTUS, a Wind and Marine Turbine Performance
+    Simulation Code.
+    \newblock In: Proceedings of the 49th AIAA Aerospace Sciences Meeting including
+    the New Horizons Forum and Aerospace Exposition; 2011. .
+
+    \bibitem{Hill2014}
+    Hill C, Neary V, Gunawan B, Guala M, Sotiropoulos F.
+    \newblock {U.S.} {D}epartment of {E}nergy {R}eference {M}odel {P}rogram {RM2}:
+    Experimental Results.
+    \newblock St. Anthony Falls Laboratory for Wind and Water Technologies Program,
+    Office of Energy Efficiency and Renewable Energy, U.S. Department of Energy;
+    2014.
+
+    \bibitem{Blackwell1976}
+    Blackwell B, Sheldahl R, Feltz L.
+    \newblock Wind Tunnel Performance Data for the {Darrieus} Wind Turbine with
+    {NACA} 0012 Blades.
+    \newblock Albuquerque, {NM}: Sandia National Laboratories; 1976. SAND76-0130.
+
+    \bibitem{Bachant2014}
+    Bachant P, Wosnik M.
+    \newblock Reynolds Number Dependence of Cross-Flow Turbine Performance and
+    Near-Wake Characteristics.
+    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
+    METS2014. Seattle, WA; 2014. Available from:
+    \url{http://hdl.handle.net/10919/49210}.
+
+    \bibitem{Bachant2016-RVAT-Re-dep}
+    Bachant P, Wosnik M. {UNH-RVAT} {R}eynolds number dependence experiment:
+    Reduced dataset and processing code; 2016.
+    \newblock fig\textbf{share}.
+    \url{http://dx.doi.org/10.6084/m9.figshare.1286960}.
+
+    \bibitem{Bachant2015-JoT}
+    Bachant P, Wosnik M.
+    \newblock Characterising the near-wake of a cross-flow turbine.
+    \newblock Journal of Turbulence. 2015 January;16(4):392--410.
+
+    \bibitem{Bachant2016-RM2-data}
+    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
+    Reduced dataset and processing code; 2016.
+    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373899.
+
+    \bibitem{Strickland1981}
+    Strickland J, Smith T, Sun K.
+    \newblock A Vortex Model of the Darrieus Turbine: An Analytical and
+    Experimental Study.
+    \newblock Lubbock, {TX}: Texas Tech University; 1981. SAND81-7017.
+
+    \bibitem{Laneville1986}
+    Laneville A, Vittecoq P.
+    \newblock Dynamic Stall: The Case of the Vertical Axis Wind Turbine.
+    \newblock Journal of Solar Energy Engineering. 1986 May;108:140--145.
+
+    \bibitem{Mays1990}
+    Mays ID, Morgan CA, Anderson MB, Powles SJR.
+    \newblock Experience with the {VAWT} 850 demonstration project.
+    \newblock In: Proceedings of European Community Wind Energy Conference; 1990. .
+
+    \bibitem{Roh2013}
+    Roh SC, Kang SH.
+    \newblock Effects of a blade profile, the {R}eynolds number, and the solidity
+    on the performance of a straight bladed vertical axis wind turbine.
+    \newblock Journal of Mechanical Science and Technology. 2013;.
+
+    \bibitem{Bedon2014}
+    Bedon G, Antonini EGA, Betta SD, Castelli MR, Benini E.
+    \newblock Evaluation of the different aerodynamic databases for vertical axis
+    wind turbine simulations.
+    \newblock Renewable and Sustainable Energy Reviews. 2014;40.
+
+    \bibitem{Sheldahl1977}
+    Sheldahl RE, Blackwell BF.
+    \newblock Free-Air Performance Tests of a 5-Metre-Diameter Darrieus Turbine.
+    \newblock Sandia Laboratories; 1977.
+
+    \bibitem{Antheaume2008}
+    Antheaume S, Maıtre T, Achard JL.
+    \newblock Hydraulic Darrieus turbines efficiency for free fluid flow conditions
+    versus power farms conditions.
+    \newblock Renewable Energy. 2008;33:2186--2198.
+
+    \bibitem{Worstell1978}
+    Worstell MH.
+    \newblock Aerodynamic Performance of the 17 Meter Diameter {Darrieus} Wind
+    Turbine.
+    \newblock Sandia National Laboratories; 1978. SAND78-1737.
+
+    \bibitem{Para1988}
+    Paraschivoiu I.
+    \newblock Double-Multiple Streamtube Model for Studying Vertical-Axis Wind
+    Turbines.
+    \newblock J Propulsion. 1988;4:370--377.
+
+    \bibitem{Orlandi2015}
+    Orlandi A, Collu M, Zanforlin S, Shires A.
+    \newblock {3D} {URANS} analysis of a vertical axis wind turbine in skewed
+    flows.
+    \newblock J Wind Eng Ind Aerodyn. 2015;147:77--84.
+
+    \bibitem{Ashwill1992}
+    Ashwill TD.
+    \newblock Measured Data for the {S}andia 34-Meter Vertical Axis Wind Turbine.
+    \newblock Albuquerque, NM 87185: Sandia National Laboratories; 1992.
+    SAND91-2228.
+
+    \bibitem{Liu1992}
+    Liu WQ, Paraschivoiu I, Martinuzzi R.
+    \newblock Calculation of Dynamic Stall on {S}andia 34-M {VAWT} Using an
+    Indicial Model.
+    \newblock Wind Engineering. 1992;.
+
+    \bibitem{Ponta2001}
+    Ponta FL, Jacovis PM.
+    \newblock A vortex model for Darrieus turbine using finite element techniques.
+    \newblock Renewable Energy. 2001;24:1--18.
+
+    \bibitem{Scheurich2011b}
+    Scheurich F, Fletcher TM, Brown RE.
+    \newblock Simulating the aerodynamic performance and wake dynamics of a
+    vertical-axis wind turbine.
+    \newblock Wind Energ. 2011;14:159--177.
+
+    \bibitem{Amet2009}
+    Amet E, Maitre T, Pellone C, Achard JL.
+    \newblock {2D} Numerical Simulations of Blade-Vortex Interaction in a
+    {D}arrieus Turbine.
+    \newblock Journal of Fluids Engineering. 2009 November;131.
+
+    \bibitem{Howell2010}
+    Howell R, Qin N, Edwards J, Durrani N.
+    \newblock Wind tunnel and numerical study of a small vertical axis wind
+    turbine.
+    \newblock Renewable Energy. 2010;35:412--422.
+
+    \bibitem{Joo2015}
+    Joo S, Choi H, Lee J.
+    \newblock Aerodynamic characteristics of two-bladed H-Darrieus at various
+    solidities and rotating speeds.
+    \newblock Energy. 2015;p. 1--13.
+
+    \bibitem{Mertens2003}
+    Mertens S, van Kuik G, van Bussel G.
+    \newblock Performance of an {H}-{D}arrieus in the skewed flow on a roof.
+    \newblock Journal of Solar Energy Engineering. 2003;125:443--440.
+    \newblock Available from:
+    \url{https://www.researchgate.net/profile/Gerard_Van_Bussel/publication/245367769_Performance_of_an_H-Darrieus_in_the_Skewed_Flow_on_a_Roof/links/0deec53bc12ee39ec4000000.pdf}.
+
+    \bibitem{Bachant2014-RVAT-baseline}
+    Bachant P, Wosnik M. {UNH-RVAT} baseline performance and near-wake
+    measurements: Reduced dataset and processing code; 2014.
+    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1080781.
+    \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
+
+    \bibitem{Michelen2014}
+    Michelen C, Neary VS, Murray JC, Barone M.
+    \newblock {CACTUS} open source code for hydrokinetic turbine design and
+    analysis: model performance evaluation and public dissemination as open
+    source design tool.
+    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium; 2014.
+    .
+
+    \bibitem{Bachant2016-Energies}
+    Bachant P, Wosnik M.
+    \newblock Effects of Reynolds Number on the Energy Conversion and Near-Wake
+    Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine.
+    \newblock Energies. 2016;9(73).
+
+    \bibitem{Bachant2015-RM2-CAD}
+    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
+    {CAD} package; 2015.
+    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373870.
+
+    \bibitem{Beam2011}
+    Beam MJ, Elbing BR, Fetterolf TK, Kline BL, Kerstetter DF, Mickey JA, et~al.
+    \newblock Power Take-Off System Design {SNL} Reference Turbine 2.
+    \newblock Penn State Applied Research Lab; 2011.
+
+    \bibitem{Fiedler2009}
+    Fiedler AJ, Tullis S.
+    \newblock Blade Offset and Pitch Effects on a High Solidity Vertical Axis Wind
+    Turbine.
+    \newblock Wind Engineering. 2009;33:237--246.
+
+    \bibitem{SentranZB}
+    Sentran. {ZB} {S} Beam Load Cell Datasheet; 2014.
+    \newblock \url{http://www.sentranllc.com/pdfs/zb1.pdf}.
+    \newblock Available from: \url{http://www.sentranllc.com/pdfs/zb1.pdf}.
+
+    \bibitem{InterfaceT8}
+    {Interface Inc }. T8 General Purpose Rotary Torque Transducer Specifications;
+    2014.
+    \newblock
+    \url{http://www.interfaceforce.com/index.php?T8-General-Purpose-Rotary-Torque-Transducer&mod=product&show=65}.
+    \newblock Available from:
+    \url{http://www.interfaceforce.com/index.php?T8-General-Purpose-Rotary-Torque-Transducer&mod=product&show=65}.
+
+    \bibitem{KollmorgenAKD}
+    Kollmorgen. {AKD} user guide; 2014.
+    \newblock
+    \url{http://www.kollmorgen.com/en-us/products/drives/servo/akd/_manuals/kollmorgen-akd-user-guide-en-rev-m/}.
+    \newblock Available from:
+    \url{http://www.kollmorgen.com/en-us/products/drives/servo/akd/_manuals/kollmorgen-akd-user-guide-en-rev-m/}.
+
+    \bibitem{RenishawLM15}
+    Renishaw. {LM}15 linear encoder datasheet; 2014.
+    \newblock
+    \url{http://resources.renishaw.com/download.aspx?lang=en&data=49238&btn=1}.
+    \newblock Available from:
+    \url{http://resources.renishaw.com/download.aspx?lang=en&data=49238&btn=1}.
+
+    \bibitem{NortekVectrino}
+    Nortek-{AS}. Vectrino 3{D} water velocity sensor lab probe datasheet; 2014.
+    \newblock
+    \url{http://www.nortekusa.com/lib/data-sheets/datasheet-vectrino-lab}.
+    \newblock Available from:
+    \url{http://www.nortekusa.com/lib/data-sheets/datasheet-vectrino-lab}.
+
+    \bibitem{ColemanSteele}
+    Coleman HW, Steele WG.
+    \newblock Experimentation, Validation, and Uncertainty Analysis for Engineers.
+    \newblock 3rd ed. John Wiley \& Sons,; 2009.
+
+    \bibitem{Cavagnaro2014}
+    Cavagnaro R, Polagye B.
+    \newblock An Evaluation of Blockage Corrections for a Helical Cross-Flow
+    Turbine.
+    \newblock In: Proceedings of the 3rd Oxford Tidal Energy Workshop. Oxford, UK;
+    2014. .
+
+    \bibitem{Lissaman1983}
+    Lissaman PBS.
+    \newblock Low-{R}eynolds-number airfoils.
+    \newblock Annual Review of Fluid Mechanics. 1983;15:223--239.
+
+    \bibitem{McMasters1980}
+    McMasters JH, Henderson ML.
+    \newblock Low-speed single-element airfoil synthesis.
+    \newblock Tech Soaring. 1980;6(2):1--21.
+
+    \bibitem{Migliore1980}
+    Migliore PG, Wolfe WP, Fanucci JB.
+    \newblock Flow Curvature Effects on {D}arrieus Turbine Blade Aerodynamics.
+    \newblock J Energy. 1980;4(2):49--55.
+
+    \bibitem{Goude2012}
+    Goude A.
+    \newblock Fluid Mechanics of Vertical Axis Turbines, Simulations and Model
+    Development.
+    \newblock Uppsala University; 2012.
+
+    \bibitem{Rawlings2008}
+    Rawlings GW.
+    \newblock Parametric characterization of an experimental vertical axis hydro
+    turbine.
+    \newblock University of British Columbia; 2008.
+
+    \bibitem{Templin1974}
+    Templin RJ.
+    \newblock Aerodynamic performance theory for the NRC vertical axis wind
+    turbine.
+    \newblock Ottawa, Canada: National Research Council Canada; 1974. LTR-LA-160.
+
+    \bibitem{Kinzel2012}
+    Kinzel M, Mulligan Q, Dabiri JO.
+    \newblock Energy exchange in an array of vertical-axis wind turbines.
+    \newblock Journal of Turbulence. 2012;13:1--13.
+
+\end{thebibliography}
 

### 2016-03-15 scripts/zip.py
Add zip script

@@ -1,0 +1,19 @@
+#!/usr/bin/env python
+"""This script zips up all the necessary source files to compile the paper."""
+
+from zipfile import ZipFile
+from subprocess import check_output
+import os
+
+# Describe version via git
+version = check_output(["git", "describe"]).strip().decode()
+
+figures = ["figures/" + f for f in os.listdir("figures") if f.endswith(".eps")]
+
+files = ["paper.tex", "PLOS-Submission.eps", "plos2015.bst"]
+
+with ZipFile("archive/paper-{}.zip".format(version), "w") as f:
+    for fig in figures:
+        f.write(fig)
+    for file in files:
+        f.write(file)

### 2016-03-16 scripts/zip.py
Add PDF paper to zip

@@ -10,7 +10,7 @@ version = check_output(["git", "describe"]).strip().decode()
 
 figures = ["figures/" + f for f in os.listdir("figures") if f.endswith(".eps")]
 
-files = ["paper.tex", "PLOS-Submission.eps", "plos2015.bst"]
+files = ["paper.pdf", "paper.tex", "PLOS-Submission.eps", "plos2015.bst"]
 
 with ZipFile("archive/paper-{}.zip".format(version), "w") as f:
     for fig in figures:

### 2016-03-16 scripts/zip.py
Zip up TIFF file as well

@@ -8,7 +8,8 @@ import os
 # Describe version via git
 version = check_output(["git", "describe"]).strip().decode()
 
-figures = ["figures/" + f for f in os.listdir("figures") if f.endswith(".eps")]
+figures = ["figures/" + f for f in os.listdir("figures") \
+           if f.endswith(".eps") or f.endswith(".tif")]
 
 files = ["paper.pdf", "paper.tex", "PLOS-Submission.eps", "plos2015.bst"]
 

### 2016-03-16 paper.tex
Add commented bib file back to paper.tex
Remove myself as corresponding author
Uncomment figures

@@
 % titles, positions, or degrees).
-\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
+\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
 Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
@@
 % in note below.
-*pxL3@unh.edu (PB), *martin.wosnik@unh.edu (MW)
+*martin.wosnik@unh.edu
 
@@
 \begin{figure}[h]
-    % \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
+    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
+    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}
 
@@
 
-    % \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}
+    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}
 
@@
 
-    % \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}
+    \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
+    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}
+    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}
+    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
+    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/perf_covers.eps}
+    \includegraphics[width=\textwidth]{figures/perf_covers.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
+    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
+    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
+    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
+    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{figures/k_contours.eps}
+    \includegraphics[width=\textwidth]{figures/k_contours.eps}
 
@@
 \begin{figure}
-    % \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
+    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}
 
@@
 \bibliographystyle{plos2015}
+%\bibliography{library}
 \begin{thebibliography}{10}

### 2016-08-28 paper.tex
Add explanation of stationary strut drag calcs

--- 2016-03-15 paper.tex
@@
 are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
-struts---both in towed and stationary conditions. These are computed in the same
-fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the rotor blades
-removed. We see that strut drag losses increase with tip speed ratio to the
-power 2--3, which makes streamlined struts much more important for low solidity
+struts---both in towed (at $U_\infty=1$ m/s) and stationary conditions. These
+are computed in the same fashion as the curves in Fig.~\ref{fig:cp-curves}, but
+with the rotor blades removed. For the stationary case, tip speed ratio and
+power coefficient were computed using the same reference velocity $U_\infty=1$
+m/s. We see that strut drag losses increase with tip speed ratio to the power
+2--3, which makes streamlined struts much more important for low solidity
 turbines, given the inverse correlation between solidity and $\lambda_0$
@@
     \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
-        (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}
+    (a) NACA 0021 and (b) cylindrical struts, both stationary and towed at 1
+    m/s. Note that stationary calculations for tip speed ratio and power
+    coefficient also assumed $U_\infty = 1$ m/s.}
 

### 2016-08-28 paper.tex
Fix virtual camber reference

@@
 coefficients given by a viscous panel method, whereas characteristics like
-lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.
+lift-to-drag ratio do not converge as strongly \cite{Bachant2016-Energies}.
 

### 2016-08-28 paper.tex
Fix typo

@@
 identical conditions, which showed similar Reynolds number thresholds but a
-flatter linear regime, likely to due virtual camber of the higher
+flatter linear regime, likely due to virtual camber of the higher
 chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results

### 2016-08-28 paper.tex
Add 'caused by'

@@
 identical conditions, which showed similar Reynolds number thresholds but a
-flatter linear regime, likely due to virtual camber of the higher
+flatter linear regime, likely due to virtual camber caused by the higher
 chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results

### 2016-08-28 paper.tex
Fix plurality error

@@
 The UNH-RVAT, for which the performance, near-wake, and Reynolds number
-dependence of was investigated using the same experimental setup as the study
+dependence were investigated using the same experimental setup as the study
 here \cite{Bachant2015-JoT, Bachant2016-Energies}, was an H-rotor of 1 m height

### 2016-08-28 paper.tex
Fix cross-reference to tow tank picture

@@
 Measurements were conducted in the UNH tow/wave tank, pictured in
-Fig.~\ref{fig:exp-setup}, a 36 m long facility with a 3.66 m wide by 2.44 m deep
-cross-section, capable of tow speeds up to 3 m/s. The blockage ratio based on
-the rotor frontal and tank cross-sectional area was 10\%. The turbine was
-mounted in a frame built from NACA 0020 struts, attached to the tow carriage by
-four linear bearings, which transfer all streamwise force to a pair of 500 lbf
-capacity Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft RPM
-was controlled by a servo motor system, which allowed precise control of the
+Fig.~\ref{fig:exp-setup-photo}, a 36 m long facility with a 3.66 m wide by 2.44
+m deep cross-section, capable of tow speeds up to 3 m/s. The blockage ratio
+based on the rotor frontal and tank cross-sectional area was 10\%. The turbine
+was mounted in a frame built from NACA 0020 struts, attached to the tow carriage
+by four linear bearings, which transfer all streamwise force to a pair of 500
+lbf capacity Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft
+RPM was controlled by a servo motor system, which allowed precise control of the
 turbine tip speed ratio. The load torque was measured by an Interface T8 200 Nm

### 2016-08-28 paper.tex
Refer back to perf-covers fig as suggested by reviewer 3

@@
 the towed versus stationary configuration, which helps explain why overall rotor
-drag coefficients remained of comparable magnitude even at low Reynolds number,
-where $C_P$ was dramatically reduced, or even negative. For the cylindrical
-struts, losses increased significantly when towed and operating in the mid range
-of tip speed ratios.
+drag coefficients shown in Fig.~\ref{fig:perf-covers} remained of comparable
+magnitude even at low Reynolds number, where $C_P$ was dramatically reduced, or
+even negative. For the cylindrical struts, losses increased significantly when
+towed and operating in the mid range of tip speed ratios.
 

### 2016-08-28 paper.tex
Add RVAT parameters to turbine geometry table

@@
 \centering
-\begin{tabular}{l|l|l}
-   & Full-scale & Model (1:6) \\
+\begin{tabular}{l|l|l|l}
+   & Full-scale RM2 & 1:6 scale RM2 & UNH-RVAT \\
 \hline
-Diameter (m)   & 6.450 & 1.075 \\
-Height (m)     & 4.840 & 0.8067 \\
-Blade root chord (m) & 0.4000 & 0.06667 \\
-Blade tip chord (m)  & 0.2400 & 0.04000 \\
-Blade profile & NACA 0021 & NACA 0021 \\
-Blade mount & 1/2 chord & 1/2 chord \\
-Blade pitch (deg.) & 0.0 & 0.0 \\
-Strut profile & NACA 0021 & NACA 0021 \\
-Strut chord (m) & 0.3600 & 0.06000 \\
-Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\
+Diameter (m)   & 6.450 & 1.075 & 1.0 \\
+Height (m)     & 4.840 & 0.8067 & 1.0 \\
+Blade root chord (m) & 0.4000 & 0.06667 & 0.14 \\
+Blade tip chord (m)  & 0.2400 & 0.04000 & 0.14 \\
+Blade profile & NACA 0021 & NACA 0021 & NACA 0020 \\
+Blade mount & 1/2 chord & 1/2 chord & 1/2 chord \\
+Blade pitch (deg.) & 0.0 & 0.0 & 0.0 \\
+Strut profile & NACA 0021 & NACA 0021 & NACA 0020 \\
+Strut chord (m) & 0.3600 & 0.06000 & 0.14 \\
+Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350 & 0.095 \\
 \end{tabular}
-\caption{\textbf{RM2 turbine geometric parameters.}}
+\caption{\textbf{Turbine geometric parameters for both the full-scale and 1:6
+scale model RM2 (tested here), along with the UNH-RVAT for comparison.}}
 \label{tab:turb-geom}

### 2016-08-28 paper.tex
Add definitions for symbols near where they're first used

@@
 River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has
-three tapered blades and a relatively low solidity $Nc/(\pi D)$ or
+three tapered blades and a relatively low solidity $Nc/(\pi D)$, where $N$ is
+the number of blades, $c$ is the chord length, and $D$ is the rotor diameter, or
 chord-to-radius ratio $c/R \approx 0.1$. A preliminary analysis with Sandia's
 CACTUS vortex line numerical model \cite{Murray2011} predicted an individual
-rotor's full-scale performance coefficient to be $C_P=0.47$ at 1 m/s flow speed
-and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$
-\cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity and
-radius, respectively. Note that the RM2 rotor solidity would be considered
-moderate to high for a wind turbine, whose $c/R$ values typically range from
-0.05 to 0.09, but MHK rotors are typically higher solidity since they must
-withstand approximately an order of magnitude higher torque in typical flows,
-necessitating relatively larger blades to meet strength and fatigue life
-requirements.
+rotor's full-scale performance coefficient to be $C_P \equiv P / \left(
+\frac{1}{2} \rho A U_\infty^3 \right) = 0.47$---where $P$ is the mechanical
+power output, $\rho$ is the fluid density, $A$ is the rotor frontal area, and
+$U_\infty$ is the free stream velocity---at 1 m/s flow speed and a tip speed
+ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where
+$\omega$ and $R$ are the rotor's angular velocity and radius, respectively. Note
+that the RM2 rotor solidity would be considered moderate to high for a wind
+turbine, whose $c/R$ values typically range from 0.05 to 0.09, but MHK rotors
+are typically higher solidity since they must withstand approximately an order
+of magnitude higher torque in typical flows, necessitating relatively larger
+blades to meet strength and fatigue life requirements.
 

### 2016-08-28 paper.tex
Rearrange wake figs so RM2 come before RVAT
Change title to include 'hydrokinetic'
Add RVAT-Re-dep perf Re dep fig to text; closes #69

@@
 
-{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
-        Cross-Flow Turbine}} \newline % Insert author names,
+{\Large \textbf\newline{Experimental Study of a Reference Model
+        Cross-Flow Hydrokinetic Turbine}} \newline % Insert author names,
 % affiliations
@@
 \cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
-$Re$-independence of the higher $c/R$ UNH-RVAT could be due to this virtual
-camber effect, since camber has been shown to cause earlier $Re$-convergence of
-the CFT's geometric torque coefficient when calculated from static foil
-coefficients given by a viscous panel method, whereas characteristics like
-lift-to-drag ratio do not converge as strongly \cite{Bachant2016-Energies}.
-
-\begin{figure}
-    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
-
-    \caption{{\bf Reynolds Number effects on performance.} Power and drag
-    coefficient at $\lambda=3.1$ plotted versus turbine diameter and approximate
-    average blade root chord Reynolds number.}
+$Re$-independence of the higher $c/R$ UNH-RVAT, shown in
+Fig.~\ref{fig:rvat-perf-re-dep}, could be due to this virtual camber effect,
+since camber has been shown to cause earlier $Re$-convergence of the CFT's
+geometric torque coefficient when calculated from static foil coefficients given
+by a viscous panel method, whereas characteristics like lift-to-drag ratio do
+not converge as strongly \cite{Bachant2016-Energies}.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}
+
+    \caption{{\bf RM2 Reynolds Number effects on performance.} Power (left) and
+    drag (right) coefficient at $\lambda=3.1$ plotted versus turbine diameter
+    and approximate average blade root chord Reynolds number.}
 
     \label{fig:perf-re-dep}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}
+
+    \caption{{\bf UNH-RVAT Reynolds Number effects on performance.} Power (left)
+    and drag (right) coefficient at $\lambda=1.9$ plotted versus turbine
+    diameter and approximate average blade chord Reynolds number. Taken from
+    \cite{Bachant2016-Energies}.}
+
+    \label{fig:rvat-perf-re-dep}
 \end{figure}
@@
 \begin{figure}
+    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
+
+    \caption{{\bf RM2 Near-Wake Mean Velocity.} RM2 near-wake mean velocity
+        field (looking upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s,
+        and $\lambda=3.1$. Refer to Fig.~\ref{fig:coordinates} for turbine axis
+        orientation. Solid dark gray lines indicate turbine frontal area.}
+
+    \label{fig:meancontquiv}
+\end{figure}
+
+\begin{figure}
     % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}
@@
     \label{fig:rvat-meancontquiv}
-\end{figure}
-
-\begin{figure}
-    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}
-
-    \caption{{\bf RM2 Near-Wake Mean Velocity.} RM2 near-wake mean velocity
-        field (looking upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s,
-        and $\lambda=3.1$. Refer to Fig.~\ref{fig:coordinates} for turbine axis
-        orientation. Solid dark gray lines indicate turbine frontal area.}
-
-    \label{fig:meancontquiv}
 \end{figure}
@@
 \begin{figure}
+    % \includegraphics[width=\textwidth]{figures/k_contours.eps}
+
+    \caption{{\bf RM2 Near-Wake Turbulence Kinetic Energy.} Turbulence kinetic
+        energy in the RM2's near-wake (looking upstream) at 1 m downstream
+        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
+        indicate turbine frontal area.}
+
+    \label{fig:kcont}
+\end{figure}
+
+\begin{figure}
     % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}
@@
     \label{fig:rvat-kcont}
-\end{figure}
-
-\begin{figure}
-    % \includegraphics[width=\textwidth]{figures/k_contours.eps}
-
-    \caption{{\bf RM2 Near-Wake Turbulence Kinetic Energy.} Turbulence kinetic
-        energy in the RM2's near-wake (looking upstream) at 1 m downstream
-        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
-        indicate turbine frontal area.}
-
-    \label{fig:kcont}
 \end{figure}

### 2016-08-28 scripts/getfigs.py

@@ -34,7 +34,7 @@ if __name__ == "__main__":
 
     # Get RVAT-Re-dep figs
     figdir = os.path.join("RVAT-Re-dep", "Figures")
-    figlist = ["meancontquiv_10.eps", "k_contours_10.eps"]
+    figlist = ["meancontquiv_10.eps", "k_contours_10.eps", "perf_re_dep.eps"]
 
     for fig in figlist:
         fix_eps(os.path.join(figdir, fig))

### 2016-08-28 paper.tex
Add labels for R and c on turbine drawing
Remove Re dep figs from text

@@
 \begin{figure}[h]
-    % \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
-
-    \caption{{\bf Turbine Model.} A drawing of the turbine model.}
+    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}
+
+    \caption{{\bf Turbine Model.} A drawing of the RM2 turbine model. All
+    dimensions are in meters}
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}
+    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}
 

### 2016-09-01 paper.tex
Revert "Change title to include 'hydrokinetic'"
This reverts commit bc6d3ad89099eb0c5cd352ab24e956631c6486bc.

--- 2016-08-28 paper.tex
@@
 
-{\Large \textbf\newline{Experimental Study of a Reference Model
-        Cross-Flow Hydrokinetic Turbine}} \newline % Insert author names,
+{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
+        Cross-Flow Turbine}} \newline % Insert author names,
 % affiliations
@@
 
-    \caption{{\bf Turbine Model.} A drawing of the turbine model.}
+    \caption{{\bf Turbine Model.} A drawing of the RM2 turbine model. All
+    dimensions are in meters}
 

### 2016-09-01 paper.tex
Add Wosnik edits from email

@@
 levels of turbulence caused by higher operating tip speed ratio and therefore
-reduced dynamic stall.
+reduced dynamic stall. Datasets, code for processing and visualization, and a
+CAD model of the turbine have been made publicly available
+\cite{Bachant2016-RM2-data,Bachant2015-RM2-CAD}.
 
@@
 (river) turbine that was designed to operate in a reach of the lower Mississippi
-River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has
-three tapered blades and a relatively low solidity $Nc/(\pi D)$, where $N$ is
-the number of blades, $c$ is the chord length, and $D$ is the rotor diameter, or
-chord-to-radius ratio $c/R \approx 0.1$. A preliminary analysis with Sandia's
-CACTUS vortex line numerical model \cite{Murray2011} predicted an individual
-rotor's full-scale performance coefficient to be $C_P \equiv P / \left(
-\frac{1}{2} \rho A U_\infty^3 \right) = 0.47$---where $P$ is the mechanical
-power output, $\rho$ is the fluid density, $A$ is the rotor frontal area, and
-$U_\infty$ is the free stream velocity---at 1 m/s flow speed and a tip speed
-ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where
-$\omega$ and $R$ are the rotor's angular velocity and radius, respectively. Note
-that the RM2 rotor solidity would be considered moderate to high for a wind
-turbine, whose $c/R$ values typically range from 0.05 to 0.09, but MHK rotors
-are typically higher solidity since they must withstand approximately an order
-of magnitude higher torque in typical flows, necessitating relatively larger
-blades to meet strength and fatigue life requirements.
+River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}, but could also
+be deployed in a tidal environment. The rotor has three tapered blades and a
+relatively low solidity $Nc/(\pi D)$, where $N$ is the number of blades, $c$ is
+the chord length, and $D$ is the rotor diameter, or chord-to-radius ratio $c/R
+\approx 0.1$. A preliminary analysis with Sandia's CACTUS vortex line numerical
+model \cite{Murray2011} predicted an individual rotor's full-scale performance
+coefficient to be $C_P \equiv P / \left( \frac{1}{2} \rho A U_\infty^3 \right) =
+0.47$---where $P$ is the mechanical power output, $\rho$ is the fluid density,
+$A$ is the rotor frontal area, and $U_\infty$ is the free stream velocity---at 1
+m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
+3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
+and radius, respectively. Note that the RM2 rotor solidity would be considered
+moderate to high for a wind turbine, whose $c/R$ values typically range from
+0.05 to 0.09, but MHK rotors are typically higher solidity since they must
+withstand approximately an order of magnitude higher torque in typical flows,
+necessitating relatively larger blades to meet strength and fatigue life
+requirements.
 
@@
 rather than diameter, though these are approximately proportional since optimal
-tip speed ratio correlates inversely with solitidy and therefore chord length),
+tip speed ratio correlates inversely with solidity and therefore chord length),
 along with a shift of the location of $C_{P_{\max}}$ toward lower tip speed
@@
     Bachant2016-RVAT-Re-dep} showed that performance and near-wake characteristics
-of a high solidity cross-flow turbine become Reynolds number independent at
+of a high solidity cross-flow turbine became Reynolds number independent at
 $Re_D \approx 10^6$ or $Re_c \approx 2 \times 10^5$.
@@
 designs via numerical rather than physical models. However, it is
-important---especially when dealing with fluid dynamics where the ``exact''
-physics cannot be resolved with even the most advanced computers---that
-numerical models be validated against experimental data. It is uncertain whether
-numerical models validated with physical model data obtained at low Reynolds
-numbers should be considered validated at all, since the scale at which the
-model will be applied for real world design problems is orders of magnitude
-larger. One way to overcome this uncertainty is to show that the scaled physical
-model test has become Reynolds number independent, so validation efforts are
-relevant at full-scale, which was the strategy employed here.
+important---especially when dealing with high Reynolds number fluid dynamics
+where the ``exact'' physics cannot be resolved with even the most advanced
+computers---that numerical models be validated against experimental data. It is
+uncertain whether numerical models validated with physical model data obtained
+at low Reynolds numbers should be considered validated at all, since the scale
+at which the model will be applied for real world design problems is orders of
+magnitude larger. One way to overcome this uncertainty is to show that the
+scaled physical model test has become Reynolds number independent, so validation
+efforts are relevant at full-scale, which was the strategy employed here.
 
@@
 operates at higher tip speed ratios. Thus, the parasitic torque from strut drag
-was measured without blades, then deliberately and significantly increased in
-the physical model to provide data to investigate its importance. The velocity
-field in the near-wake of the turbine was then measured to compare with
-measurements from a higher solidity rotor in the same experimental setup
+was measured without blades, then deliberately and dramatically increased in the
+physical model to provide data to investigate its importance. The velocity field
+in the near-wake of the turbine was then measured to compare with measurements
+from a higher solidity rotor in the same experimental setup
 \cite{Bachant2015-JoT}, and to provide validation data for numerical models that
@@
 spacing for turbine arrays. This dataset, along with the code for processing and
-visualization, has been made publicly available (licensed via Creative Commons
-CC-BY for data and MIT license for code) as a Git repository on GitHub
-(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
-digital object identifier (DOI) \cite{Bachant2016-RM2-data}.
+visualization, has been made publicly available \cite{Bachant2016-RM2-data}.
 
@@
 dependence were investigated using the same experimental setup as the study
-here \cite{Bachant2015-JoT, Bachant2016-Energies}, was an H-rotor of 1 m height
-and 1 m diameter. The UNH-RVAT experimental datasets are also openly available
-\cite{Bachant2014-RVAT-baseline, Bachant2016-RVAT-Re-dep}, and provide an
-interesting comparison for the near-wake dynamics of a rotor similar in size to
-the 1:6 scale RM2, but with non-tapered blades and a high solidity $c/R = 0.28$.
+reported here \cite{Bachant2015-JoT, Bachant2016-Energies}, was an H-rotor of 1
+m height and 1 m diameter. The UNH-RVAT experimental datasets are also openly
+available \cite{Bachant2014-RVAT-baseline, Bachant2016-RVAT-Re-dep}, and provide
+an interesting comparison for the near-wake dynamics of a rotor similar in size
+to the 1:6 scale RM2, but with non-tapered blades and a high solidity $c/R =
+0.28$.
 
@@
 covers were designed to slip over the struts, which provided a deliberate and
-significant increase in strut drag. Endcaps were also fabricated to allow the
-high drag strut cover configuration to be operated without blades. A drawing of
-the strut covers is shown in Fig.~\ref{fig:covers}.
+dramatic increase in strut drag. Endcaps were also fabricated to allow the high
+drag strut cover configuration to be operated without blades. A drawing of the
+strut covers is shown in Fig.~\ref{fig:covers}.
 
@@
 samples (tow speed, torque, drag, angular velocity), ensuring precise
-calculation of, e.g., power coefficient. Since there was also synchronization of
-the initial sample from each of the three subsystems, correlation of events in
-the performance and wake signals is also possible.
+calculation of turbine performance parameters, e.g., power coefficient. Since
+there was also synchronization of the initial sample from each of the three
+subsystems, correlation of events in the performance and wake signals is also
+possible.
 
@@
 Since the blockage ratio was relatively low (10\%), and a definitive blockage
-correction for cross-flow turbines has not been established \cite{Cavagnaro2014}
-blockage effects were not corrected for. Furthermore, most numerical modeling
-efforts can easily incorporate finite domains. Therefore, applying blockage
-corrections to experimental data could actually complicate validation efforts.
+correction method for cross-flow turbines has not been established
+\cite{Cavagnaro2014} blockage effects were not corrected for. Furthermore, most
+numerical modeling efforts can easily model finite domains, i.e., incorporate
+tow tank walls. Therefore, applying blockage corrections to experimental data
+could actually complicate validation efforts.
 
@@
 was reached at $Re_D=1.3 \times 10^6$. Note how at lower tip speed ratios and
-Reynolds numbers, $C_P$ becomes significantly negative, which was possible
-thanks to the speed control of the experimental setup's servo motor applying
-negative torque to the rotor.
+Reynolds numbers, $C_P$ becomes significantly negative, which was possible with
+the speed control of the experimental setup's servo motor applying negative
+torque to the rotor.
 
@@
 
-Mean rotor drag coefficients are plotted versus tip speed ratio in
+Mean rotor drag (or thrust) coefficients are plotted versus tip speed ratio in
 Fig.~\ref{fig:cd-curves}. These $C_D$ curves show little difference compared to
-the power coefficient curves, which is most noticeable at low $\lambda$ and low
-$Re$. The relative similarity could be attributed to the effects of stall, where
-the lift-to-drag ratio on the blades may drop, decreasing rotor torque, though
-the total resultant force due to high blade drag retains a similar component in
-the streamwise direction. When operating at maximum power coefficient,
-$\lambda_0=3.1$, and $Re_D=1.3 \times 10^6$, a rotor drag coefficient $C_D=0.84$
-was measured.
+the power coefficient curves; differences are most noticeable at low $\lambda$
+and low $Re$. The relative similarity could be attributed to the effects of
+stall, where the lift-to-drag ratio on the blades may drop, decreasing rotor
+torque, though the total resultant force due to high blade drag retains a
+similar component in the streamwise direction. When operating at maximum power
+coefficient, $\lambda_0=3.1$, and $Re_D=1.3 \times 10^6$, a rotor drag
+coefficient $C_D=0.84$ was measured.
 
@@
 was about 5\% lower for this experiment. However, the differences observed are
-larger than the area ratio between the two experiments. We also see relatively
+larger than the differences in measurement plane area. We also see relatively
 lower levels of cross-stream turbulent transport due to the lack of blade stall
@@
 
-\subsection*{Conclusions}
+\section*{Conclusions}
 
@@
 lower levels of turbulence in the near-wake, which may present a trade-off when
-considering optimal array layouts.
-
-This dataset, along with the code for processing and visualization, is provided
-openly via a Creative Commons license (MIT license for code), and is available
-as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
-citable archive \cite{Bachant2016-RM2-data}.
+considering optimal array layouts for maximizing power output per unit footprint
+area.
+
+\section*{Data Availability}
+
+The data reported in this publication, along with code for processing and
+visualization have been made publicly available (licensed via Creative Commons
+CC-BY for data and MIT license for code) as a Git repository on GitHub
+(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citable archive with a
+digital object identifier (DOI). A CAD model of the turbine (also licensed
+CC-BY) is available from \cite{Bachant2015-RM2-CAD}.
 

### 2016-09-01 paper.tex
Add Vince edits

@@
 The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
-(1.075 m diameter) DOE/Sandia National Labs Reference Model 2 (RM2)
-vertical-axis cross-flow turbine were measured experimentally in a towing tank,
-to provide a comprehensive open dataset for validating numerical models.
-Performance was measured for a range of tip speed ratios and at multiple
-Reynolds numbers by varying the rotor's angular velocity and tow carriage speed,
-respectively. A peak power coefficient $C_P = 0.37$ and rotor drag coefficient
-$C_D = 0.84$ were observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of
-weak linear $Re$-dependence of the power coefficient was observed above a
-turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of support
-strut drag on turbine performance were investigated by covering the rotor's NACA
-0021 struts with cylinders. As expected, this modification drastically reduced
-the rotor power coefficient. Strut drag losses were also measured for the NACA
-0021 and cylindrical configurations with the rotor blades removed. For
+model (1.075 m diameter) US Department of Energy's Reference Model vertical-axis
+cross-flow turbine were measured experimentally in a towing tank, to provide a
+comprehensive open dataset for validating numerical models. Performance was
+measured for a range of tip speed ratios and at multiple Reynolds numbers by
+varying the rotor's angular velocity and tow carriage speed, respectively. A
+peak power coefficient $C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were
+observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of weak linear
+$Re$-dependence of the power coefficient was observed above a turbine diameter
+Reynolds number $Re_D \approx 10^6$. The effects of support strut drag on
+turbine performance were investigated by covering the rotor's NACA 0021 struts
+with cylinders. As expected, this modification drastically reduced the rotor
+power coefficient. Strut drag losses were also measured for the NACA 0021 and
+cylindrical configurations with the rotor blades removed. For
 $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.

### 2016-09-01 paper.tex
Add 'of the' to abstract

@@
 The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
-model (1.075 m diameter) US Department of Energy's Reference Model vertical-axis
-cross-flow turbine were measured experimentally in a towing tank, to provide a
-comprehensive open dataset for validating numerical models. Performance was
-measured for a range of tip speed ratios and at multiple Reynolds numbers by
-varying the rotor's angular velocity and tow carriage speed, respectively. A
-peak power coefficient $C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were
-observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of weak linear
-$Re$-dependence of the power coefficient was observed above a turbine diameter
-Reynolds number $Re_D \approx 10^6$. The effects of support strut drag on
-turbine performance were investigated by covering the rotor's NACA 0021 struts
-with cylinders. As expected, this modification drastically reduced the rotor
-power coefficient. Strut drag losses were also measured for the NACA 0021 and
-cylindrical configurations with the rotor blades removed. For
+model (1.075 m diameter) of the US Department of Energy's Reference Model
+vertical-axis cross-flow turbine were measured experimentally in a towing tank,
+to provide a comprehensive open dataset for validating numerical models.
+Performance was measured for a range of tip speed ratios and at multiple
+Reynolds numbers by varying the rotor's angular velocity and tow carriage speed,
+respectively. A peak power coefficient $C_P = 0.37$ and rotor drag coefficient
+$C_D = 0.84$ were observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of
+weak linear $Re$-dependence of the power coefficient was observed above a
+turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of support
+strut drag on turbine performance were investigated by covering the rotor's NACA
+0021 struts with cylinders. As expected, this modification drastically reduced
+the rotor power coefficient. Strut drag losses were also measured for the NACA
+0021 and cylindrical configurations with the rotor blades removed. For
 $\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.

### 2016-09-02 scripts/diff.sh
Update diff script to use current rev in filename

@@ -3,9 +3,10 @@
 # is supplied as the first argument. This can be any valid Git identifier, e.g.,
 # a commit hash, tag, etc.
 
+CURRENT=$(git describe --always --dirty)
 rev=$1
-git show $rev:paper.tex > archive/paper-$rev.tex
-latexdiff --exclude-textcmd="section,subsection,subsubsection" --math-markup=off archive/paper-$rev.tex paper.tex > paper-$rev-diff.tex
-latexmk paper-$rev-diff.tex -pdf -f
-mv paper-$rev-diff.pdf archive
-rm paper-$rev*
+git show $rev:paper.tex > archive/paper-$CURRENT-$rev.tex
+latexdiff --exclude-textcmd="section,subsection,subsubsection" --math-markup=off archive/paper-$CURRENT-$rev.tex paper.tex > paper-$CURRENT-$rev-diff.tex
+latexmk paper-$CURRENT-$rev-diff.tex -pdf -f
+mv paper-$CURRENT-$rev-diff.pdf archive
+rm paper-$CURRENT-$rev*

### 2016-09-18 paper.tex
Remove citations from abstract; resolves #75
Regenerate bibliography in order; resolves #74

--- 2016-09-01 paper.tex
@@
 reduced dynamic stall. Datasets, code for processing and visualization, and a
-CAD model of the turbine have been made publicly available
-\cite{Bachant2016-RM2-data,Bachant2015-RM2-CAD}.
+CAD model of the turbine have been made publicly available.
 
@@
 \bibliographystyle{plos2015}
-%\bibliography{library}
+% \bibliography{library}
+
 \begin{thebibliography}{10}
@@
     \newblock In: Proceedings of the Marine Energy Technology Symposium (METS2014).
-    Seattle, WA; 2014. .
+      Seattle, WA; 2014.
 
@@
     \newblock In: Proceedings of the 49th AIAA Aerospace Sciences Meeting including
-    the New Horizons Forum and Aerospace Exposition; 2011. .
+      the New Horizons Forum and Aerospace Exposition; 2011.
 
@@
     \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
-    METS2014. Seattle, WA; 2014. Available from:
+      METS2014. Seattle, WA; 2014.Available from:
       \url{http://hdl.handle.net/10919/49210}.
@@
     \newblock Characterising the near-wake of a cross-flow turbine.
-    \newblock Journal of Turbulence. 2015 January;16(4):392--410.
+    \newblock Journal of Turbulence. 2015;16(4):392--410.
+    \newblock doi:{10.1080/14685248.2014.1001852}.
 
@@
       Reduced dataset and processing code; 2016.
-    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373899.
+    \newblock fig\textbf{share}.
+      \url{http://dx.doi.org/10.6084/m9.figshare.1373899}.
 
@@
     \newblock Dynamic Stall: The Case of the Vertical Axis Wind Turbine.
-    \newblock Journal of Solar Energy Engineering. 1986 May;108:140--145.
+    \newblock Journal of Solar Energy Engineering. 1986;108:140--145.
 
@@
     \newblock Experience with the {VAWT} 850 demonstration project.
-    \newblock In: Proceedings of European Community Wind Energy Conference; 1990. .
+    \newblock In: Proceedings of European Community Wind Energy Conference; 1990.
 
@@
     \bibitem{Antheaume2008}
-    Antheaume S, Maıtre T, Achard JL.
-    \newblock Hydraulic Darrieus turbines efficiency for free fluid flow conditions
-    versus power farms conditions.
+    Antheaume S, Ma{\^\i}tre T, Achard JL.
+    \newblock Hydraulic {D}arrieus turbines efficiency for free fluid flow
+      conditions versus power farms conditions.
     \newblock Renewable Energy. 2008;33:2186--2198.
@@
     \bibitem{Amet2009}
-    Amet E, Maitre T, Pellone C, Achard JL.
+    Amet E, Ma{\^\i}tre T, Pellone C, Achard JL.
     \newblock {2D} Numerical Simulations of Blade-Vortex Interaction in a
       {D}arrieus Turbine.
-    \newblock Journal of Fluids Engineering. 2009 November;131.
+    \newblock Journal of Fluids Engineering. 2009;131.
+    \newblock doi:{10.1115/1.4000258}.
 
@@
       solidities and rotating speeds.
-    \newblock Energy. 2015;p. 1--13.
+    \newblock Energy. 2015; p. 1--13.
 
@@
     \newblock Journal of Solar Energy Engineering. 2003;125:443--440.
-    \newblock Available from:
-    \url{https://www.researchgate.net/profile/Gerard_Van_Bussel/publication/245367769_Performance_of_an_H-Darrieus_in_the_Skewed_Flow_on_a_Roof/links/0deec53bc12ee39ec4000000.pdf}.
+    \newblock doi:{10.1115/1.1629309}.
 
@@
       measurements: Reduced dataset and processing code; 2014.
-    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1080781.
+    \newblock fig\textbf{share}.
+      \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
     \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
@@
     \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium; 2014.
-    .
 
@@
     \newblock Energies. 2016;9(73).
+    \newblock doi:{10.3390/en9020073}.
 
@@
       {CAD} package; 2015.
-    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373870.
+    \newblock fig\textbf{share}.
+      \url{http://dx.doi.org/10.6084/m9.figshare.1373870}.
 
@@
     \newblock In: Proceedings of the 3rd Oxford Tidal Energy Workshop. Oxford, UK;
-    2014. .
+      2014.
 
@@
     \newblock Journal of Turbulence. 2012;13:1--13.
+    \newblock doi:{10.1080/14685248.2012.712698}.
 

### 2016-09-18 paper.tex
Add VS for all Neary refs; towards #72

@@
     \bibitem{Hill2014}
-    Hill C, Neary V, Gunawan B, Guala M, Sotiropoulos F.
+    Hill C, Neary VS, Gunawan B, Guala M, Sotiropoulos F.
     \newblock {U.S.} {D}epartment of {E}nergy {R}eference {M}odel {P}rogram {RM2}:
@@
     \bibitem{Bachant2016-RM2-data}
-    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
+    Bachant P, Wosnik M, Gunawan B, Neary VS. {UNH} {RM2} tow tank experiment:
       Reduced dataset and processing code; 2016.
@@
     \bibitem{Bachant2015-RM2-CAD}
-    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
+    Bachant P, Wosnik M, Gunawan B, Neary VS. 1:6 scale {RM2} cross-flow turbine
       {CAD} package; 2015.

### 2016-09-18 paper.tex
Use 'N' for number of blades in table for consistency
Fix table ref format; resolves #76

@@
     \begin{tabular}{c|c|c|c|c|c}
-        Name & Rotor type & $N_\mathrm{b}$ & $c/R$ & $Re_D$ & Used in \\
+        Name & Rotor type & $N$ & $c/R$ & $Re_D$ & Used in \\
         \hline
@@
 scaled from the SAFL RM2 model \cite{Hill2014}. Values for both the 1:6 and
-full-scale designs are presented in Tab.~\ref{tab:turb-geom} and a drawing of
+full-scale designs are presented in Table~\ref{tab:turb-geom} and a drawing of
 the turbine is shown in Fig.~\ref{fig:turbine-drawing}. The rotor
@@
 file of the experimental data and code repository \cite{Bachant2016-RM2-data}.
-Tow speed and their corresponding turbine diameter and blade chord Reynolds
-numbers are presented in Tab.~\ref{tab:re}.
+Tow speeds and their corresponding turbine diameter and blade chord Reynolds
+numbers are presented in Table~\ref{tab:re}.
 

### 2016-09-18 paper.tex
Correct fig ref format; resolves #77

@@
 full-scale designs are presented in Table~\ref{tab:turb-geom} and a drawing of
-the turbine is shown in Fig.~\ref{fig:turbine-drawing}. The rotor
+the turbine is shown in Fig~\ref{fig:turbine-drawing}. The rotor
 components---blades, struts, shaft, and center hub sections---were fabricated
@@
 drag strut cover configuration to be operated without blades. A drawing of the
-strut covers is shown in Fig.~\ref{fig:covers}.
+strut covers is shown in Fig~\ref{fig:covers}.
 
@@
 Measurements were conducted in the UNH tow/wave tank, pictured in
-Fig.~\ref{fig:exp-setup-photo}, a 36 m long facility with a 3.66 m wide by 2.44
+Fig~\ref{fig:exp-setup-photo}, a 36 m long facility with a 3.66 m wide by 2.44
 m deep cross-section, capable of tow speeds up to 3 m/s. The blockage ratio
@@
 and drawing of the experimental setup are shown in
-Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
+Figs~\ref{fig:exp-setup-photo}~and~\ref{fig:exp-setup}, respectively.
 
@@
 $x/D = 0.93$. The cross-stream and vertical coordinates are shown in
-Fig.~\ref{fig:coordinates}. Altogether 750 tows were performed and included in
+Fig~\ref{fig:coordinates}. Altogether 750 tows were performed and included in
 the experimental database.
@@
 Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
-tip speed ratio in Fig.~\ref{fig:cp-curves}. In general, $C_P$ increases with
+tip speed ratio in Fig~\ref{fig:cp-curves}. In general, $C_P$ increases with
 $Re$, along with a reduction in the optimal tip speed ratio, due to the tendency
@@
 Mean rotor drag (or thrust) coefficients are plotted versus tip speed ratio in
-Fig.~\ref{fig:cd-curves}. These $C_D$ curves show little difference compared to
+Fig~\ref{fig:cd-curves}. These $C_D$ curves show little difference compared to
 the power coefficient curves; differences are most noticeable at low $\lambda$
@@
 The effects of Reynolds number on the power and drag coefficients at
-$\lambda=3.1$ are shown in Fig.~\ref{fig:perf-re-dep}. The rotor drag
+$\lambda=3.1$ are shown in Fig~\ref{fig:perf-re-dep}. The rotor drag
 coefficient $C_D$ became more or less Reynolds number independent for $Re_D \ge
@@
 $Re$-independence of the higher $c/R$ UNH-RVAT, shown in
-Fig.~\ref{fig:rvat-perf-re-dep}, could be due to this virtual camber effect,
+Fig~\ref{fig:rvat-perf-re-dep}, could be due to this virtual camber effect,
 since camber has been shown to cause earlier $Re$-convergence of the CFT's
@@
 Performance curves for the rotor with both NACA 0021 and cylindrical struts are
-shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
+shown in Fig~\ref{fig:perf-covers}. As expected, the high drag cylindrical
 struts reduce performance dramatically, producing an entirely negative $C_P$
@@
 Measurements for the power coefficient contributions of the strut drag losses
-are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
+are presented in Fig~\ref{fig:no-blades} for NACA 0021 and cylindrical
 struts---both in towed (at $U_\infty=1$ m/s) and stationary conditions. These
-are computed in the same fashion as the curves in Fig.~\ref{fig:cp-curves}, but
+are computed in the same fashion as the curves in Fig~\ref{fig:cp-curves}, but
 with the rotor blades removed. For the stationary case, tip speed ratio and
@@
 the towed versus stationary configuration, which helps explain why overall rotor
-drag coefficients shown in Fig.~\ref{fig:perf-covers} remained of comparable
+drag coefficients shown in Fig~\ref{fig:perf-covers} remained of comparable
 magnitude even at low Reynolds number, where $C_P$ was dramatically reduced, or
@@
 m downstream ($x/D=0.93$) from the rotor axis is plotted in
-Fig.~\ref{fig:meancontquiv}. The mean streamwise velocity deficit is markedly
+Fig~\ref{fig:meancontquiv}. The mean streamwise velocity deficit is markedly
 more symmetric than that of the higher solidity UNH-RVAT, shown in
-Fig.~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower acceleration
+Fig~\ref{fig:rvat-meancontquiv}, with the RM2 inducing lower acceleration
 around the turbine due to the lower rotor drag coefficient and a slightly lower
@@
         field (looking upstream) at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s,
-        and $\lambda=3.1$. Refer to Fig.~\ref{fig:coordinates} for turbine axis
+        and $\lambda=3.1$. Refer to Fig~\ref{fig:coordinates} for turbine axis
         orientation. Solid dark gray lines indicate turbine frontal area.}
@@
 
-Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
+Fig~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
 mainly see unsteadiness in the flow generated by the blade tip vortex shedding
 (the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, shown in
-Fig.~\ref{fig:rvat-kcont}, turbulence generation is lower overall, without the
+Fig~\ref{fig:rvat-kcont}, turbulence generation is lower overall, without the
 intense vertical band around $y/R=-1$, which indicates that the RM2 blades are
@@
 following the methodology in \cite{Bachant2015-JoT}. Weighted averages for these
-calculations are shown in Fig.~\ref{fig:Ktransport}. Due to the weaker blade
+calculations are shown in Fig~\ref{fig:Ktransport}. Due to the weaker blade
 vortex shedding, transport due to vertical advection at this point in the wake

### 2016-09-18 paper.tex
Remove redundant URLs from bibliography

@@
     \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
-      METS2014. Seattle, WA; 2014.Available from:
+      METS2014. Seattle, WA; 2014. Available from:
       \url{http://hdl.handle.net/10919/49210}.
@@
     \newblock fig\textbf{share}.
+    \newblock
       \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
-    \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
 
@@
     Sentran. {ZB} {S} Beam Load Cell Datasheet; 2014.
-    \newblock \url{http://www.sentranllc.com/pdfs/zb1.pdf}.
     \newblock Available from: \url{http://www.sentranllc.com/pdfs/zb1.pdf}.
@@
       2014.
-    \newblock
-      \url{http://www.interfaceforce.com/index.php?T8-General-Purpose-Rotary-Torque-Transducer&mod=product&show=65}.
     \newblock Available from:
@@
     Kollmorgen. {AKD} user guide; 2014.
-    \newblock
-      \url{http://www.kollmorgen.com/en-us/products/drives/servo/akd/_manuals/kollmorgen-akd-user-guide-en-rev-m/}.
     \newblock Available from:
@@
     Renishaw. {LM}15 linear encoder datasheet; 2014.
-    \newblock
-      \url{http://resources.renishaw.com/download.aspx?lang=en&data=49238&btn=1}.
     \newblock Available from:
@@
     Nortek-{AS}. Vectrino 3{D} water velocity sensor lab probe datasheet; 2014.
-    \newblock
-      \url{http://www.nortekusa.com/lib/data-sheets/datasheet-vectrino-lab}.
     \newblock Available from:
